### 2014-10-03 doc/paper/latex/getting_started.tex
Initial Commit to GITHUB

\section{Introduction}

Modern core routers are complex system where a large part of the functionalities
is implemented in software. From a single-process/single-threaded model
systems have evolved to multiple threads, multiple processes, and even multiple 
nodes operating cooperatively. Even when processes are single threaded, they 
often carry out asynchronous comunication and react to events, effectively
handling concurrent execution contexts within a single thread. Control plane,
admin plane and to some extent data plane implement multiple functionalities
through transactions and interactions across different processes and threads.
Some thread may cooperate to carry out multiple occurrencies of the same or
different functionality. Hence, verifying the correct execution of a
functionality is a complex task, typically requiring engineers to examine traces
produced by various processes. Due to the complexity of the system
very few engineers are familiar enough with the internals of all the
processes involved, and therefore able to confidently interpret all traces. Thus
triaging of bugs often requires multiple engineers attention for a considerable
amount of time, diverting those engineers from more productive tasks.

This reliance on engineers for doing even the first level of triaging is very
expensive and not scalable. In this paper we present a solution addressing this  
problem. The solution is based on emitting traces in a formal language where 
events and interactions are captured, and from which a model can be
automatically built. Through a second formal language we support specification
of expected flows for various functionalities. Finally, we provide a tool which
can  apply flow specifications to the model created from the traces, allowing
to do both visual inspection of flows in the form of sequence diagram charts as
well as GUI-less verification, for use in automatic tests.

MSCViewer is a
\href{http://en.wikipedia.org/wiki/Message_Sequence_Chart#Live_Sequence_Charts}{message sequence chart}
visualization and analysis tool. The tool was created in NOSTG in the context of
the NG-XR admin-plane development, and it is part of a set of technologies known
under the name of RISE (Reusable Infrastructure Software Elements).
while MSCViewer is indepenent from other RISE elements, such elements can
be easily integrated in new or existing application to 
leverage the power of Message Sequence Chart analysis efficiently and with
minimal effort.
A brief overview of RISE will be provided in section~\ref{sec:RISE}.

### 2014-10-03 src/com/cisco/mscviewer/expression/ParserState.java

@@ -1,0 +1,95 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since   Aug 2012
+ */
+package com.cisco.mscviewer.expression;
+
+import java.util.ArrayList;
+import java.util.Collections;
+import java.util.HashSet;
+import java.util.Properties;
+
+public class ParserState {
+    public static int COMPLETION = 1;
+    String txt;
+    Properties props;
+    Tokenizer tk;
+    int pos;
+    HashSet<String> completion;
+
+    public ParserState(String txt) {
+        this(txt, 0);
+    }
+
+    public ParserState(String txt, int flags) {
+        if ((flags & COMPLETION) != 0)
+            txt += Token.COMPL_CHAR;
+        pos = -1;
+        props = new Properties();
+        completion = new HashSet<String>();
+        tk = new Tokenizer(txt);
+        //		tk.print();
+    }
+
+    void setPos(int p) {
+        pos = p;
+    }
+
+    int getPos() {
+        return pos;
+    }
+
+    Token next() throws NoMoreTokensException {
+        try {
+            setPos(getPos()+1);		
+            return tok();
+        }catch(IndexOutOfBoundsException ex) {
+            throw new NoMoreTokensException();
+        }
+    }
+
+    Token prev()  {
+        setPos(getPos()-1);		
+        return tok();
+    }
+
+    void setProperty(String key, String value) {
+        props.setProperty(key, value);
+    }
+
+    String getProperty(String key) {
+        return props.getProperty(key);
+    }
+
+    Token tok() {
+        return tk.getTokenAt(pos);
+    }
+
+    void compl(String str) {
+        String t = tok().string;
+        if (t.charAt(t.length()-1) == Token.COMPL_CHAR) {
+            t = t.substring(0, t.length()-1);
+            if (str.startsWith(t))
+                completion.add(str);
+        }		
+    }
+
+    public ArrayList<String> getCompletions() {
+        ArrayList<String> al = new ArrayList<String>();
+        al.addAll(completion);
+        Collections.sort(al);
+        return 	al;
+    }
+
+    public int getTokenCount() {
+        return tk.getTokenCount();
+    }
+
+}

### 2014-10-03 src/com/cisco/mscviewer/expression/Token.java

@@ -1,0 +1,97 @@
+ /*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since   Aug 2012
+*/
+package com.cisco.mscviewer.expression;
+ public class Token {
+     final static char COMPL_CHAR = '$';
+     //	String toks[] = new String[] {
+     //			null, null, "(", ")", ">=", "<=", ">", "<", "=", 
+     //			"or", "and", "not", "label", "time", "duration",
+     //			"startswith", "endswith", "contains", "ns", "us", 
+     //			"ms", "s", "event", "interaction", null, "where",
+     //			"type", "source", "sink", "[", "]"
+     //	};
+     enum TT {
+         STRING(null), NUM(null), OPEN("("), CLOSE(")"), GEQ(">="),
+         LEQ("<="), GT(">"), LT("<"), EQ("="), OR("or"), AND("and"),
+         NOT("not"), LABEL("label"), TIME("time"), DURATION("duration"),
+         STARTSWITH("startswith"), ENDSWITH("endswith"), CONTAINS("contains"),
+         UNKNOWN(null), TYPE("type"), SOURCE("source"), SINK("sink"), 
+         OPEN_SQUARE("["), CLOSE_SQUARE("]"), NS("ns"), US("us"), MS("ms"), S("s"); 
+         String s;
+
+         TT(String s) {
+             this.s = s;
+         }
+         @Override
+         public String toString() {
+             return s;
+         }
+     };
+     //	final static int TT_STRING=0;
+     //	final static int TT_NUM=1;
+     //	final static int TT_OPEN=2;
+     //	final static int TT_CLOSE=3;
+     //	final static int TT_GEQ=4;
+     //	final static int TT_LEQ=5;
+     //	final static int TT_GT=6;
+     //	final static int TT_LT=7;
+     //	final static int TT_EQ=8;
+     //	final static int TT_OR=9;
+     //	final static int TT_AND=10;
+     //	final static int TT_NOT=11;
+     //	final static int TT_LABEL=12;
+     //	final static int TT_TIME=13;
+     //	final static int TT_DURATION=14;
[…]

### 2014-10-03 src/com/cisco/mscviewer/graph/Graph.java

@@ -1,0 +1,296 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jan 2014
+ */
+package com.cisco.mscviewer.graph;
+
+import com.cisco.mscviewer.util.ProgressReport;
+import com.cisco.mscviewer.model.Entity;
+import com.cisco.mscviewer.model.Event;
+import com.cisco.mscviewer.model.Interaction;
+import com.cisco.mscviewer.model.MSCDataModel;
+import java.util.HashMap;
+import java.util.Iterator;
+import java.util.TreeSet;
+
+
+public class Graph {
+    private ProgressReport pr;
+    
+    class I {
+
+        int v;
+        boolean entity;
+
+        public I(int v, boolean entity) {
+            this.v = v;
+            this.entity = entity;
+        }
+
+        @Override
+        public String toString() {
+            return "(" + v + ", " + (entity ? "E)" : "I)");
+        }
+    }
+    I[][] fromNode;
+    I[][] toNode;
+
+    private final MSCDataModel dm;
+
+    /**
+     * creates a graph where:
+     * <ul>
+     * <li> Each node represents a sequence of events with same timestamp and
+     * entity
+     * <li> there is an edge between each pair of consecutive (by timestamp)
+     * nodes for the same entity
+     * <li> there is an edge between each pair of consecutive (by timestamp)
+     * nodes not belonging to the same entity and with different timestamp
+     * </ul>
+     * note: this code assumes that all events belonging to the same entity and
+     * with the same timestamp are going to appear contiguously in the global
+     * array of events in the datamodel.
+     *
+     * @param dm
+     * @param obs
+     */
+    public Graph(MSCDataModel dm) {
+        this.dm = dm;
+        final int evCount = dm.getEventCount();
+        if (evCount == 0) {
+            return;
+        }
+        int interCount = dm.getInteractionCount();
+        fromNode = new I[evCount][];
+        toNode = new I[evCount][];
+        HashMap<Entity, Integer> enToEvIdx = new HashMap<Entity, Integer>();
+        pr = null;
+        ProgressReport subPr = null;
+        try {
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/CompactViewFilter.java

@@ -1,0 +1,38 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+package com.cisco.mscviewer.gui;
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
+import com.cisco.mscviewer.model.*;
+
+/**
+ * @author Roberto Attias
+ * @since  Jan 2012
+ */
+class CompactViewFilter implements MSCDataModelEventFilter { 
+    private final ViewModel m;
+    private Matcher matcher;
+
+    public CompactViewFilter(ViewModel m, String filterRegExp) {
+        this.m = m;
+        if (m == null)
+            throw new NullPointerException("null EntityHeaderModel");
+        if (filterRegExp != null) {
+            matcher = Pattern.compile(filterRegExp).matcher("");
+        }
+    }
+
+    @Override
+    public boolean filter(Event ev) {
+        return 
+        m.indexOf(ev.getEntity()) != -1 && 
+        (matcher != null ? matcher.reset(ev.getLabel()).matches() : true);
+    }
+
+}

### 2014-10-03 src/com/cisco/mscviewer/gui/DataPanel.java

@@ -1,0 +1,162 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+package com.cisco.mscviewer.gui;
+import com.cisco.mscviewer.io.JSonException;
+import com.cisco.mscviewer.model.Event;
+import com.cisco.mscviewer.model.Interaction;
+import com.cisco.mscviewer.model.JSonObject;
+
+import java.awt.BorderLayout;
+import java.util.logging.Level;
+import java.util.logging.Logger;
+
+import javax.swing.JPanel;
+import javax.swing.JScrollPane;
+import javax.swing.JTable;
+
+import org.jdesktop.swingx.JXTreeTable;
+import org.jdesktop.swingx.treetable.AbstractTreeTableModel;
+
+class TreeTableNodeModel {
+    String fieldName;
+    Object value;
+    
+    public TreeTableNodeModel(String key, Object value) {
+        fieldName = key;
+        this.value = value;
+    }
+}
+
+/**
+ * @author Roberto Attias
+ * @since  Aug 2012
+ */
+class TreeTableModel extends AbstractTreeTableModel {
+    private final static String[] COLUMN_NAMES = {"Key", "Value"};
+    
+    public TreeTableModel(JSonObject obj) {
+        super(new TreeTableNodeModel("ROOT", obj));
+    }
+    
+    @Override
+    public int getColumnCount() {
+        return COLUMN_NAMES.length;
+    }
+    
+    @Override
+    public String getColumnName(int column) {
+        return COLUMN_NAMES[column];
+    }
+    
+    @Override
+    public boolean isCellEditable(Object node, int column) {
+        return false;
+    }
+    
+    @Override
+    public boolean isLeaf(Object node) {
+        boolean b = ! (((TreeTableNodeModel)node).value instanceof JSonObject);
+        return b;
+    }
+    
+    @Override
+    public int getChildCount(Object node) {
+        int c;
+        TreeTableNodeModel o = (TreeTableNodeModel)node;
+        if (o.value instanceof JSonObject)
+            c = ((JSonObject)o.value).getFieldCount();
+        else
+            c = 0;
+        return c;
+    }
+    
+    @Override
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/DoubleTextField.java

@@ -1,0 +1,100 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jun 2011
+ */
+package com.cisco.mscviewer.gui;
+
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.text.DecimalFormat;
+
+import javax.swing.text.AttributeSet;
+import javax.swing.JTextField;
+import javax.swing.text.BadLocationException;
+import javax.swing.text.Document;
+import javax.swing.text.PlainDocument;
+
+@SuppressWarnings("serial")
+class DoubleTextField extends JTextField {
+    private DecimalFormat zfFormat;
+    private DecimalFormat zfFormatE;
+    private double minNonExp;
+
+    public DoubleTextField(double initVal, int decimalDigits) {
+        super("" + initVal);
+        String fmt = "####.";
+        for(int i=0; i<decimalDigits; i++)
+            fmt += "#";
+        zfFormat = new DecimalFormat(fmt);
+        minNonExp = 1.0/Math.pow(10,decimalDigits);
+        fmt += "E0";
+        zfFormatE = new DecimalFormat(fmt);
+        addActionListener(new ActionListener() {
+            public void actionPerformed(ActionEvent arg0) {
+                double v = Double.parseDouble(getText());
+                setValue(v);
+            }
+        });
+
+    }
+
+    protected Document createDefaultModel() {
+        return new DoubleTextDocument();
+    }
+
+    public boolean isValid() {
+        try {
+            Double.parseDouble(getText());
+            return true;
+        } catch (NumberFormatException e) {
+            String s = getText();
+            if (! s.endsWith("."))
+                return false;
+            for(int i=0; i<s.length()-1; i++)
+                if (s.charAt(i)<'0' || s.charAt(i)>'9')
+                    return false;
+            return true;
+        }catch(NullPointerException ex) {
+            return true;
+        }
+    }
+
+    public double getValue() {
+        try {
+            return Double.parseDouble(getText());
+        } catch (NumberFormatException e) {
+            return 0;
+        }
+    }
+
+    public void setValue(double zoomFactor) {
+        if (zoomFactor < minNonExp)
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/EntityTree.java

@@ -1,0 +1,337 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jan 2012
+ */
+package com.cisco.mscviewer.gui;
+import com.cisco.mscviewer.model.*;
+
+import java.awt.Color;
+import java.awt.Component;
+import java.awt.event.ActionEvent;
+import java.awt.event.MouseAdapter;
+import java.awt.event.MouseEvent;
+import java.util.ArrayList;
+import java.util.Enumeration;
+import java.util.Vector;
+
+import javax.swing.AbstractAction;
+import javax.swing.JTree;
+import javax.swing.KeyStroke;
+import javax.swing.SwingUtilities;
+import javax.swing.event.TreeModelEvent;
+import javax.swing.event.TreeModelListener;
+import javax.swing.tree.DefaultTreeCellRenderer;
+import javax.swing.tree.TreeModel;
+import javax.swing.tree.TreePath;
+
+class EntityTreeModel implements TreeModel, MSCDataModelListener {
+    private final String root = "Entities";
+    private final Vector<TreeModelListener> listeners;
+    private final MSCDataModel dm;
+
+    public EntityTreeModel(MSCDataModel dm) {
+        this.dm = dm;
+        dm.addListener(this);
+        listeners = new Vector<TreeModelListener>();
+    }
+
+    @Override
+    public Object getRoot() {
+        return root;
+    }
+
+    @Override
+    public Object getChild(Object parent, int index) {
+        if (dm != null) {
+            if (parent == root)
+                return dm.getRootEntityAt(index);
+            else
+                return ((Entity)parent).getChildAt(index);
+        } else
+            return null;
+    }
+
+    @Override
+    public int getChildCount(Object parent) {
+        if (dm != null) {
+            if (parent == root)
+                return dm.getRootEntityCount();
+            else
+                return ((Entity)parent).getChildCount();
+        } else
+            return 0;
+    }
+
+    @Override
+    public boolean isLeaf(Object node) {
+        return (node == root)? false : ((Entity)node).getChildCount() == 0;
+    }
+
+    @Override
+    public void valueForPathChanged(TreePath path, Object newValue) {
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/FilterDialog.java

@@ -1,0 +1,207 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jun 2011
+ */
+package com.cisco.mscviewer.gui;
+
+import javax.swing.JButton;
+import javax.swing.JDialog;
+import javax.swing.JFrame;
+import javax.swing.JPanel;
+import javax.swing.JRadioButton;
+import javax.swing.JScrollPane;
+import javax.swing.JTable;
+import javax.swing.JTextArea;
+import javax.swing.table.DefaultTableModel;
+import javax.swing.table.TableColumnModel;
+
+import javax.swing.JOptionPane;
+import javax.swing.border.EtchedBorder;
+
+import java.beans.*; //property change stuff
+import java.util.Vector;
+import java.awt.BorderLayout;
+import java.awt.GridLayout;
+import java.awt.event.*;
+
+@SuppressWarnings("serial")
+class FilterDialog extends JDialog
+implements ActionListener,
+PropertyChangeListener {
+    private JTable table;
+    private Vector<Vector<String>> filters;
+    private Vector<Vector<String>> tmpFilters;
+    private String btnEnterStr= "Ok";
+    private String btnCancelStr = "Cancel";
+    private boolean approved;
+    JButton add, remove;
+    private Vector<String> columns; 
+    private JOptionPane optionPane;
+
+    public  FilterDialog(JFrame aFrame, Vector<Vector<String>> filters) {
+        super(aFrame, true);
+        setTitle("Filters");
+        this.filters = filters;
+        tmpFilters = new Vector<Vector<String>>();
+        for(int i=0; i<filters.size(); i++) {
+            Vector<String> f = filters.get(i);
+            Vector<String> newF = new Vector<String>();
+            for(int j=0; j<f.size(); j++) {
+                newF.add(f.elementAt(j));
+            }
+            tmpFilters.add(f);
+        }
+
+        JPanel c = new JPanel();
+        c.setLayout(new BorderLayout());
+
+        JTextArea jta = new JTextArea(
+                "Define filters to limit the number of shown events." +
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/FindDialog.java

@@ -1,0 +1,109 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jun 2011
+ */
+package com.cisco.mscviewer.gui;
+
+import java.awt.event.WindowAdapter;
+import java.awt.event.WindowEvent;
+import java.beans.PropertyChangeEvent;
+import java.beans.PropertyChangeListener;
+
+import javax.swing.JDialog;
+import javax.swing.JFrame;
+import javax.swing.JOptionPane;
+
+@SuppressWarnings("serial")
+class FindDialog extends JDialog implements PropertyChangeListener{
+    private JOptionPane optionPane;
+    private final String btnEnterStr= "Ok";
+    private final String btnCancelStr = "Cancel";
+    private boolean approved;
+    private final JScriptPanel jsp;
+
+    public  FindDialog(JFrame aFrame) {
+        super(aFrame, true);
+        setTitle("Find");
+        jsp = new JScriptPanel();
+        jsp.setScriptContext("function filter(label, type) {$$}");
+        Object[] array = {jsp};
+        Object[] options = {btnEnterStr, btnCancelStr};
+
+        //Create the JOptionPane.
+        optionPane = new JOptionPane(array,
+                JOptionPane.PLAIN_MESSAGE,
+                JOptionPane.YES_NO_OPTION,
+                null,
+                options,
+                options[0]);
+
+        //Make this dialog display it.
+        setContentPane(optionPane);
+        //		setDefaultCloseOperation(DO_NOTHING_ON_CLOSE);
+        addWindowListener(new WindowAdapter() {
+            @Override
+            public void windowClosing(WindowEvent we) {
+                /*
+                 * Instead of directly closing the window,
+                 * we're going to change the JOptionPane's
+                 * value property.
+                 */
+                optionPane.setValue(JOptionPane.CLOSED_OPTION);
+            }
+        });
+        //Register an event handler that reacts to option pane state changes.
+        optionPane.addPropertyChangeListener(this);
+        pack();
+    }
+
+    /** This method reacts to state changes in the option pane.
+     * @param e */
+    public void propertyChange(PropertyChangeEvent e) {
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/FindPanel.java

@@ -1,0 +1,110 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  May 2012
+ */
+package com.cisco.mscviewer.gui;
+
+import javax.swing.JButton;
+import javax.swing.JLabel;
+import javax.swing.JPanel;
+
+import com.cisco.mscviewer.expression.ExpressionParser;
+import com.cisco.mscviewer.expression.ParsedExpression;
+import com.cisco.mscviewer.model.ViewModel;
+
+import java.awt.BorderLayout;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+
+@SuppressWarnings("serial")
+class FindPanel extends JPanel {
+    private final MSCRenderer r;
+    public FindPanel(final MSCRenderer r) {
+        this.r = r;
+        setLayout(new BorderLayout());
+        JLabel jl = new JLabel("Find:");
+        add(jl, BorderLayout.WEST);
+
+        JPanel p = new JPanel();
+        p.setLayout(new BorderLayout());
+        add(p, BorderLayout.CENTER);
+        final JButton prev = new JButton("<");
+        final JButton next = new JButton(">");
+        final RuleComponent fc = new RuleComponent();
+
+        p.add(prev, BorderLayout.WEST);
+        p.add(fc, BorderLayout.CENTER);
+        p.add(next, BorderLayout.EAST);
+
+        fc.addActionListener(new ActionListener() {			
+            @Override
+            public void actionPerformed(ActionEvent e) {
+                ParsedExpression expr = fc.getParsedExpression();
+                findNext(expr);
+            }
+        });
+
+        prev.addActionListener(new ActionListener() {
+            @Override
+            public void actionPerformed(ActionEvent e) {
+                ParsedExpression expr = fc.getParsedExpression();
+                findPrev(expr);
+            }
+        });		
+
+        next.addActionListener(new ActionListener() {
+            @Override
+            public void actionPerformed(ActionEvent e) {
+                ParsedExpression expr = fc.getParsedExpression();
+                findNext(expr);
+            }
+        });		
+    }
+
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/HelpFrame.java

@@ -1,0 +1,42 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  May 2012
+ */
+package com.cisco.mscviewer.gui;
+
+import java.io.IOException;
+import java.net.URL;
+
+import javax.swing.JEditorPane;
+import javax.swing.JFrame;
+import javax.swing.JScrollPane;
+
+@SuppressWarnings("serial")
+class HelpFrame extends JFrame {
+    private final JScrollPane scrollPane;  
+    private final JEditorPane editorPane;  
+
+    public HelpFrame(){  
+        setBounds(100, 100, 600, 400);
+        setTitle("MSCViewer Help");
+
+        editorPane=new JEditorPane();  
+        try {  
+            URL url = ClassLoader.getSystemResource("com/cisco/mscviewer/doc/help_home.html");
+            System.out.println("URL: "+url);
+            editorPane.setPage(url);  
+        } catch (IOException e) {  
+            e.printStackTrace();  
+        }  
+
+        scrollPane=new JScrollPane(editorPane);
+        setContentPane(scrollPane);
+    }  
+}

### 2014-10-03 src/com/cisco/mscviewer/gui/JSViewFilter.java

@@ -1,0 +1,36 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jan 2012
+ */
+package com.cisco.mscviewer.gui;
+
+import com.cisco.mscviewer.expression.ExpressionParser;
+import com.cisco.mscviewer.expression.ParsedExpression;
+import com.cisco.mscviewer.model.*;
+
+class JSViewFilter implements MSCDataModelEventFilter {
+    private final boolean filterEvents;
+    private final ExpressionParser exp = new ExpressionParser();
+    private final ParsedExpression expr;
+    private final ViewModel ehm;
+
+    public JSViewFilter(MSCDataModel dm, ViewModel ehm, ParsedExpression e) {
+        this.ehm = ehm;
+        this.expr = e;
+        filterEvents =  (expr != null); // && expr.getFirstToken().toString().equals("event");
+    }
+
+    @Override
+    public boolean filter(Event ev) {
+        return ehm.indexOf(ev.getEntity()) != -1 && 
+        (filterEvents ? exp.evaluateAsJavaScriptonEvent(ev, expr) : true);
+    }
+
+}

### 2014-10-03 src/com/cisco/mscviewer/gui/JScriptPanel.java

@@ -1,0 +1,90 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jun 2011
+ */
+package com.cisco.mscviewer.gui;
+
+import javax.swing.JPanel;
+import javax.swing.JScrollPane;
+import javax.swing.JSplitPane;
+import javax.swing.JTextArea;
+import javax.swing.SwingUtilities;
+import javax.script.*;
+
+import java.awt.BorderLayout;
+import java.awt.Color;
+import java.util.*;
+
+@SuppressWarnings("serial")
+class JScriptPanel extends JPanel {
+    private ScriptEngine engine;
+    private JTextArea scriptTA;
+    private JTextArea errorTA;
+    private Timer t;
+    private String scriptContext;
+
+    public JScriptPanel() {
+        JSplitPane jsp = new JSplitPane(JSplitPane.VERTICAL_SPLIT);
+        setLayout(new BorderLayout());
+        add(jsp, BorderLayout.CENTER);
+        jsp.setResizeWeight(.7);
+        ScriptEngineManager mgr = new ScriptEngineManager();
+        List<ScriptEngineFactory> factories = mgr.getEngineFactories();
+        for (ScriptEngineFactory factory: factories) {
+            String langName = factory.getLanguageName();
+            String langVersion = factory.getLanguageVersion();
+            if (langName.equals("ECMAScript") && 
+                    langVersion.equals("1.6")) {
+                engine = factory.getScriptEngine();
+                break;	
+            }
+        }
+        if (engine == null) {
+            throw new Error("Unable to retrieve JavaScript engine.");
+        }
+        scriptTA = new JTextArea();
+        jsp.setTopComponent(new JScrollPane(scriptTA));
+        errorTA = new JTextArea();
+        errorTA.setForeground(Color.red);
+        errorTA.setEditable(false);
+        jsp.setBottomComponent(new JScrollPane(errorTA));
+
+        TimerTask tt = new TimerTask() {
+            @Override
+            public void run() {
+                SwingUtilities.invokeLater(new Runnable() {
+                    @Override
+                    public void run() {
+                        System.out.println("evaluating script");
+                        try {
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/LogList.java

@@ -1,0 +1,211 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+package com.cisco.mscviewer.gui;
+
+import com.cisco.mscviewer.model.*;
+
+import java.awt.Color;
+import java.awt.Component;
+import java.awt.Dimension;
+import java.awt.Font;
+import java.awt.FontMetrics;
+import java.awt.Graphics;
+import java.awt.event.MouseAdapter;
+import java.awt.event.MouseEvent;
+import java.awt.geom.Rectangle2D;
+import java.util.ArrayList;
+
+import javax.swing.AbstractListModel;
+import javax.swing.DefaultListCellRenderer;
+import javax.swing.JList;
+import javax.swing.JPanel;
+import javax.swing.ListCellRenderer;
+
+/**
+ * @author Roberto Attias
+ * @since  Jun 2011
+ */
+
+@SuppressWarnings("serial")
+class LogListRenderer extends JPanel {
+    private Font f;
+    private FontMetrics fm;
+    private int line;
+    private String text;
+    private final int cnt;
+    private int numWidth;
+    private boolean isSelected;
+    private final Color numBackground = new Color(0xE0E0FF); 
+    private final Color selBackground = new Color(0xD0D0FF);
+
+    public LogListRenderer(int cnt) {
+        this.cnt = cnt;
+    }
+
+    public void setText(String txt) {
+        this.text = txt;
+    }
+
+    public void setNum(int n) {
+        line = n;
+    }
+
+    private void initFontInfo(Graphics g) {
+        f = getFont();
+        fm = g.getFontMetrics(f);
+        Rectangle2D r = fm.getStringBounds(""+cnt, g);
+        numWidth = (int)r.getWidth();
+    }
+
+    @Override
+    public void paintComponent(Graphics g) {
+        super.paintComponent(g);
+        if (f == null)
+            initFontInfo(g);
+        g.setColor(numBackground);
+        g.fillRect(0, 0, numWidth+5, getHeight());
+        g.setColor(Color.black);
+        g.drawString(""+line, 0, fm.getAscent());
+        if (isSelected) {
+            g.setColor(selBackground);
+        } else
+            g.setColor(Color.white);
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/Marker.java

@@ -1,0 +1,41 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jan 2012
+ */
+package com.cisco.mscviewer.gui;
+
+import java.awt.Color;
+
+public enum Marker {
+
+    ERROR(Color.red),
+    RED(Color.red),
+    YELLOW(new Color(0xFFFF99)),
+    BLUE(new Color(0x99FFFF)),
+    GREEN(new Color(0x29FF29));
+
+    private Color transparentColor;
+    private final Color color;
+
+    Marker(Color c) {
+        color = c;
+    }
+
+    public Color getColor() {
+        return color;
+    }
+
+    public Color getTransparentColor() {
+        if (transparentColor == null)
+            transparentColor = new Color(color.getRed(), color.getGreen(), color.getBlue(), 128);
+        return transparentColor;
+    }
+
+}

### 2014-10-03 src/com/cisco/mscviewer/gui/ResultPanel.java

@@ -1,0 +1,145 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jan 2012
+ */
+package com.cisco.mscviewer.gui;
+
+import java.awt.BorderLayout;
+import java.awt.Component;
+import java.awt.Font;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.awt.event.MouseEvent;
+import java.awt.event.MouseListener;
+import java.io.IOException;
+import java.io.StringReader;
+
+import javax.swing.JEditorPane;
+import javax.swing.JMenuItem;
+import javax.swing.JPanel;
+import javax.swing.JPopupMenu;
+import javax.swing.JScrollPane;
+import javax.swing.event.HyperlinkEvent;
+import javax.swing.event.HyperlinkListener;
+import javax.swing.text.BadLocationException;
+import javax.swing.text.Document;
+import javax.swing.text.html.HTMLEditorKit;
+
+import com.cisco.mscviewer.Main;
+import com.cisco.mscviewer.model.Event;
+import com.cisco.mscviewer.model.MSCDataModel;
+
+@SuppressWarnings("serial")
+class ResultPanel extends JPanel implements MouseListener {
+    private final JEditorPane editor;
+
+    public ResultPanel(final MSCDataModel model) {        
+        setLayout(new BorderLayout());
+        Font font = new Font("courier", Font.PLAIN, 12);
+        String CSS = "<style> " +
+        "body { "+
+        "font-family: " + font.getFamily() + "; " +
+        "font-size: " + font.getSize() + "pt; "+
+        "}" +
+        ".match {  color: #00A000; }" +
+        ".mismatch {  color: #FF0000; }" +
+        "</style>";
+        editor = new JEditorPane("text/html", "<html><head>"+CSS+"</head><body>"); 
+        //((HTMLDocument)editor.getDocument()).getStyleSheet().addRule(bodyRule);
+        editor.setEditable(false);
+        editor.addHyperlinkListener(new HyperlinkListener() {
+            @Override
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/RuleComponent.java

@@ -1,0 +1,181 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  May 2012
+ */
+package com.cisco.mscviewer.gui;
+
+import java.awt.AWTKeyStroke;
+import java.awt.KeyboardFocusManager;
+import java.awt.Point;
+import java.awt.Toolkit;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.awt.event.KeyEvent;
+import java.util.ArrayList;
+import java.util.Collections;
+
+import javax.swing.DefaultComboBoxModel;
+import javax.swing.JComboBox;
+import javax.swing.JMenuItem;
+import javax.swing.JOptionPane;
+import javax.swing.JPopupMenu;
+import javax.swing.MutableComboBoxModel;
+import javax.swing.text.BadLocationException;
+import javax.swing.text.Document;
+import javax.swing.text.JTextComponent;
+
+import com.cisco.mscviewer.expression.ExpressionParser;
+import com.cisco.mscviewer.expression.ParsedExpression;
+import com.cisco.mscviewer.expression.ParserState;
+
+@SuppressWarnings("serial")
+class RuleComponent extends JComboBox<String> {
+    final static int HISTORY_SZ = 16; 
+    JTextComponent ed;
+    Document doc;
+
+
+    public RuleComponent() {
+        final MutableComboBoxModel<String> cbm = new DefaultComboBoxModel<String>();
+        setModel(cbm);
+        setEditable(true);
+        ed = (JTextComponent) getEditor().getEditorComponent();
+        ed.setFocusTraversalKeys(
+                KeyboardFocusManager.FORWARD_TRAVERSAL_KEYS, Collections.<AWTKeyStroke> emptySet());
+
+        ed.addKeyListener(new java.awt.event.KeyAdapter() {
+            @Override
+            public void keyPressed(java.awt.event.KeyEvent evt) {
+                if(evt.getKeyCode() == KeyEvent.VK_TAB){
+                    complete();
+                }
+            }});
+
+        doc = ed.getDocument();
+
+        addActionListener(new ActionListener() {			
+            @Override
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/TimeDialog.java

@@ -1,0 +1,171 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jun 2011
+ */
+package com.cisco.mscviewer.gui;
+
+import com.cisco.mscviewer.model.*;import javax.swing.JComboBox;
+import javax.swing.JDialog;
+import javax.swing.JFrame;
+
+import javax.swing.JOptionPane;
+import java.beans.*; //property change stuff
+import java.awt.event.*;
+
+@SuppressWarnings("serial")
+class TimeDialog extends JDialog
+implements ActionListener,
+PropertyChangeListener {
+    //private JTextField tsScaleTf;
+    private final JComboBox<Unit> tsInputUnitCB; 
+    private final JComboBox<Unit>  tsAbsUnitCB; 
+    private JOptionPane optionPane;
+    private final JComboBox<Unit>  tsDeltaUnitCB;
+    private final String btnEnterStr= "Enter";
+    private final String btnCancelStr = "Cancel";
+    private int timeFactor;
+    private boolean approved;
+
+    public  TimeDialog(JFrame aFrame, long initTimeFactor, Unit abs, Unit delta) {
+        super(aFrame, true);		
+        setTitle("Quiz");
+
+        //Create an array of the text and components to be displayed.
+        String tsScaleStr = "Input timestamp unit";
+        //		tsScaleTf = new JTextField(""+initTimeFactor);
+        tsInputUnitCB = new JComboBox<Unit>(Unit.values());
+        String tsAbsUnitStr = "Output absolute time unit";
+        tsAbsUnitCB = new JComboBox<Unit> (Unit.values());
+        tsAbsUnitCB.setSelectedItem(abs);
+        String tsDeltaUnitStr = "Output time-delta unit";
+        tsDeltaUnitCB = new JComboBox<Unit> (Unit.values());
+        tsDeltaUnitCB.setSelectedItem(delta);
+        Object[] array = {tsScaleStr, tsInputUnitCB, tsAbsUnitStr, tsAbsUnitCB, tsDeltaUnitStr, tsDeltaUnitCB};
+
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/mvg/Poly.java

@@ -1,0 +1,53 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Sep 2014
+ */
+package com.cisco.mscviewer.gui.mvg;
+
+import java.awt.geom.Path2D;
+import java.util.ArrayList;
+
+/**
+ *
+ * @author rattias
+ */
+public class Poly extends Primitive {
+    class Point {
+        float x, y;
+        public Point(float x, float y) {
+            this.x = x;
+            this.y = y;
+        }
+    }
+    private final ArrayList<Point> points;
+    
+    public Poly(float x0, float y0) {
+        points = new ArrayList<Point>();
+        points.add(new Point(x0, y0));
+    }
+    
+    public void addPoint(float x, float y) {
+        points.add(new Point(x, y));
+    }
+    
+    @Override
+    public void setContainerDimension(int w, int h) {        
+        Path2D s = new Path2D.Float();
+        boolean first = true;
+        for(Point p: points) {
+            if (first)
+                s.moveTo(p.x*w,p.y*h);
+            else
+                s.lineTo(p.x*w, p.y*h);
+        }
+        setShape(s);
+    }
+    
+}

### 2014-10-03 src/com/cisco/mscviewer/gui/package-info.java

@@ -1,0 +1,13 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * Contains classes for the GUI of MSCViewer. 
+ * @author Roberto Attias
+ * @since  Aug 2014
+ */
+package com.cisco.mscviewer.gui;

### 2014-10-03 src/com/cisco/mscviewer/gui/renderer/FdEventRenderer.java

@@ -1,0 +1,71 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jan 2012
+ */
+package com.cisco.mscviewer.gui.renderer;
+
+import com.cisco.mscviewer.model.JSonObject;
+import java.awt.Color;
+import java.awt.Dimension;
+import java.awt.Graphics2D;
+import java.awt.Rectangle;
+
+public class FdEventRenderer extends EventRenderer {
+    final static int MARGIN=3;
+
+    @Override
+    public void setup(JSonObject props) {
+        super.setup(props);		
+    }
+
+
+    @Override
+    public void render(Graphics2D g2d, Dimension maxDim) {
+        int H = maxDim.height;
+        int W = maxDim.height*2/3;
+        int xs[] = new int[]{
+                0-W/2,
+                0+W/2-W/4,
+                0+W/2,
+                0+W/2,
+                0-W/2,
+                0-W/2};
+        int ys[] = new int[] {
+                0-H/2+MARGIN,
+                0-H/2+MARGIN,
+                0-H/2+MARGIN+H/4,
+                0+H/2-MARGIN,
+                0+H/2-MARGIN,
+                0-H/2+MARGIN				
+        };
+        g2d.setColor(Color.white);
+        g2d.fillPolygon(xs, ys, xs.length);
+        g2d.setColor(Color.gray);
+        g2d.drawPolygon(xs, ys, xs.length);
+        int x0=0-W/2+2;
+        int x1=0+W/2-2;		
+        g2d.setColor(Color.lightGray);
+        g2d.drawLine(x0, 0-3, x1, 0-3);
+        g2d.drawLine(x0, 0, x1, 0);
+        g2d.drawLine(x0, 0+3, x1, 0+3);
+    }
+
+
+    @Override
+    public Rectangle getBoundingBox(Dimension maxDim, int x, int y, Rectangle bb) {
+        if (bb == null)
+            bb = new Rectangle();
+        bb.x = x-maxDim.height/2;
+        bb.y = y-maxDim.height/2+MARGIN;
[…]

### 2014-10-03 src/com/cisco/mscviewer/gui/renderer/LaneRenderer.java

@@ -1,0 +1,179 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jan 2012
+ */
+package com.cisco.mscviewer.gui.renderer;
+
+import com.cisco.mscviewer.gui.Marker;
+import com.cisco.mscviewer.model.JSonObject;
+import com.cisco.mscviewer.model.*;
+
+import java.awt.BasicStroke;
+import java.awt.Color;
+import java.awt.Graphics2D;
+import java.awt.Rectangle;
+import java.awt.Stroke;
+import java.util.HashMap;
+
+public class LaneRenderer extends InteractionRenderer {
+    final static int MAX_LANES = 1280;
+    private static final HashMap<Entity, String[]> hm = new HashMap<Entity, String[]>();
+    private int lane;
+    private final static int LANE_WIDTH = 10;
+    BasicStroke basic, basic2, thickStroke;
+    private final static BasicStroke dashedStroke =  new BasicStroke(1.0f, 
+            BasicStroke.CAP_BUTT,
+            BasicStroke.JOIN_BEVEL, 1.0f,
+            new float[] { 3.0f, 3.0f, 3.0f, 3.0f },
+            0.0f);
+    int[] xp = new int[4];
+    int[] yp = new int[4];
+
+    @Override
+    public void setColor(Color c) {
+    }
+
+    @Override
+    public void setup(JSonObject props, Event ev) {
+        float strokeWidth = 1.0f;
+        if (props != null) {
+            Integer stroke = (Integer)props.get("stroke_width");
+            if (stroke != null)
+                strokeWidth = stroke;
+        }
+        basic = new BasicStroke(strokeWidth);
+        basic2 = new BasicStroke(strokeWidth+2);
+        thickStroke = getBasicStroke((int)strokeWidth+6, false);        
+
+        if (getInteraction().getFromEvent() == ev) {
+            Entity en = ev.getEntity();
+            String lanes[] = hm.get(en);
+            if (lanes == null) {
+                lanes = new String[MAX_LANES];
[…]

### 2014-10-03 src/com/cisco/mscviewer/io/ConfigLoader.java

@@ -1,0 +1,175 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jan 2012
+ */
+package com.cisco.mscviewer.io;
+
+import java.io.File;
+import java.io.IOException;
+import java.text.ParseException;
+
+import javax.swing.JOptionPane;
+import javax.xml.parsers.ParserConfigurationException;
+import javax.xml.parsers.SAXParser;
+import javax.xml.parsers.SAXParserFactory;
+
+import org.xml.sax.Attributes;
+import org.xml.sax.SAXException;
+import org.xml.sax.helpers.DefaultHandler;
+
+import com.cisco.mscviewer.model.MSCDataModel;
+
+@SuppressWarnings("serial")
+class UserAbortException extends SAXException {
+}
+
+public class ConfigLoader {
+    /**
+     * loads a configuration and applies it to the passed model if non-null, or tries
+     * to load the model referred to by the configuration first.  
+     * @param fname
+     * @param mod
+     * @param obs
+     * @return 
+     * @throws java.io.IOException 
+     */
+    public static MSCDataModel load(String fname, MSCDataModel mod) throws IOException {
+        SAXParserFactory factory = SAXParserFactory.newInstance();
+        SAXParser saxParser = null;
+        try {
+            saxParser = factory.newSAXParser();
+        } catch (ParserConfigurationException e1) {
+            throw new IOException(e1);
+        } catch (SAXException e1) {
+            throw new IOException(e1);
+        }
+        final String cfgPath = fname;
+        final MSCDataModel min = mod; 
+
+        DefaultHandler handler = new DefaultHandler() {
+            @Override
+            public void startElement(String uri, String localName,String qName, 
+                    Attributes attributes) throws SAXException {
+                if (qName.equalsIgnoreCase(Config.EL_MSCCONFIG)) {
+                    String logPath = attributes.getValue(Config.ATTR_MSCCONFIG_LOG);
+                    String dateString = attributes.getValue(Config.ATTR_MSCCONFIG_DATE);
+
+                    long t = 0;
+                    try {
+                        t = Config.getTimeSinceEpoch(dateString);
+                    } catch (ParseException e) {
[…]

### 2014-10-03 src/com/cisco/mscviewer/model/Event.java

@@ -1,0 +1,248 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jun 2011
+ */
+package com.cisco.mscviewer.model;
+
+
+import com.cisco.mscviewer.gui.Marker;
+import com.cisco.mscviewer.gui.renderer.DefaultEventRenderer;
+import com.cisco.mscviewer.gui.renderer.EventRenderer;
+
+/**
+ * An <code>Event</code> represents an occurence of relevance for an {@link Entity} within
+ * a data model (see {@link MSCDataModel}.
+ * 
+ * An Event is characterized by a timestamp, a label, a type.
+ * @author rattias
+ */
+public class Event {
+    
+    private MSCDataModel model; /** model the event belongs to */
+    private long timestamp;     /** timestamp when the event occurred */
+    private Entity en;        /** Entity the event belongs to */
+    private int lineIndex;    /** index of the line in the source file this event was generated from */
+    private int index;        /** index of this event within the model */
+    private String ts;        /** cached timestamp representation */
+    private Marker marker;	/** marker this Event is marked with (see {@link Marker}) */
+    private EventRenderer renderer; /** renderer object associated to this event */
+    private String label;     /** label for the Event */
+    private String note;      /** note associated to the Event */
+    private JSonObject data;  /** some data */
+
+    /**
+     * Instantiates an Event with the specified parameters.
+     * @param dm        the {@link MSCDataModel} this Event belongs to
+     * @param timestamp the timestamp the event occurred at
+     * @param en        the {@link Entity} the event belong to 
+     * @param label     the label associated to the event
+     * @param lineIndex the index of the source line this event was generated from
+     * @param renderer  the {@link EventRenderer} associated to the event
+     * @param props     properties for the renderer
+     */
+    public Event(MSCDataModel dm, long timestamp, Entity en, String label, 
+            int lineIndex, EventRenderer renderer, JSonObject props) {
+        if (en == null)
+            throw new NullPointerException("Null entity");
+        model = dm;
[…]

### 2014-10-03 src/com/cisco/mscviewer/model/EventRange.java

@@ -1,0 +1,30 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jun 2011
+ */
+package com.cisco.mscviewer.model;
+
+public class EventRange {
+    private final int fromIdx, toIdx;
+    private final MSCDataModel dm;
+
+    public EventRange(MSCDataModel dm, int fromIdx, int toIdx) {
+        this.dm = dm;
+        this.fromIdx = fromIdx;
+        this.toIdx = toIdx;
+    }
+
+    public int getSize() {
+        return toIdx-fromIdx+1;
+    }
+    public Event getEventAtIndex(int idx) {
+        return dm.getEventAt(fromIdx+idx);
+    }
+}

### 2014-10-03 src/com/cisco/mscviewer/model/JSonObject.java

@@ -1,0 +1,185 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Aug 2014
+ */
+package com.cisco.mscviewer.model;
+
+import com.cisco.mscviewer.io.JSonException;
+import com.cisco.mscviewer.util.JSonParser;
+
+import java.util.ArrayList;
+import java.util.Collection;
+import java.util.HashMap;
+import java.util.LinkedHashMap;
+import java.util.Set;
+
+
+/**
+ * Model element representing a JSon object. 
+ * 
+ * A JSon object is expressed by the grammar shown in {@link http://json.org/}
+ * 
+ * @author rattias
+ */
+public class JSonObject extends Object {
+
+    private HashMap<String, Object> map;
+
+    public JSonObject() {
+        map = new LinkedHashMap<String, Object>();
+    }
+
+    public JSonObject(String str) throws JSonException {
+        this();
+        JSonParser.parseObject(str, this);
+    }
+
+    public static JSonObject parse(String text, String file, int lineNum, int pos) throws JSonException {
+        return JSonParser.parseObject(text, file, lineNum);
+    }
+    
+    public static JSonObject parse(String text) throws JSonException {
+        return parse(text, null, 0, 0);
+    }
+
+    private String toStringInternal(boolean pretty, int indent) {
+        StringBuilder sb = new StringBuilder();
+        sb.append("{ ");
+        for (String k : map.keySet()) {
+            if (pretty) {
+                sb.append('\n');
+                for (int c = 0; c < indent * 2; c++) {
+                    sb.append(' ');
+                }
+            }
+            sb.append('"');
+            sb.append(k);
+            sb.append('"');
+            sb.append(':');
+            Object value = map.get(k);
+            if (value instanceof JSonObject) {
+                JSonObject v = (JSonObject) value;
+                sb.append(v.toStringInternal(pretty, indent + 1));
+            } else if (value instanceof String) {
+                sb.append('"');
+                sb.append(value);
+                sb.append('"');
+            } else {
[…]

### 2014-10-03 src/com/cisco/mscviewer/tree/IntervalTree.java

@@ -1,0 +1,93 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Aug 2014
+ */
+package com.cisco.mscviewer.tree;
+
+import java.util.ArrayList;
+
+/**
+ *
+ * @author rattias
+ */
+public class IntervalTree extends AVLTree {
+    public static boolean dbg = false;
+    
+    public ArrayList<Interval> getIntervalsWithEndBound(int c) {
+        ArrayList<Interval> els = new ArrayList<Interval>();
+        getIntervalsWithEndBound(c, els);
+        return els;
+    }
+
+    public ArrayList<Interval> getContainingIntervals(int c) {
+        ArrayList<Interval> els = new ArrayList<Interval>();
+        if (root != null)
+            ((IntervalTreeNode)root).getContainingIntervals(c, els);
+        return els;
+    }
+    
+    public void getContainingIntervals(int c, ArrayList<Interval> ret) {
+        if (root != null)
+            ((IntervalTreeNode)root).getContainingIntervals(c, ret);        
+    }
+
+    public ArrayList<Interval> getIntersectingIntervals(int start, int end) {
+        ArrayList<Interval> els = new ArrayList<Interval>();
+        if (root != null)
+            ((IntervalTreeNode)root).getIntersectingIntervals(start, end, els);
+        return els;
+        
+    }
+
+    public void getIntersectingIntervals(int start, int end, ArrayList<Interval> ret) {
+        if (root != null)
+            ((IntervalTreeNode)root).getIntersectingIntervals(start, end, ret);
+    }
+    
+    public void getIntervalsWithEndBound(int c, ArrayList<Interval> ret) {
+        Interval o = (Interval)find(c);
+        if (o != null) {
+            ret.add(o);
+        }
+    }
+    
+    public void getIntervalsWithStartBound(int  c, ArrayList<Interval> ret) {
+        if (root != null)
+            ((IntervalTreeNode)root).getIntervalsWithStartBound(c, ret);
+    }
+    
+    public void verifyIntegrity() throws TreeIntegrityException {
[…]

### 2014-10-03 src/com/cisco/mscviewer/tree/IntervalTreeNode.java

@@ -1,0 +1,316 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Aug 2014
+ */
+package com.cisco.mscviewer.tree;
+
+import com.cisco.mscviewer.model.Interaction;
+
+import java.io.FileWriter;
+import java.io.IOException;
+import java.util.ArrayList;
+
+/**
+ *
+ * @author rattias
+ */
+public class IntervalTreeNode extends AVLTreeNode {
+    public static boolean debugging = false;
+    private int  minStart;
+    
+    public IntervalTreeNode(Interval el) {
+        super(el);
+        minStart = el.getStart();
+        
+    }
+    
+    
+    @Override
+    public void add(AVLTreeNode tn) { 
+        super.add(tn);
+        fixMinStart();
+    }
+    
+
+    private void fixMinStart() {
+        Interaction in = (Interaction)data;
+        minStart = Integer.MAX_VALUE;
+        if (left != null && minStart > ((IntervalTreeNode)left).minStart)
+            minStart = ((IntervalTreeNode)left).minStart;
+        if (right != null && minStart > ((IntervalTreeNode)right).minStart)
+            minStart = ((IntervalTreeNode)right).minStart;
+        int  st = in.getStart();
+        if (st >= 0 && minStart > st)
+            minStart = st;
+    }
+
+    protected void fixMinStartRecursive() {
+        if (left != null)
+            ((IntervalTreeNode)left).fixMinStartRecursive();
+        if (right != null)
+            ((IntervalTreeNode)right).fixMinStartRecursive();
+        fixMinStart();
+    }
+    
+    @Override
+    protected void balance() {
+        super.balance();
+        fixMinStart();
+    }
+    
+
+    @Override
+    protected void rotateLL() {        
+        super.rotateLL();
+        fixMinStartRecursive();
+    }
+    @Override
+    protected void rotateLR() {
+        super.rotateLR();
+        fixMinStartRecursive();        
+    }
+    
+    @Override
+    protected void rotateRR() {
+        super.rotateRR();
+        fixMinStartRecursive();    
+    }
+    @Override
+    protected void rotateRL() {
+        super.rotateRL();
[…]

### 2014-10-03 src/com/cisco/mscviewer/util/PNGSnapshotTarget.java

@@ -1,0 +1,19 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jan 2012
+ */
+package com.cisco.mscviewer.util;
+
+import java.awt.Component;
+
+public interface PNGSnapshotTarget {
+    Component getPNGSnapshotClient();
+    String getName();
+}

### 2014-10-03 src/com/cisco/mscviewer/util/Utils.java

@@ -1,0 +1,209 @@
+/*------------------------------------------------------------------
+ * Copyright (c) 2014 Cisco Systems
+ * All rights reserved. This program and the accompanying materials
+ * are made available under the terms of the Eclipse Public License v1.0
+ * which accompanies this distribution, and is available at
+ * http://www.eclipse.org/legal/epl-v10.html
+ *------------------------------------------------------------------*/
+/**
+ * @author Roberto Attias
+ * @since  Jan 2012
+ */
+package com.cisco.mscviewer.util;
+
+import java.awt.Component;
+import java.awt.Container;
+import java.awt.Rectangle;
+import java.awt.image.BufferedImage;
+import java.io.File;
+import java.io.IOException;
+import java.lang.reflect.InvocationTargetException;
+import java.util.ArrayList;
+import java.util.HashSet;
+
+import javax.imageio.ImageIO;
+import javax.swing.JFileChooser;
+import javax.swing.SwingUtilities;
+
+import com.cisco.mscviewer.gui.MainFrame;
+
+public class Utils {
+    private static final HashSet<String> en = new HashSet<String>(); 
+    private static final boolean tracing = false;
+    public final static String EVENTS = "events";
+    public static JFileChooser jfc;
+
+
+    public static void setEnabled(String cl, boolean enabled) {
+        if (enabled)
+            en.add(cl);
+        else
+            en.remove(cl);
+    }
+
+    public static void trace(String group, String msg) {
+        if (tracing) {
+            StackTraceElement[] frames = Thread.currentThread().getStackTrace();
+            int cnt;
+            for(cnt=2; cnt<frames.length; cnt++) {
+                if (! frames[cnt].getClass().getPackage().getName().startsWith("com.cisco"))
+                    break;
+            }
+            String ind = "                                                                                            ".substring(2, cnt);
+            String cl = frames[2].getClassName();
+            cl = cl.substring(cl.lastIndexOf('.')+1);
+            String m = frames[2].getMethodName();
+            if (en.contains(group))
+                System.out.println(ind+cl+"."+m+":"+msg);
+        }
+    }
+
+    public static void dispatchOnAWTThreadNow(Runnable r) {
+        if (SwingUtilities.isEventDispatchThread())
+            r.run();
+        else
+            try {
+                SwingUtilities.invokeAndWait(r);
+            } catch (InterruptedException e) {
+                // TODO Auto-generated catch block
+                e.printStackTrace();
+            } catch (InvocationTargetException e) {
[…]

### 2015-04-01 doc/manual/manual.tex
modifications

\documentclass[11pt, twoside, titlepage]{book}
\usepackage[hcentering,textwidth=150mm,textheight=225mm]{geometry}
\usepackage[Bjornstrup]{fncychap}
\usepackage{graphicx}
\usepackage[colorlinks=true, 
            urlcolor=blue]{hyperref}
\usepackage{mathtools} 
\usepackage{makeidx}
\makeindex

%\usepackage[margin=1in]{geometry}
\usepackage{fixltx2e} 
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{centernot}
\usepackage{listings}
\usetikzlibrary{shadows}
\usepackage[toc,page]{appendix}
\usepackage{breakurl}
\usepackage{wrapfig}
\usepackage{tcolorbox}
\usepackage{lipsum}
\include{titlepage}

\newcommand{\prog}{MSCViewer} 
\newcommand{\eventprefix}{\texttt{@msc}}
\newcommand{\mscevent}{\texttt{@msc\_event}}
\newcommand{\naive}{ na\"{\i}ve}
\newcommand{\closebutton}{\includegraphics[height=.7\baselineskip]{../../src/com/cisco/mscviewer/resources/icons/16x16/close1.png}}
\newenvironment{Sidebar}[1][r]
  {\wrapfigure{#1}{0.5\textwidth}\tcolorbox}
  {\endtcolorbox\endwrapfigure}

\newcommand*\keystroke[1]{%
  \tikz[baseline=(key.base)]
    \node[%
      draw, 
      fill=white,
      drop shadow={shadow xshift=0.25ex,shadow yshift=-0.25ex,fill=black,opacity=0.75},
      rectangle,
      rounded corners=2pt,
      inner sep=1pt,
      line width=0.5pt,
      font=\scriptsize\sffamily
    ](key) {#1\strut}
  ;
}

\newcommand{\todo}[1]{\textit{#1}}
\newcommand{\defterm}[1]{\textit{#1}\index{#1}}

%\title{\prog{} v1.0} \author{ Roberto Attias  \\
%    User Manual
%    }
\date{\today}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{lightcyan}{rgb}{0.83,0.97, 1}

\lstset{frame=tb,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=left,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{mauve},
  stringstyle=\color{dkgreen},
  backgroundcolor=\color{lightcyan},
  frame=shadowbox,
  xleftmargin=2em,
  framexleftmargin=1.5em, 
  rulesepcolor=\color{gray},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3,
  escapeinside={(*}{*)}
}

\makeatletter
\renewcommand\tableofcontents{%
    \if@twocolumn
      \@restonecoltrue\onecolumn
    \else
      \@restonecolfalse
    \fi
    \chapter*{\contentsname}%
        \@mkboth{%
           \MakeUppercase\contentsname}{\MakeUppercase\contentsname}%
    \@starttoc{toc}%
    \if@restonecol\twocolumn\fi
    }
\makeatother

\titleGM

\begin{document}
%\maketitle
\clearpage
\thispagestyle{empty}

\tableofcontents

\cleardoublepage

\setcounter{page}{1}
% Hint: \title{what ever}, \author{who care} and \date{when ever} could stand 
% before or after the \begin{document} command 
% BUT the \maketitle command MUST come AFTER the \begin{document} command! 
%\maketitle

\chapter{Introduction}

\section{\prog}
\prog{} is a tool supporting visualization and analysis of message sequence
charts. The tool loads a text file, interprets lines containing the
\eventprefix{} qualifier and representing events and interactions occurring on
entities, ignoring other lines. From the interpreted lines a model is
constructed in memory. In the GUI the tool can visualize the list of enties,
from which the user can select a subset to be shown in a sequence diagram chart.
through keyboard or mouse commands the user can easily navigate through events
and interactions, search, and perform a number of other actions for browsing the
diagram.

In a design phase the user can write a concise description of one or
more flows in the inpujt language,load it in the tool, and export an image to 
be used for documentation.

By instrumenting certain point in the program or application with syslogs,
printf, traces or any other mechanism avaliable, the user can generate run the
application and generate the input file for \prog{}. In this case the input
file contains flows corresponding to actual executions, which could be visually
inspected for verification.

Visual inspection of flows from execution logs is useful, but doesn't scale for
debugging, as it requires a human operator familiar with the expected flows.
When applications are large enough, their development might be distributed
across multiple teams, with only few members fully aware of cross-component
flows. To address this problem \prog{} is integrated with a Python interpreter
and supports execution of scripts which can browse the model and perform any
sort of validation. In addition, a set of classes is provided to support a
concise description of expected flows. With these mechanism the user can create
validation script to be executed in the tool on the model created from execution
logs, automatically validating their correctness. Scripts can also be executed
from command line, without any GUI visualization, supporting batch validations
and product smoke-testing.

\section{Message Sequence Charts and Flows}
A large class of products and application is composed by multiple concurrent
entities. For example a web application may be composed by a front-end running
in a browser, a backend web server and a database. The user interacts with the 
frontend, which in turn interacts with the backend. The backend interacts with
the database. We refer to elements involved in the interactions as 
\defterm{Entities}, and the sequence of interactions among entities required to
perform a functionality as \defterm{Flow}.

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{simple-flow.png}
  \caption{A simple flow example}
  \label{fig:simple-flow} 
\end{figure}

Fig~\ref{fig:simple-flow} shows, as an example, the flow involving a user
logging into a server which stores users information in a database. 
In complex concurrent system multiple homogeneous or heterogeneous flows
spawning tens or hundreds of entities may be in execution at any point in time.

When designing, implementing and debugging such a complex system flows play a
very important role in the entire development cycle.

In the design phase is fairly common to represent expected flows in a design
document through some variation of Message Sequence Charts
\footnote{for more information on Message Sequence Chart see~
\href{http://en.wikipedia.org/wiki/Message\_sequence\_chart}
{http://en.wikipedia.org/wiki/Message\_sequence\_chart}}, such as the one shown
in fig~\ref{fig:simple-flow}.

In the implementation phase the developer can sprinkle calls to a
tracing/logging \footnote{ for more information about tracing vs.
logging
see~\href{http://en.wikipedia.org/wiki/Tracing\_(software)}
{http://en.wikipedia.org/wiki/Tracing\_(software)}} infrastructure
around the main points of flows.

At debug time
the user can then browse the various log files and mentally reconstruct and
verify flows. If not properly supported by a tool this exercise can be complex
and time-consuming, as the user has to reassemble flows identifying relevant
information often diluted in hundreds of lines of unrelated logs. To add to this
complexity, flows may not always be purely sequential like the one shown in
fig~\ref{fig:simple-flow}.

For example, fig~\ref{fig:concurrent-flow} shows a user requesting the
instantiation of a virtual machine to an hypotetical VM Manager. the VM Manager
requests asynchrously resources (disk space, CPU, memory) to a Resource Manager
and an image for the VM to a VM Repository. When the resources and VM image are
provided, VM Manager spawns the VM.

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{concurrent-flow.png}
  \caption{A flow with two concurrent branches}
  \label{fig:concurrent-flow} 
\end{figure}

Note that the flow could also happen in different ways. For example, 
the response from the Image Repo could reach VM Manager before the response from
the Resource Manager. The implication of this consideration is that verifying
whether a flow happened as expected doesn't always amount to simply checking
whether certain string appear in a specific total order in the logs. Sometimes
events (i.e. log lines) have only a partial order, or some parts may be
optional, for example in case of an \textit{if} vs. \textit{else} branch taken 
in the code.

Capturing flows at design time is very
important to properly document how a system composed by multiple concurrent
elements operate. Validating flows in logs of runtime executions is crucial to
guarantee a complex system is operating as expected. \prog{} was designed  to
support this.

%\section{Tracing and Logging}
%\prog{} Accepts in input is either hand written to capture a desired flow at design time,
%case the program has produced information through some infrastructure
%or generated by running code, to capture an actual execution. In the latter
%The definition of tracing and logging are not always

\section{History and Acknowledgements}
Work on \prog{} was started around 2010 at CISCO. The idea was to develop a tool
for usage during development of the control plane for the NCS-6000, CISCO 
last-generation core router, specifically to address the problem of
automatically identifying potential problems in flows and reducing the triaging 
time and amount of resources required. While the tool was started as a personal
initiative, it has found good adoption by some communities in the company.

Before 2010, I had worked on other tools with some common aspects, so \prog{} can
be considered the result of an effort started around 2001 
(no code or IP from those early efforts has been used in \prog{}).

As of Sept. 2014 CISCO has gracefully consented to release \prog{} in the
open-source.

I want to thank the following people for their ideas, suggestions, feedback and
support during development of \prog{}:

\begin{itemize}
\item Akash Deshpande and Marco Zandonadi, whose collaboration in CISCO and before
has helped shaping \prog{} to its current form;

\item Edward Conger, for his suggestions, observation and his ability to push
the boundary of \prog{} and other tools I developed;

\item the CISCO managment, in particular Sunil Khaunte, Feisal Daruwalla, Satish
Gannu, Sohyong Chong and Robert Krohn, for their support during the developement
of \prog{} and for facilitating its release as open source.
\end{itemize}

\chapter{Getting Started} 
In this chapter we will start familiarizing with \prog{} concepts through some
examples. The files used in the examples are located in the \texttt{examples/}
directory of the distribution.

\section{Your First Sequence Diagram}
The following is a simple input file for \prog{}:
\lstinputlisting{../../examples/lst1.msc}
Each line defines an \defterm{event}, i.e. an occurrence of something relevant
in an entity. The syntax consists in the \mscevent{} token followed by a JSON
object (see \href{http://json.org/}{http://json.org/} for more information about the JSON format).

Line 1 defines a \defterm{local} event, which is not part of any interaction
with other entities. The value of the \texttt{entity} key indicates the entity
this event belongs to. There is no explicit sytax to define an entity: as it
parses events, \prog{} creates entities the events belong to.

Line 2 defines an event which is part of an interaction. More specifically, this
event is the \defterm{source} (or \defterm{cause}) for the interaction, as
indicated by the presence of the \texttt{src} key. Line 3 defines a
\defterm{destination}, or \defterm{effect}, as indicated by the presence of the
\texttt{dst} key. An interaction is an ordered pair composed by a cause and an
effect event.

\section{Running \prog}

We can now start \prog{} with this input file. Assuming the current directory is
the top directory of the  distribution, run:

\begin{lstlisting}
bin/(*\MakeLowercase{\prog}*) examples/lst1.msc
\end{lstlisting}

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex1.png}
  \caption{\prog{} GUI with \texttt{lst1.msc} loaded.}
  \label{fig:gui-lst1}
\end{figure}

Fig.~\ref{fig:gui-lst1} shows the GUI in its initial state.  The bottom-right
area shows the the input file, while the top-left tree shows the various
entities. Double-click on the \texttt{producer} and \texttt{consumer} entities
to open them in the diagram area, in the top-right part of the window
(fig.~\ref{fig:gui-lst1-open}). Each entity is shown in a column, with events
interleaving each other across entities. Columns can be sorted by dragging them
from their header (the part showing the entity name), and closed by clicking on
the   \closebutton{} button. Clicking on an event selects it; the selection can
be moved to the previous/next event for an entity by pressing respectively the
\keystroke{SHIFT} \keystroke{$\uparrow$} and \keystroke{SHIFT}
\keystroke{$\downarrow$} key combinations. To navigate from a source or
destination event to the paired event in an interaction use the 
\keystroke{SHIFT} \keystroke{$\leftarrow$} or \keystroke{SHIFT} \keystroke{$\rightarrow$}.

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex1-open.png}
  \caption{The user has opened all the entities in the diagram}
  \label{fig:gui-lst1-open}
\end{figure}

Try closing the \texttt{consumer} entity by clicking on the \closebutton{}
button. As the destination entity is now closed, the interaction outgoing from
the producer is shown as an arrow stub. In this case, it is pretty obvious who the
destination entity is, but in more complex scenarios there can be hundreds of
entities, and it wouldn't be easy to know which one to open from the entities tree. In
this situation the keyboard navigation cames handy. Select the interaction stub,
then press \keystroke{SHIFT} \keystroke{$\rightarrow$}: ``pushing'' on the
tip/base of an interaction stub for which the destination/source entity is not
open causes the entity to be opened.

\section{Topological Sorting}
In the diagram in fig.~\ref{fig:gui-lst1-open} events appear in the 
same order in which they were in the file. However, this is not always
the case. Select the \texttt{File/Open...} menu item, and from the file
selection widget open the \texttt{lst2.msc} file. As shown in the input area,
this file is the same as \texttt{lst1.msc}, except that the last two lines have
been swapped. Despite the fact that the destination for the interaction is
listed before the source, opening the two entities will show the same diagram as
before: \prog{} tries to preserve cause-effect ordering among events by applying
a topological sort to the events as they're loaded. It is possible to write
input files with create circular dependencies of events, resulting in the
impossibility of performing a topological sorting. In this case \prog{} reports
an error upon loading the file and skips the sorting. This case is captured in
\texttt{lst3.msc}, shown in fig.~\ref{fig:gui-lst3}

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex3-cycle.png}
  \caption{Diagram with circular dependencies caused by interactions}
  \label{fig:gui-lst3}
\end{figure}

\section{Timestamps}
It is possible to associate timestamps to each event throught the \texttt{time}
key. The value can assume different formats, as shown in \texttt{lst4.msc},
visible in fig.~\ref{fig:gui-lst4}. \prog{} internally converts the units
indicated in the input files into nanoseconds. By default timestamps are shown
to the left of events in a \texttt{hh:mm:ss} format. The format can be changed
through the \texttt{view/Preferences...} menu item.

%\lstinputlisting[language=Java]{../../examples/lst4.msc}
\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex4-time.png}
  \caption{Diagram with timestamps associated to events.}
  \label{fig:gui-lst4}
\end{figure}

\section{Associating Data to Events}
To associate some data to an event, use the \texttt{data} key. The value is a
JSON object that will be visualized in the bottom-right area, in the
\texttt{Data} tab. For example, loading the following input file  and selecting
the third event results in the screen as shown in fig.~\ref{fig:gui-lst5}:

\begin{minipage}{\linewidth} 
\lstinputlisting{../../examples/lst5.msc}
\end{minipage}

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex5-data.png}
  \caption{The Data view showing data associated to the selected event}
  \label{fig:gui-lst5}
\end{figure}

\section{Orphaned Interactions}
When collecting traces from a system it is possible that either the even
representing a cause or the one representing an effect for an interaction goes
missing. This can be caused by multiple reasons, such as the fact that a trace
has wrapped around (typically traces don't grow indefinitely, but rather wrap
around, loosing older information), or that traces for one of the two entity
involved in the interaction are not available. We will refer to interactions for
which only one of the two events is available as \defterm{Orphaned
Interactions}.
\prog{} visualizes orphaned interactions as dashed arrow stubs outgoing or
incoming into the only available event.

\chapter{\prog{} Model}
This chapter provides a more formal definition of the \prog{} model.

\section {Entity}
An \defterm{entity} is an autonomous execution entity such as a thread or state
machine. In MSCViewer entities can be defined hierarchically. For example, in a
router a node entity might contain a process entity, containing  a thread
entity, containing a state machine entity. An entity is characterized by a name,
a unique ID and a set of events. The ID of an entity is composed by the ID of
the parent, a slash (\texttt{/}) and an identifier. In other words, entity IDs
have a namespace similar to a filesystem path.
Let's consider the example shown in table~\ref{tab:entities}:

\begin{center}
    \begin{table}[h]
    \centering
    \label{tab:entities}
    \begin{tabular}{ | l | l | l | l |}
    \hline
    ID & Name\\ 
    \hline
    0       & Node0 \\  
    1       & Node1 \\  
    0/1234  & Node0/DS \\
    0/1236  & Node0/DS \\
    1/1234  & Node1/DS \\
    \hline
    \end{tabular}
    \caption{Example of entities}
    \end{table}
\end{center}

Here we have two nodes, named \texttt{Node0} and \texttt{Node1}. The entity IDs
are respectively 0 and 1, while their names are \texttt{Node0} and
\texttt{Node1}.

On the first node two processes are running, the first with PID
1234, the second with PID 1236. The IDs for the corresponding entities are
\texttt{0/1234} and \texttt{0/1236}. The processes are instances of the same
executable called DS, so the entity names are \texttt{Node0/DS} and
\texttt{Node0/DS}.

On the second node a single instance of \texttt{DS} is running, with ID
\texttt{1/1234} and name \texttt{Node1/DS}

It's worth mentioning that \prog{} does not have any semantic knowledge of
concept such as nodes, processes, or threads, and the model could be used to
represent any kind of problem domain. \prog{} understands only the concept of
hyerarchical IDS and names where elements in the hyerarchy are separated by
slashes.

Some entities can have an extra attribute characterizing them as clock sources.
This indicates that the entity and all its descendants are on
the same clock domain, hence sharing the same clock. As an example, a group of
computational nodes may have a shared system clock (via software or dedicated
hardware), in which case a system root entity could be used to represent this.
In other scenarios a set of nodes may have a loose clock synchronization (for
example via NTP), in which case entities representing nodes could be clock
sources for children representing processes running on the node.

\section {Event} 
An event is an occurrence of some relevance happening to an entity. Examples of
event are the state transitions in state machines or receiving or sending a
message. An event is always characterized by a timestamp, a label, and a type.
The timestamp is relative to the clock source the entity belongs to. The label is a
human-readable message providing information about the event. They type is an
identifier representing formally the specific type of the event, used for
example to select how to visually render the event in the sequence diagram 
(see~\ref{sec:rendering}). In addition to these mandatory attributes, an event
may have a dictionary of extra attributes. Rendering code or model browsing code can retrieve these
attribute to perform special tasks.

\subsection{Events Partial Order}
\label{events-partial-order}
Theoretically all events within an clock domain are fully ordered in a
``happened-before'' relationship by their timestamp. In reality however high
event granularity, low clock resolution, or the presence of multiprocessing capabilities can result in
multiple events with the same timestamp. For example a trace may
have been generated for a computational node where have two processes have an
event happening exactly at the same timestamp. This means that model events are
a \href{http://en.wikipedia.org/wiki/Partially_ordered_set}{Partially Ordered
Set} where $ev_i < ev_j$ if at least one of the following conditions is true:

\begin{itemize}
  \item $ev_i$ and $ev_j$ belong to the same clock domain and $t(ev_i) <
   t(ev_j)$
   \item  $\exists$ an interaction $I$ such that $(ev_i \rightarrow ev_j)$ 
   \item $\exists ev_1\ldots ev_n$ such that $ev_1=ev_i,\quad ev_n=ev_j,\quad
   ev_k<ev_{k+1} \quad \forall k \in (1 \ldots n-1)$
\end{itemize}

Upon parsing the model from the input file MSCViewer applies the Kahn 
\href{http://en.wikipedia.org/wiki/Topological_sorting}{topological sorting
algorithm} according to the partial order specified above. In the algorithm
however the set $S$ set is replaced with a FIFO where elements are added in the
order in which they are defined in the input file. This, and the assumption that
the input file was sorted on timestamps, guarantees that events with the same
timestamp and no incoming edges in the graph will not be shuffled around.

The sorted events output by the algorithm are stored in an array which reflects
the visualization order.

The topological sorting is particularly useful when the input data is produced
by entities with different clock sources. For example, an input file may be
produced by joining traces collected on two separate Linux nodes. Even when
nodes are synchronized through NTP, there may be a small drift resulting in the
tracing of a source event having a timestamp larger than the corresponding to
the tracing of the destination event. A simple merging of the two traces based
on timestamp would produce a model where cause and effect are in the opposite
order (with the arrow representing the interaction going from bottom to top).
The topological sorting takes care of this problem. Note that the timestamps
associated to the events are not modified, hence while the arrow flows from top
to bottom, the source will still show up with a timestamp greater than the
destination. Computing the actual offset between the two nodes is not trivial
if not impossible, and anyway correcting the timestamp may confuse the user.

\section {Interaction}

An interaction is a tuple $(ev_i, ev_j, type)$ where:
\begin{itemize}
  \item $ev_i$ is called the {\it source} or {\it cause} event, and the entity
  the event belongs to is called the {\it source entity};
  \item $ev_j$ is called the {\it destination} or {\it effect} event, and the
  entity the event belongs to is called the {\it destination entity}
  \item $type$ is an identifier characterizing the nature of the interaction
  (for example \texttt{message}, or \texttt{creation})
\end{itemize}
In the model adopted interaction implies a causality between the source and
destination event, hence $(ev_i, ev_j, T) \centernot\implies (ev_j, ev_i, T)$.

Note also that the model allows source and destination event to belong to the
same entity.

An example of interaction type is a message-passing. In this case the source
event captures the sending of the message, while the destination event captures
the reception. Another example is a state machine instantiation:
in this case the creating entity would have an ``sm instantiation'' event, while
the created state machine would have a first event corresponding to its birth.
In this case, clearly, the state machine entity would be a children of the
creator entity. An example where source and destination events belong to the
same entity is initiation and completion of a DMA operation. 
Note that the model allows for additional events
to be present between the source and destination event for an interaction.

In the model interactions are captured with an interaction ID attribute
associated to the source and destination events. This attribute has the same
value (a unique id) for events belonging to the same  interaction.

The model allows for an event to be the source of multiple interactions, but
the destination to only one interaction. events with multiple outgoing
interaction can be used, for example, to capture multicast messaging.

In this document we will in some cases use the notation $(A_{e_1} \rightarrow
B_{e_2})$ to represent an interaction between an event $e_1$ on entity $A$ and
an event $e_2$ on entity $B$

\section{Input Language}
\prog{} can load a single file containing description of events for multiple
entities and build a model in memory. The input file is composed by lines of
text. \prog{} ignores any line not containing the \texttt{@msc\_event} or
\texttt{@msc\_entity} word. This allows to load trace files which might contain
a mix of trace lines catered to \prog{} and unrelated trace lines.

An event is described in the input language by a line containing the
\texttt{@msc\_event} followed by a JSON object. If the reader is not familiar
with this format, it is explained here: \href{http://json.org/}{http://json.org/}

\chapter{\prog{}  GUI}

\chapter{Customizing \prog}
\section{Icons}
\section{Python Scripts}

\chapter{Flow Definition}
\section{Introduction}
\prog{} provides a powerful infrastructure supporting automated flow validation.
This means that a developer can write once a concise Python script describing an expected flow,
and apply such definition to models built from traces generated a runtime by a system. This
is the basis for flow-level verification automation, which is crucial to scale at least the first
level of triaging for a system.

\section{Your First Flow Definition}
The following is a simple flow-definition script:
\lstinputlisting{../../examples/flw1.py}

\appendix
\section{Useful Links}
\begin{tabular}{l l p{9.0cm}}

\end{tabular}

\printindex

\end{document}

### 2015-04-03 doc/manual/mscviewer.tex
Added a lot more info in manual Images for manual are now automatically generated running tool in batch improved build system added generation of html manual

--- 2015-04-01 doc/manual/manual.tex
@@
 \usepackage{mathtools} 
+\usepackage{longtable}
 \usepackage{makeidx}
@@
 \usepackage[toc,page]{appendix}
-\usepackage{breakurl}
+\usepackage{etoolbox}
 \usepackage{wrapfig}
@@
 \newcommand{\prog}{MSCViewer}
-\newcommand{\eventprefix}{\texttt{@msc}}
-\newcommand{\mscevent}{\texttt{@msc\_event}}
+
+\newcommand{\mscevent}{\texttt{@event}}
+\newcommand{\mscentity}{\texttt{@entity}}
 \newcommand{\naive}{ na\"{\i}ve}
-\newcommand{\closebutton}{\includegraphics[height=.7\baselineskip]{../../src/com/cisco/mscviewer/resources/icons/16x16/close1.png}}
+\newcommand{\closebutton}{\includegraphics[height=.7\baselineskip]{images/close1.png}}
+\newcommand{\tblimg}[1]{\raisebox{-.5\height}{\includegraphics[height=.2in]{#1}}}
+
 \newenvironment{Sidebar}[1][r]
@@
 \makeatletter
-\renewcommand\tableofcontents{%
+\renewcommand\tableofcontents{
     \if@twocolumn
@@
 
-\tableofcontents
+\include{tocnotoc}
 
@@
 charts. The tool loads a text file, interprets lines containing the
-\eventprefix{} qualifier and representing events and interactions occurring on
+\mscevent{} or \mscentity{} keywords and representing events and interactions occurring on
 entities, ignoring other lines. From the interpreted lines a model is
@@
   \centering
-  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{simple-flow.png}
+  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/simple-flow.png}
   \caption{A simple flow example}
@@
   \centering
-  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{concurrent-flow.png}
+  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/concurrent-flow.png}
   \caption{A flow with two concurrent branches}
@@
 Line 1 defines a \defterm{local} event, which is not part of any interaction
-with other entities. The value of the \texttt{entity} key indicates the entity
+with other entities. The value of the \mscentity{} key indicates the entity
 this event belongs to. There is no explicit sytax to define an entity: as it
@@
   \centering
-  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex1.png}
+  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/gui-ex1.png}
   \caption{\prog{} GUI with \texttt{lst1.msc} loaded.}
@@
 Fig.~\ref{fig:gui-lst1} shows the GUI in its initial state.  The bottom-right
-area shows the the input file, while the top-left tree shows the various
+area shows the content of the input file, while the top-left tree shows the various
 entities. Double-click on the \texttt{producer} and \texttt{consumer} entities
@@
   \centering
-  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex1-open.png}
+  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/gui-ex2-open.png}
   \caption{The user has opened all the entities in the diagram}
@@
   \centering
-  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex3-cycle.png}
+  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/gui-ex3-cycle.png}
   \caption{Diagram with circular dependencies caused by interactions}
@@
   \centering
-  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex4-time.png}
+  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/gui-ex4-time.png}
   \caption{Diagram with timestamps associated to events.}
@@
   \centering
-  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex5-data.png}
+  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/gui-ex5-data.png}
   \caption{The Data view showing data associated to the selected event}
@@
 entities and build a model in memory. The input file is composed by lines of
-text. \prog{} ignores any line not containing the \texttt{@msc\_event} or
-\texttt{@msc\_entity} word. This allows to load trace files which might contain
+text. \prog{} ignores any line not containing the \mscevent{} or
+\mscentity{} word. This allows to load trace files which might contain
 a mix of trace lines catered to \prog{} and unrelated trace lines.
@@
 An event is described in the input language by a line containing the
-\texttt{@msc\_event} followed by a JSON object. If the reader is not familiar
+\mscevent{} followed by a JSON object. If the reader is not familiar
 with this format, it is explained here: \href{http://json.org/}{http://json.org/}
 
+\prog interprets certain keys-value pairs in the JSON objects in order to build
+the entity/event/interaction model.
+
+For events, the following keys are interpreted:
+
+\begin{center}
+    \begin{longtable}{ll}
+    \hline
+    \textbf{Key:}         & \texttt{entity} \\
+    \textbf{Type:}        & String \\
+    \textbf{Mandatory:}   & y\\
+    \textbf{Example:}     & \texttt{"id":"node0/producer\_1"}\\
+    \textbf{Description:} &
+    \begin{minipage}[t]{0.8\columnwidth}%
+        an identifier for the entity this event belongs to. identifiers can contain slash to indicate hierarchy of entities.\\
+    \end{minipage}    
+    \tabularnewline
+    \hline
+    \textbf{Key:}         & \texttt{label} \\
+    \textbf{Type:}        & String \\
+    \textbf{Mandatory:}   & y\\
+    \textbf{Example:}     & \texttt{label":"operation competed"}\\
+    \textbf{Description:} &
+    \begin{minipage}[t]{0.8\columnwidth}%
+        a label specifying some immediate info about this event. In MSCViewer the label is shown on the right 
+        of the icon representing the event.\\
+    \end{minipage}    
+    \tabularnewline
+    \hline
+    \textbf{Key:}         & \texttt{time} \\
+    \textbf{Type:}        & String \\
+    \textbf{Mandatory:}   & n\\
+    \textbf{Example:}     & \texttt{"time":"1542532s"}\\
+    \textbf{Description:} &
+    \begin{minipage}[t]{0.8\columnwidth}%
+        a timestamp for the event.  It's an integer number followed by a unit qualifier: "s" (seconds), "ms" 
+        (milliseconds), "us" (microseconds) or "ns" (nanoseconds). The timestamp is interpreted as elapsed time 
+        since the Unix Epoch . If the timestamp is not present inside the JSON object, it is expected to be 
+        present before it in one of the formats supported by syslog.  time is shown in MSCViewer at the right 
+        of the event icon. \\
+    \end{minipage}    
+    \tabularnewline
+    \hline
+    \textbf{Key:}         & \texttt{type} \\
+    \textbf{Type:}        & String \\
+    \textbf{Mandatory:}   & n\\
+    \textbf{Example:}     & \texttt{"type":"Timer"}\\
+    \textbf{Description:} &
+    \begin{minipage}[t]{0.8\columnwidth}%
+        If present, the value specifies a distinct type for the event. Events of different types can be rendered
+         by different icons in MSCViewer. Icons can be provided by a user in a directory in the form of PNG images
+          whose name matches the type name. This allows to plug domain-specific representation for events.\\
+    \end{minipage}    
+    \tabularnewline
+    \hline
+    \textbf{Key:}         & \texttt{data} \\
+    \textbf{Type:}        & JSON Value\\
+    \textbf{Mandatory:}   & n\\
+    \textbf{Example:}     & \texttt{"data":\{"v1":10, "v2":20\}} \\
+    \textbf{Description:} &
+    \begin{minipage}[t]{0.8\columnwidth}%
+	    Specifies some data associated to the event. For example, if the event corresponds to the sending of 
+	    a message, the value here could be a JSON representation of the message. in MSCViewer data is shown in 
+	    a table in the data section when the event is selected.\\
+    \end{minipage}    
+   \tabularnewline
+    \hline
+    \textbf{Key:}         & \texttt{src} \\
+    \textbf{Type:}        & JSON Value\\
+    \textbf{Mandatory:}   & n\\
+    \textbf{Example:}     & 
+        \begin{minipage}[t]{0.8\columnwidth}%
+            \texttt{"src":"producer\_1/123"},\\
+            \texttt{"src":"\{"id":"producer\_1/123", "color":"00FF00"\}} 
+        \end{minipage}  \\  
+    \textbf{Description:} &
+    \begin{minipage}[t]{0.8\columnwidth}%
+        Interactions are pairs of events. In a pair, one event contains the src key, while the other contains the 
+        dst key, both with the same value. Interactions are visualized in MSCViewer as arrows going from the source
+        to the destination event. The file format doesn't mandate a particular format for the value, but the value
+        should be unique for an interaction (more on this in the interaction section of this document. In the 
+        simplest case the value can be a string (which is a valid JSON value). When certain aspects of the 
+        rendering need to be controlled, the value can be a JSON object with an "id" key identifying the unique
+         interaction, and other keys (such as "color") identifying rendering aspects.\\
+     \end{minipage}   
+   \tabularnewline
+    \hline
+    \textbf{Key:}         & \texttt{dst} \\
+    \textbf{Type:}        & JSON Value\\
+    \textbf{Mandatory:}   & n\\
+    \textbf{Example:}     & 
+        \begin{minipage}[t]{0.8\columnwidth}%
+            \texttt{"dst":"producer\_1/123"},\\
+            \texttt{"dst":"\{"id":"producer\_1/123", "color":"00FF00"\}} 
+        \end{minipage}  \\  
+    \textbf{Description:} &
+    \begin{minipage}[t]{0.8\columnwidth}%
+        Interactions are pairs of events. In a pair, one event contains the src key, while the other contains 
+        the dst key, both with the same value. Interactions are visualized in MSCViewer as arrows going from
+        the source to the destination event. The file format doesn't mandate a particular format for the value,
+        but the value should be unique for an interaction (more on this in the interaction section of this 
+        document. In the simplest case the value can be a string (which is a valid JSON value). When certain
+        aspects of the rendering need to be controlled, the value can be a JSON object with an "id" key 
+        identifying the unique interaction, and other keys (such as "color") identifying rendering aspects.\\
+     \end{minipage}    
+   \tabularnewline
+  \hline
+  \end{longtable}
+\end{center}
+
+The following table shows the keys interpreted by MSCViewer for entities:
+
+\begin{center}
+    \begin{longtable}{ll}
+    \hline
+    \textbf{Key:}         & \texttt{id} \\
+    \textbf{Type:}        & String \\
+    \textbf{Mandatory:}   & y\\
+    \textbf{Example:}     & \texttt{"id":"/node0/1984"}\\
+    \textbf{Description:} &
+    \begin{minipage}[t]{0.8\columnwidth}%
+		The unique identifier for the entity \\
+    \end{minipage}    
+    \tabularnewline
+    \hline
+    \textbf{Key:}         & \texttt{name} \\
+    \textbf{Type:}        & String \\
+    \textbf{Mandatory:}   & y\\
+    \textbf{Example:}     & \texttt{"id":"/node0/producer\_1"}\\
+    \textbf{Description:} &
+    \begin{minipage}[t]{0.8\columnwidth}%
+        A name for the entity. Names don't need to be unique and provide a more human-readable representation for the entity\\    
+    \end{minipage}    
+    \tabularnewline
+	\end{longtable}
+\end{center}
+
 \chapter{\prog{}  GUI}
+This chapter provides a description of all the GUI elements in \prog.
+
+\section{The Entities Tree}
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=0.3\textwidth]{images/left-pane.png}
+  \caption{The Entities tree}
+  \label{fig:entity-tree} 
+\end{figure}
+
+The Entities Tree is visible on the top-left are of the GUI once an input file is loaded and the \textit{Entities} tab 
+is selected. This tree shows all entities defined in the input file. An entity is defined if a \mscentity{} line is 
+present or if the entity is specified in the \texttt{entity} entry of a \mscevent line. Elements of an entity 
+ID separated by slashes constitute nodes in the tree. Internal nodes of the tree may have event of their own, if 
+they appear as the terminal element in the \texttt{entity} entry of at least one event, or not, in which case they
+just represent some relationship among the child nodes. In the latter case the node is visualized in a lighter 
+shade.
+
+For example, a system may be composed by multiple processes running in different hosts. The user may decide to 
+have a log file for each process, and use a \texttt{host-id/process-id} notation for entity events. In this case,
+Intermediate tree nodes for host-id will be created, but clearly there will be no events associated to them.
+
+Double-clicking on a node corresponding to an entity with at least one event opens the entity in the Sequence 
+Diagram. Double-clicking on a node corresponding to an entity already opened in the Sequence Diagram causes
+it to be removed from the diagram. The following legend shows the various representations of the tree nodes:
+
+\begin{center}
+    \begin{longtable}{ll}
+  	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/entity.png}
+	& entity with at least one event, currently closed in sequence diagram\\
+  	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/entity_open.png}
+	& entity with at least one event, currently open in sequence diagram\\
+  	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/entity_faded.png}
+	& entity with no event, can't be opened in sequence diagram\\
+	\end{longtable}
+\end{center}
+
+\section{The Sequence Diagram area}
+The sequence diagram area is situated on the top-right part of the GUI. Entities can be opened in this area by
+double-clicking on them in the Entity Tree. Open entities can be rearranged by dragging them from their 
+header.
+
+\section{The Tool Bar}
+The toolbar contains the following buttons:
+
+\begin{center}
+    \begin{longtable}{ll}
+	 \multicolumn{2}{l}{\textbf{Actions}} \\
+	\hline
+  	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/load.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Loads a new input file. Pressing this button causes a file chooser to open. Selecting a file and
+      	pressing ok results in the file being loaded. 
+       \end{minipage}\\ \\
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/reload.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Reload the present file. This command can be used if changes are made to the file after it was loaded.
+	  	Note that all currently opened entities are closed before the new file is loaded.
+	  	\end{minipage}\\ \\
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/camera.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Captures a screenshot of the sequence diagram. The user can select whether to capture the entire model 
+		(regardless of what entities are opened in the diagram), The entities currently opened, or just the 
+		entities for which at least one event is highlighted.
+		\end{minipage}\\ \\
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/clear_highlights.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Removes any highlight set on events or interactions, whether they're on open entity or not.
+		\end{minipage}\\ \\
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/run.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Re-run the latest script that was executed. Scripts can be executed by double-clicking on nodes in the
+		tree shown in the Script tab, but this button provides a convenient shortcut to rerun the latest script.
+		\end{minipage}\\ \\
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/options.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Opens a window where various program options can be configured.
+		\end{minipage}\\ \\
+
+	\multicolumn{2}{l}{\textbf{Cursor Tools}} \\
+	\hline
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/select.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Chooses the select tool associated to the mouse pointer. The select tool allows to select an event or
+		interaction. 
+		\end{minipage}\\ \\
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/highlight_green.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		chooses the green marker for highlighting events. When this tool is selected clicking on an event
+		causes it to be highlighted in green.
+		\end{minipage}\\ \\
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/highlight_blue.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Same as the green highlighter, but with blue color.
+		\end{minipage}\\ \\
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/highlight_yellow.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Same as the green highlighter, but with yellow color.
+		\end{minipage}\\ \\
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/highlight_red.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Same as the green highlighter, but with red color.
+		\end{minipage}\\ \\
+
+	\multicolumn{2}{l}{\textbf{Visualization Options}} \\
+	\hline
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/blocks.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Shows/hides blocks. 
+	  \end{minipage}\\ \\
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/time.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Shows/hides event timestamps
+		\end{minipage}\\ \\
+	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/label.png}
+	& \begin{minipage}[t]{0.8\columnwidth}
+		Shows/hides event labels
+		\end{minipage}\\ \\
+	\end{longtable}  
+\end{center}
 

### 2015-04-03 batch/gen_manual_captures.py

@@ -1,0 +1,64 @@
+from mscviewer import *
+import time
+
+#Main.maximize();
+
+### SIMPLE-FLOW.PNG ###
+Main.batchLoad("examples/simple-flow.msc");
+Main.open("User 1")
+Main.open("Backend")
+Main.open("Database")
+Main.captureDiagram("doc/manual/images/simple-flow.png");
+
+#### CONCURRENT-FLOW.PNG ### 
+Main.batchLoad("examples/concurrent-flow.msc");
+Main.open("User 1")
+Main.open("Image Repo")
+Main.open("VM Manager")
+Main.open("Resource Manager")
+Main.captureDiagram("doc/manual/images/concurrent-flow.png");
+
+### GUI-EX1.PNG ###
+Main.batchLoad("examples/lst1.msc");
+Main.captureGUI("MainFrame", "doc/manual/images/gui-ex1.png");
+
+### GUI-EX2-OPEN.PNG ###
+Main.open("producer")
+Main.open("consumer")
+Main.captureGUI("MainFrame", "doc/manual/images/gui-ex2-open.png");
+
+### GUI-EX3-CYCLE.PNG ###
+Main.batchLoad("examples/lst3.msc");
+Main.open("producer")
+Main.open("consumer")
+Main.captureGUI("MainFrame", "doc/manual/images/gui-ex3-cycle.png");
+
+### GUI-EX4-TIME.PNG ###
+Main.batchLoad("examples/lst4.msc");
+Main.open("producer")
+Main.open("consumer")
+Main.captureGUI("MainFrame", "doc/manual/images/gui-ex4-time.png");
+
+### GUI-EX5-DATA.PNG ###
+Main.batchLoad("examples/lst5.msc");
+Main.open("producer")
+en = Main.open("consumer")
+m = Main.getModel();
+for i in range(m.getEventCount()):
+    ev = m.getEventAt(i)
+    if ev.getEntity() == en:
+        Main.select(ev);
+        break;
+    Main.setRightSplitPaneDividerLocation(0.5);
+Main.showDataTab();
+Main.captureGUI("MainFrame", "doc/manual/images/gui-ex5-data.png");
+
+### GEN GUI ENTITY TREE ###
+Main.batchLoad("examples/os.msc");
+Main.expandEntityTree();
+Main.setLeftRightSplitPaneDividerLocation(.35);
+Main.captureGUI("LeftPane", "doc/manual/images/left-pane.png");
+
+#give time for last snapshot to complete
+time.sleep(1)
+Main.quit()

### 2015-04-03 src/com/cisco/mscviewer/gui/EntityTree.java

@@ -249,7 +249,7 @@ class EntityTreeModel implements TreeModel, MSCDataModelListener {
 
 
 @SuppressWarnings("serial")
-class EntityTree extends JTree implements EntityHeaderModelListener {
+public class EntityTree extends JTree implements EntityHeaderModelListener {
     private final ViewModel eh;
 
     @Override
@@ -259,6 +259,7 @@ class EntityTree extends JTree implements EntityHeaderModelListener {
     class EntityTreeRenderer extends DefaultTreeCellRenderer {
     	private ImageIcon entityIcon = Resources.getImageIcon("32x32/entity.png", "entity");
     	private ImageIcon entityFadedIcon = Resources.getImageIcon("32x32/entity_faded.png", "entity");
+    	private ImageIcon entityOpenIcon = Resources.getImageIcon("32x32/entity_open.png", "entity");
 
         @Override
         public Component getTreeCellRendererComponent(
@@ -284,9 +285,9 @@ class EntityTree extends JTree implements EntityHeaderModelListener {
                 if (en.hasEvents()) {
                 	setIcon(entityIcon);
                     if (eh.indexOf(en) != -1) {
-                        setForeground(Color.red);
+                        setIcon(entityOpenIcon);
                     } else
-                        setForeground(Color.black);
+                        setIcon(entityIcon);
                 } else {
                 	setIcon(entityFadedIcon);
                     //setForeground(Color.lightGray);
@@ -395,6 +396,12 @@ class EntityTree extends JTree implements EntityHeaderModelListener {
             int idx) {
         // TODO Auto-generated method stub
 
+    }
+    
+    public void expandAll() {
+    	int cnt = getRowCount();
+    	for(int i=0; i<cnt; i++)
+    		expandRow(i);
     }
 
 }

### 2015-04-03 src/com/cisco/mscviewer/gui/MainFrame.java

@@ -103,7 +103,7 @@ public class MainFrame extends JFrame implements PNGSnapshotTarget {
     private final DataPanel data;
     private final JLabel info;
     final private JFileChooser jfc;
-    //private JToggleButton selectBtn;
+
     private JSlider zoom;
     private Vector<Vector<String>> filters = new Vector<Vector<String>>();
     private final FilterPanel filterP;
@@ -111,7 +111,9 @@ public class MainFrame extends JFrame implements PNGSnapshotTarget {
     private final String progName;
     private String fname;
     private boolean isMarking;
-
+    private JTabbedPane jtabbed;
+    private JSplitPane leftRightSplitPane,  leftSplitPane, rightSplitPane;
+    
     class MouseHandler implements MouseListener, MouseMotionListener {
         
         private void popupMenu(final MouseEvent me) {
@@ -525,9 +527,9 @@ public class MainFrame extends JFrame implements PNGSnapshotTarget {
         toolBar.setFloatable(false);
         toolBar.setBorder(BorderFactory.createEtchedBorder(EtchedBorder.LOWERED));
         getContentPane().add(toolBar, BorderLayout.NORTH);
-        JSplitPane horizontalSplitPane = new JSplitPane(JSplitPane.HORIZONTAL_SPLIT);
-        JSplitPane rightVerticalSplitPane = new JSplitPane(JSplitPane.VERTICAL_SPLIT);
-        getContentPane().add(horizontalSplitPane, BorderLayout.CENTER);
+        leftRightSplitPane = new JSplitPane(JSplitPane.HORIZONTAL_SPLIT);
+        rightSplitPane = new JSplitPane(JSplitPane.VERTICAL_SPLIT);
+        getContentPane().add(leftRightSplitPane, BorderLayout.CENTER);
         info = new JLabel("");
         info.setBorder(BorderFactory.createEtchedBorder());
         getContentPane().add(info, BorderLayout.SOUTH);
@@ -555,14 +557,14 @@ public class MainFrame extends JFrame implements PNGSnapshotTarget {
         bottomLeft.setLayout(new BorderLayout());
         bottomLeft.add(new JLabel("Open Entities"), BorderLayout.NORTH);
         bottomLeft.add(new JScrollPane(entityList), BorderLayout.CENTER);
-        JSplitPane leftPane = new LeftPane(topLeft, bottomLeft);
-        leftPane.setOneTouchExpandable(true);
[…]

### 2015-04-03 src/com/cisco/mscviewer/gui/MainPanel.java

@@ -101,9 +101,7 @@ SelectionListener, MSCDataModelListener, EntityHeaderModelListener {
 
     @Override
     public void paintComponent(Graphics g) {
-
         Graphics2D g2d = (Graphics2D)g;
-        //		if (r.getDataModel() != null) {
         JViewport jvp = getAncestorViewport();
         Rectangle rec = jvp.getViewRect();	
         r.render(g2d, false, rec.y, rec.height);

### 2015-04-03 src/com/cisco/mscviewer/gui/ResultPanel.java

@@ -66,7 +66,7 @@ class ResultPanel extends JPanel implements MouseListener {
                         for (String idarr1 : idarr) {
                             if (!idarr1.equals("")) {
                                 Event ev = model.getEventAt(Integer.parseInt(idarr1));
-                                Main.show(ev);
+                                Main.open(ev);
                             }
                         }
                     }

### 2015-04-09 doc/python-api/source/conf.py
major changes to build infra and streamlining of python API

@@ -1,0 +1,288 @@
+# -*- coding: utf-8 -*-
+#
+# mscviewer documentation build configuration file, created by
+# sphinx-quickstart on Wed Apr  8 14:18:08 2015.
+#
+# This file is execfile()d with the current directory set to its
+# containing dir.
+#
+# Note that not all possible configuration values are present in this
+# autogenerated file.
+#
+# All configuration values have a default; values that are commented out
+# serve to show the default.
+
+import sys
+import os
+import shlex
+
+# If extensions (or modules to document with autodoc) are in another directory,
+# add these directories to sys.path here. If the directory is relative to the
+# documentation root, use os.path.abspath to make it absolute, like shown here.
+#sys.path.insert(0, os.path.abspath('.'))
+
+# -- General configuration ------------------------------------------------
+
+# If your documentation needs a minimal Sphinx version, state it here.
+#needs_sphinx = '1.0'
+
+# Add any Sphinx extension module names here, as strings. They can be
+# extensions coming with Sphinx (named 'sphinx.ext.*') or your custom
+# ones.
+extensions = [
+    'sphinx.ext.autodoc',
+]
+
+# Add any paths that contain templates here, relative to this directory.
+templates_path = ['_templates']
+
+# The suffix(es) of source filenames.
+# You can specify multiple suffix as a list of string:
+# source_suffix = ['.rst', '.md']
+source_suffix = '.rst'
+
+# The encoding of source files.
+#source_encoding = 'utf-8-sig'
+
+# The master toctree document.
+master_doc = 'index'
+
+# General information about the project.
+project = u"MSCViewer's Python API"
+copyright = u'2015, Roberto Attias'
+author = u'Roberto Attias'
+
+# The version info for the project you're documenting, acts as replacement for
+# |version| and |release|, also used in various other places throughout the
+# built documents.
+#
+# The short X.Y version.
+version = '2.0B'
+# The full version, including alpha/beta/rc tags.
+release = '2.0B'
+
+# The language for content autogenerated by Sphinx. Refer to documentation
+# for a list of supported languages.
+#
+# This is also used if you do content translation via gettext catalogs.
+# Usually you set "language" from the command line for these cases.
+language = None
+
+# There are two options for replacing |today|: either, you set today to some
+# non-false value, then it is used:
+#today = ''
+# Else, today_fmt is used as the format for a strftime call.
+#today_fmt = '%B %d, %Y'
+
[…]

### 2015-04-09 src/com/cisco/mscviewer/io/LegacyLoader.java

@@ -308,8 +308,8 @@ public class LegacyLoader implements Loader {
     }
 
     @Override
-    public void load(final String fname, final MSCDataModel dm) throws IOException {
-        if (Main.batchMode()) {
+    public void load(final String fname, final MSCDataModel dm, boolean batchMode) throws IOException {
+        if (batchMode) {
             loadInternal(fname, dm);
         } else {
             latch = new CountDownLatch(1);
@@ -344,7 +344,7 @@ public class LegacyLoader implements Loader {
 //                @Override
 //                public void propertyChange(PropertyChangeEvent evt) {
 //                    if ("progress".equals(evt.getPropertyName())) {
-//                        Main.progress((Integer) evt.getNewValue());
+//                        MSC.progress((Integer) evt.getNewValue());
 //                    }
 //                }
 //            });

### 2015-04-09 src/com/cisco/mscviewer/io/Loader.java

@@ -17,5 +17,5 @@ import com.cisco.mscviewer.model.MSCDataModel;
 
 public interface Loader {
     void waitIfLoading();
-    void load(final String fname, final MSCDataModel dm) throws IOException;
+    void load(final String fname, final MSCDataModel dm, boolean batchMode) throws IOException;
 }

### 2015-04-09 src/com/cisco/mscviewer/model/MSCDataModel.java

@@ -51,7 +51,8 @@ class KeyEvent extends Event {
  * @author rattias
  */
 public final class MSCDataModel {
-    private final LinkedHashMap<String, Entity> entities = new LinkedHashMap<String, Entity>();
+    private static MSCDataModel singleton;
+	private final LinkedHashMap<String, Entity> entities = new LinkedHashMap<String, Entity>();
     private final ArrayList<Entity> rootEntities;
     private ArrayList<Event> events;
     private IntervalTree interactions;
@@ -68,7 +69,7 @@ public final class MSCDataModel {
     /**
      * Instantiate a data model
      */
-    public MSCDataModel() {
+    private MSCDataModel() {
         this.listeners = new Vector<MSCDataModelListener>();
         this.events = new ArrayList<Event>();
         this.rootEntities = new ArrayList<Entity>();
@@ -214,9 +215,9 @@ public final class MSCDataModel {
         return events.get(idx);
     }
 
-//    public int getEventIndex(Event ev) {
-//        return events.indexOf(ev);
-//    }
+    public int getEventIndex(Event ev) {
+        return events.indexOf(ev);
+    }
     
     /**
      * returns the number of events in the data model.
@@ -840,4 +841,10 @@ public final class MSCDataModel {
         }
         return null;
     }
+
+	public static MSCDataModel getInstance() {
+		if (singleton == null)
+			singleton = new MSCDataModel();
+		return singleton;
+	}
 }

### 2015-04-09 src/com/cisco/mscviewer/script/PythonFunction.java

@@ -26,11 +26,13 @@ public class PythonFunction {
     private String doc;
     private boolean wasSet;
     private Python python;
+    private String pkg;
     
     public PythonFunction(Python p, String pkg, String name) {
+    	this.pkg = pkg;
         this.name = name;
         python = p;
-        PyObject args = p.eval("inspect.getargspec("+name+")");
+        PyObject args = p.eval("inspect.getargspec("+pkg+"."+name+")");
         PyTuple t = (PyTuple) args;
         PyObject[] objs = ((PyList) t.get(0)).getArray();
         argNames = new String[objs.length];
@@ -117,7 +119,7 @@ public class PythonFunction {
 
     public void invoke() throws ScriptException {
         StringBuilder sb = new StringBuilder();
-        sb.append(name).append("(");
+        sb.append(pkg).append('.').append(name).append("(");
         StringBuffer args = new StringBuffer();
         int regArgCount = argValues.length - argDefaults.length;
         for (int i = 0; i < regArgCount; i++) {

### 2015-04-15 doc/python-api/mscviewer.py
rationalized python API, removed dependency on sphinx for python API documentation.

@@ -1,406 +1,0 @@
-"""This module contains wrappers for the MSCViewer Java API intended to be 
-  used by Python scripts. Even though Python scripts may have access to the
-  full Java API, this module defines a stable interface that will guarantee
-  compatibility in the future. Internal Java APIs may, and most likely will, 
-  be subject to change, so use those at your own risk.
-"""
-
-from string import Template
-from com.cisco.mscviewer import Main
-from com.cisco.mscviewer.model import MSCDataModel
-from com.cisco.mscviewer.util import Report, ProgressReport, Utils
-from com.cisco.mscviewer.model import Entity, Event, Interaction
-from com.cisco.mscviewer.gui import Marker
-from com.cisco.mscviewer.gui import MainFrame
-from types import TupleType 
-import sys 
-import re
-#import logging WATCH OUT! this import changes name of thread to MainThread for some reason
-import inspect
-import time
-
-#MATCH_LOGGER =  logging.getLogger("flow_match")
-#logging.basicConfig(filename='example.log',level=logging.DEBUG)
-#logging.warning("logging enabled (warning)")
-#logging.debug("logging enabled (debug)")
-
-msc_debug = {} 
-DBG_MATCH = " db"
-
-############## UTILITY CLASSES #######################
-class marker(object):
-    GREEN = Marker.GREEN
-    BLUE = Marker.BLUE
-    RED = Marker.RED
-    YELLOW = Marker.YELLOW
-
-
-def msc_fun(f):
-    """Marks a function to make it visible in the GUI.
-    
-    Each user-defined function that needs to be invokable
-    from the GUI should be decorated with the msc_fun attribute. 
-
-    **Example:** ::
-    
-        @msc_fun
-        def myfun():
-        ...
-    """       
-    f.is_msc_fun = True
-    return f
-
-                   
-
-################ MODEL BROWSING FUNCTIONS ###############
-
-#------ ENTITY-SPECIFIC FUNCTIONS --------------
-def entities(root_only=False):
-    """returns an iterable on all entities in the model.
-    
-    This function can be used to iterate on all entities in the model.
-    
-    :param root_only: if True, only top-level entities are iterated upon
-    :type root_only: boolean
-    
-    **Example:** ::
-    
-        for en in entities():
-            print entity_name(en)    
-    """
-    
-    model = MSCDataModel.getInstance();
-    it = model.getEntityIterator(root_only)
-    while it.hasNext():
-        yield it.next()
-
-def entity_id(entity):
-    """returns the unique ID of this entity"""
[…]

### 2015-04-15 resources/default/script/event_rate.py

@@ -1,9 +1,9 @@
-from com.cisco.mscviewer.model import MSCDataModel
-from com.cisco.mscviewer.graph import GraphData
-import mscviewer
+import msc.model as model
+import msc.graph as graph
+import msc.gui as gui
 import math
     
-@mscviewer.msc_fun  
+@gui.msc_fun  
 def event_rate_fn():
     """
     Creates a set of graph representing rate of events, one for each entity of the
@@ -11,23 +11,23 @@ def event_rate_fn():
     """
     cnt = 0;
     info = {}
-    evcount = mscviewer.event_count()
-    for en in mscviewer.entities():
-        info[en] = GraphData(en.getPath())
+    evcount = model.event_count()
+    for en in model.entities():
+        info[en] = graph.series(en.getPath())
         info[en].setXType("time")
         
-    pr = mscviewer.progress_start("processing events", 0, mscviewer.event_count());
+    pr = gui.progress_start("processing events", 0, model.event_count());
     prev = {}
-    twidth = mscviewer.event_timestamp(mscviewer.event_at(evcount-1)) - mscviewer.event_timestamp(mscviewer.event_at(0))
-    for ev in mscviewer.events():
+    twidth = model.event_timestamp(model.event_at(evcount-1)) - model.event_timestamp(model.event_at(0))
+    for ev in model.events():
         cnt += 1
-        mscviewer.progress_report(pr, cnt)
-        en = mscviewer.event_entity(ev)
-        enp = mscviewer.entity_path(en)
-        t = mscviewer.event_timestamp(ev)
+        gui.progress_report(pr, cnt)
+        en = model.event_entity(ev)
+        enp = model.entity_path(en)
+        t = model.event_timestamp(ev)
         v = 0
         if enp in prev:
-            tprev = mscviewer.event_timestamp(prev[enp])
+            tprev = model.event_timestamp(prev[enp])
             v = t - tprev
             if v < 0:
                 v = -v
@@ -39,10 +39,14 @@ def event_rate_fn():
         info[en].add(t, v, ev)
         prev[enp] = ev
         
-    arr = []
-    for en in mscviewer.entities():
+    g = graph.graph("graph") 
+    for en in model.entities():
         inf = info[en]
         if not inf.isEmpty():
-            arr.append(inf)
-    mscviewer.graph(arr)
-    pr.progressDone() 
+            graph.graph_add_series(g, inf)
+            print model.entity_path(en)
[…]

### 2015-04-15 resources/default/script/flows.py

@@ -1,200 +1,0 @@
-from mscviewer import *
-import mscviewer_flows
-from sets import Set
-
-def add_backward(selEv, res):
-    pending = [selEv]
-    for ev in pending:
-        res.append(ev)
-        ent = ev.getEntity()
-        inters = ev.getIncomingInteractions()
-        limit = ent.getFirstEventIndex()        
-        for inter in inters:
-            fromEv = inter.getFromEvent()
-            if fromEv: 
-                pending.append(fromEv)
-        if len(inters) != 0:
-            continue
-        idx = ev.getIndex() - 1
-        while idx >= limit:
-            tmpEv = event_at(idx)
-            if tmpEv.getEntity() == ent:
-                pending.append(tmpEv)
-                break
-            idx -= 1
-
-def add_forward(selEv, res):
-    pending = [selEv]
-    for ev in pending:
-        res.append(ev)
-        ent = ev.getEntity()
-        inters = ev.getOutgoingInteractions()
-        limit = ent.getLastEventIndex()
-        for inter in inters:
-            toEv = inter.getToEvent()
-            if toEv: 
-                pending.append(toEv)
-
-        idx = ev.getIndex() + 1
-        while idx <= limit:
-            tmpEv = event_at(idx)
-            if tmpEv.getEntity() == ent:
-                inters = tmpEv.getIncomingInteractions()
-                if len(inters) == 0 and not tmpEv.isBlockBegin():
-                    pending.append(tmpEv)
-                break
-            idx += 1
-	
-@msc_fun
-def mark_flow(before=False, after=True):
-    """
-    marks in green a flow starting from the selected event. 
-    
-    a flow here is a set S of event constructed as follows:
-      1) TMP = {Es} (where Es is the selected event)
-    2) for each event E in TMP:
-        - add E to S
-        - remove E from TMP
-        - add to S all events which are sinks for interactions
-        where E is the source
-        - add to S the next event in the same Entity as E, unless
-        such event begins a block
-    3) if TMP is not empty, goto 2    
-    
-    Arguments:
-    - before: if set to True all events before the selected one
-              and belonging to the same flow are marked.
-              default is False
-    - after:  if set to True all events after the selected one
-              and belonging to the same flow are marked.
-              default is True
-    """
-    selEv = event_selected()
[…]

### 2015-04-15 resources/default/script/mscviewer_flows.py

@@ -1,725 +1,0 @@
-from string import Template
-from com.cisco.mscviewer import Main
-from com.cisco.mscviewer.util import Report, ProgressReport, Utils
-from com.cisco.mscviewer.model import MSCDataModel, Entity, Event, Interaction
-from com.cisco.mscviewer.gui import Marker
-from types import TupleType 
-import sys 
-import re
-#import logging WATCH OUT! this import changes name of thread to MainThread for some reason
-import inspect
-import time
-
-#MATCH_LOGGER =  logging.getLogger("flow_match")
-#logging.basicConfig(filename='example.log',level=logging.DEBUG)
-#logging.warning("logging enabled (warning)")
-#logging.debug("logging enabled (debug)")
-
-msc_debug = {} 
-DBG_MATCH = " db"
-class AbortSearchException(Exception):
-    pass
-
-class FlowError(Exception):
-    """
-    Exception rosen for flow-related problems
-    """
-    causes = None
-    
-    #causes is one or a list of FlowError 
-    def __init__(self, message, causes=None):
-        self.causes = causes        
-        if self.causes != None:
-            cstr = "\nCause:\n"        
-            for c in self.causes:
-                cstr += str(c)+"\n";
-        else:
-            cstr = ""
-        Exception.__init__(self, message+cstr)
-        
-                            
-                                            	
-#def flow_add_event(res, mev):
-#    ints = mev.getIncomingInteractions()
-#    if ints != None:
-#        for t in ints:
-#            if not t in res:
-#                res.append(t)
-#                src = t.getFromEvent()              
-#                if src != None and not dst in res:
-#                    res.append(src)
-#    res.append(mev)
-#    ints = mev.getOutgoingInteractions()
-#    if ints != None:
-#        for t in ints:
-#            if not t in res:
-#                res.append(t)
-#                dst = t.getToEvent()
-#                if dst != None and not dst in res:
-#                    res.append(dst)
-                            
-          
-#class fen:
-#    def __init__(self, _path="???"):
-#        self.path = _path
-
-class flow_base:
-    """
-    Base class for all flow declaration constructs
-    """
-    traversed = False
-    parent = None
-    children = ()
-    
-    def __init__(self, *_arg):
-        self.children = _arg
-        for el in self.children:
-            el.parent = self
-        self.setvars({});
-
-    def matched(self):
-        return self.traversed and self._matched  
-    
-    def get_mismatching_fevs(self, arr=[]):
-        if not self.traversed:
-            return
-        for el in self.get_children():
[…]

### 2015-04-15 src/com/cisco/mscviewer/graph/Graph.java

@@ -1,0 +1,26 @@
+package com.cisco.mscviewer.graph;
+
+import java.util.ArrayList;
+import java.util.Collections;
+import java.util.List;
+
+import com.cisco.mscviewer.model.MSCDataModel;
+
+public class Graph {
+    private String name;
+    private ArrayList<GraphSeries> series;
+    
+    public Graph(String name) {
+        this.name = name;
+        this.series = new ArrayList<GraphSeries>();
+        MSCDataModel.getInstance().addGraph(this);
+    }
+    
+    public void add(GraphSeries g) {
+        series.add(g);
+    }
+    
+    public List<GraphSeries> getSeries() {
+        return Collections.unmodifiableList(series);
+    }
+}

### 2015-04-15 src/com/cisco/mscviewer/gui/graph/LineGraphPanel.java

@@ -2,7 +2,7 @@ package com.cisco.mscviewer.gui.graph;
 
 import java.awt.Graphics2D;
 
-import com.cisco.mscviewer.graph.GraphData;
+import com.cisco.mscviewer.graph.GraphSeries;
 import com.cisco.mscviewer.graph.Point;
 import com.cisco.mscviewer.tree.Interval;
 
@@ -10,10 +10,10 @@ import com.cisco.mscviewer.tree.Interval;
 public class LineGraphPanel extends GraphPanel {    
     @Override
     public void paintGraph(Graphics2D g) {
-        GraphData[] graphs = getGraphData();
+        GraphSeries[] graphs = getGraphData();
         long minX = 0;
         long maxX = getMaxModelX();
-        for (GraphData d : graphs) {
+        for (GraphSeries d : graphs) {
             if (isEnabled(d)) {
                 Interval in = d.getInterval(minX, maxX);
                 int start = in.getStart();

### 2015-05-27 doc/manual/mscviewer.tex
major changes to build infra and streamlining of python API
fixed user guide to just mention python-api guide
V2.0.0

@@
 \usepackage{lipsum}
-\include{titlepage}
+\include{generated/titlepage}
 
@@
 \newcommand{\defterm}[1]{\textit{#1}\index{#1}}
-
+%
+\makeatletter
+\newenvironment{indentation}[2]%
+{ \par \setlength{\leftmargin}{#1}
+  \setlength{\rightmargin}{#2}
+  \advance\linewidth -\leftmargin
+  \advance\linewidth -\rightmargin
+  \advance\@totalleftmargin\leftmargin
+  \@setpar{{\@@par}}%
+  \parshape 1 \@totalleftmargin
+  \linewidth \ignorespaces
+}{\par}
+\makeatother
+%
 %\title{\prog{} v1.0} \author{ Roberto Attias  \\
@@
   stringstyle=\color{dkgreen},
-  backgroundcolor=\color{lightcyan},
-  frame=shadowbox,
-  xleftmargin=2em,
-  framexleftmargin=1.5em, 
-  rulesepcolor=\color{gray},
+  %backgroundcolor=\color{lightcyan},
+  %frame=shadowbox,
+  %xleftmargin=2em,
+  %framexleftmargin=1.5em, 
+  %rulesepcolor=\color{gray},
   breaklines=true,
@@
 \prog{} is a tool supporting visualization and analysis of message sequence
-charts. The tool loads a text file, interprets lines containing the
-\mscevent{} or \mscentity{} keywords and representing events and interactions occurring on
-entities, ignoring other lines. From the interpreted lines a model is
-constructed in memory. In the GUI the tool can visualize the list of enties,
-from which the user can select a subset to be shown in a sequence diagram chart.
-through keyboard or mouse commands the user can easily navigate through events
-and interactions, search, and perform a number of other actions for browsing the
-diagram.
+charts intended primaritly for debugging of logs/traces obtained from concurrent systems.
 
-In a design phase the user can write a concise description of one or
-more flows in the inpujt language,load it in the tool, and export an image to 
-be used for documentation.
+The tool loads a text file and interprets lines containing well known keywords representing
+events and interactions occurring in entities. Lines not containing the known keywords are
+ignored. From the interpreted lines a model is constructed in memory. In the GUI the tool 
+shows the list of all entities for which events exist. From this list the user can 
+select a subset to be shown in a sequence diagram chart. Through keyboard or mouse commands
+the user can easily navigate through events and interactions, rearrange entities, search, 
+and perform a number of other actions for browsing the diagram.
 
-By instrumenting certain point in the program or application with syslogs,
-printf, traces or any other mechanism avaliable, the user can generate run the
-application and generate the input file for \prog{}. In this case the input
-file contains flows corresponding to actual executions, which could be visually
-inspected for verification.
+In addition to using the tool for visualization of traces for existing 
+systems, during a design phase the user can write a concise description of one or
+more flow\footnote{a formal definiton of flow will be provided later in this document.
+For the time being consider it a sequence of events across one or more entities} 
+in the input language, load it in the tool, and export an image to 
+be used for documentation. Later on, the implemented system should produce diagrams
+similar to the one defined at design time, hence this approach can be used to confirm
+the system behaves as designed.
 
-Visual inspection of flows from execution logs is useful, but doesn't scale for
-debugging, as it requires a human operator familiar with the expected flows.
+In order for a system to produce the required data for \prog{}, the program code 
+need to be instrumented with syslogs, printf, traces or any other mechanism avaliable,
+using the format expected by the tool for the messages.
+The user can run the application and generate the input file for \prog{}, possibly
+by merging together multiple generated files.
+
+Visual inspection of the system behavior from execution logs is useful, but doesn't
+scale for debugging, as it requires a human operator familiar with the expected behavior.
 When applications are large enough, their development might be distributed
-across multiple teams, with only few members fully aware of cross-component
-flows. To address this problem \prog{} is integrated with a Python interpreter
-and supports execution of scripts which can browse the model and perform any
-sort of validation. In addition, a set of classes is provided to support a
-concise description of expected flows. With these mechanism the user can create
-validation script to be executed in the tool on the model created from execution
-logs, automatically validating their correctness. Scripts can also be executed
-from command line, without any GUI visualization, supporting batch validations
-and product smoke-testing.
+across multiple teams, and possibly even geographically, with only few members
+fully aware of cross-component flows. To address this problem \prog{} is 
+integrated with a Python interpreter and supports execution of scripts which 
+can browse the model and perform any sort of validation. In addition, a set
+of classes is provided to support a concise description of expected flows.
+With these mechanism the user can create script to be executed in
+the tool on the model created from execution logs, automatically validating 
+their correctness. Scripts can also be executed from command line, without 
+any GUI visualization, supporting batch validations and product smoke-testing.
 
@@
 
-When designing, implementing and debugging such a complex system flows play a
+When designing, implementing and debugging such a complex system, flows play a
 very important role in the entire development cycle.
@@
 represent any kind of problem domain. \prog{} understands only the concept of
-hyerarchical IDS and names where elements in the hyerarchy are separated by
+hierarchical IDS and names where elements in the hierarchy are separated by
 slashes.
@@
 
+\chapter{Pyhton API}
+One of the most powerful aspects of \prog{} is the integration with a Python interpreter
+which allows to access programmatically both model as wel as GUI.
+
+One use of this feature
+consist in writing validation scripts that can browse model data and report whether a 
+particular computational flow is present or not, it respects certain timing constraints, etc. 
+Because the script is written once and then applied to traces produced by running the 
+system multiple times, this scales the effort of an activity that otherwise would have to be
+performed by one or more human beings.
+
+Python scripts can also be used to drive the GUI. For example, the screen captures in this 
+manual are all generated automatically a build time by a Python script which loads a model,
+open some entities in the sequence diagram, captures screenshots and saves them.
+
+The interaction between the user Python script and the tool is done through APIs 
+collected in a few Python files the script can import. The Python language doesn't 
+have a concept of private vs. public API, and the technology used to integrate the 
+Python interpreted in \prog{} (which is written in Java) results in all the Java 
+classes being actually visible and accessible from the Python code. However the 
+user should restrict itself to using the API documented in the next few sections,
+as this provides better guarantees of not being modified in the future. No such 
+claims are made agains any of the Java classes.
+
+The API is currently divided in the following modules:
+\begin{itemize}
+\item \texttt{msc.model} -- provides API to access entities, events and interactions in the model
+\item \texttt{msc.gui} -- provides API to access the GUI 
+\item \texttt{msc.utils} -- provides some utility API 
+\item \texttt{msc.graph} -- provides API to access the graphing capabilities (experimental). 
+\item \texttt{msc.flowdef} -- provides API to implement compact definition of expected flows and apply them
+                              to the current model
+\end{itemize}                              
+\section{Model API}
+
+\input{generated/python-api-model.tex}
+
+\section{GUI API}
+\input{generated/python-api-gui.tex}
+
+\section{Flows API}
+\input{generated/python-api-flowdef.tex}
+
+\section{Graph API}
+\input{generated/python-api-graph.tex}
+
 \chapter{Customizing \prog}

### 2015-05-27 resources/calvados/script/vm.py

@@ -2,7 +2,10 @@ from string import Template
 import re
 from msc.model import *
 from msc.flows import *
-	
+
+def fconn_to(client_entity,server_entity):
+    return fev(client_entity, "<"+server_entity+"_init>", predicate=is_sink, descr="connecting to "+server_entity)
+
             
 def vm_creation_flow(human_friendly=True):
     # print "*** vm_creation_flow called with arg=", arg, "with_model=", with_model, "human=", human 

### 2015-05-27 resources/default/script/msc/flowdef.py

@@ -47,6 +47,7 @@ class FlowError(Exception):
                                             	
 class flow_base:
     """
+    $ignore
     Base class for all flow declaration constructs
     """
     traversed = False
@@ -226,6 +227,9 @@ class flow_base:
         return res
            
     def get_min_model_index(self):
+        """$descr{returns the minimum among the index of the events this flow 
+        definition has been annotated with.}
+        """
         res = sys.maxint
         if self.traversed:
             if isinstance(self, fev) and self.model_idx >= 0:
@@ -238,9 +242,22 @@ class flow_base:
      
         
 class fev(flow_base):
+    """$descr{Instances of this class represent a single event.}"""
+    
     def __init__(self, entity, label, 
                  predicate=None, predicate_arg=None, action=None, 
-                 action_arg=None, descr=None, nomatch_action=None, nomatch_action_arg=None):
+                 action_arg=None, descr=None):
+        """$descr{creates an instance of the class}
+        $header{Parameters}
+        $param{entity}{String}{The string or regexp representing the ID of the entity for the event to be matched.}
+        $param{label}{String}{The string or regexp representing the ID of the event to be matched}
+        $param{predicate}{function}{an optional function that should return True for the comparison to succeed (in
+        addition to entity and label comparison)}
+        $param{predicate_arg}{any}{An argument to be passed to the predicate function when it's called}
+        $param{action}{function}{An optional function to be called if a match is found}
+        $param{action_arg}{any}{A parameter to be passed to the action function when it's called}
+        $param{desc}{String}{A description of the element}
+        """
         self.model = None
         self.description = descr
         self.entity = Template(entity)          
@@ -249,10 +266,9 @@ class fev(flow_base):
         self.predicate_arg = predicate_arg
         self.action = action
         self.action_arg = action_arg
-        self.nomatch_action = nomatch_action
-        self.nomatch_action_arg = nomatch_action_arg
-
+ 
     def get_model(self, arr=[], dbg=False):
+        """$descr{returns a tuple of model element that have annotated this flow (see flow_match())}"""
         if dbg:
[…]

### 2015-05-27 src/com/cisco/mscviewer/graph/Graph.java

@@ -7,19 +7,19 @@ import java.util.List;
 import com.cisco.mscviewer.model.MSCDataModel;
 
 public class Graph {
-    private String name;
-    private ArrayList<GraphSeries> series;
-    
+    private final String name;
+    private final ArrayList<GraphSeries> series;
+
     public Graph(String name) {
         this.name = name;
         this.series = new ArrayList<GraphSeries>();
         MSCDataModel.getInstance().addGraph(this);
     }
-    
+
     public void add(GraphSeries g) {
         series.add(g);
     }
-    
+
     public List<GraphSeries> getSeries() {
         return Collections.unmodifiableList(series);
     }

### 2015-05-27 src/com/cisco/mscviewer/gui/BottomRightPane.java

@@ -15,14 +15,14 @@ import com.cisco.mscviewer.util.PNGSnapshotTarget;
 
 /**
  * @author Roberto Attias
- * @since  Jan 2012
+ * @since Jan 2012
  */
 @SuppressWarnings("serial")
-class BottomRightPane extends JTabbedPane implements PNGSnapshotTarget{
+class BottomRightPane extends JTabbedPane implements PNGSnapshotTarget {
     public BottomRightPane() {
         setName("BottomRightPane");
     }
-    
+
     @Override
     public Component getPNGSnapshotClient() {
         return null;

### 2015-05-27 src/com/cisco/mscviewer/gui/CompactViewFilter.java

@@ -6,16 +6,19 @@
  * http://www.eclipse.org/legal/epl-v10.html
  *------------------------------------------------------------------*/
 package com.cisco.mscviewer.gui;
+
 import java.util.regex.Matcher;
 import java.util.regex.Pattern;
 
-import com.cisco.mscviewer.model.*;
+import com.cisco.mscviewer.model.Event;
+import com.cisco.mscviewer.model.MSCDataModelEventFilter;
+import com.cisco.mscviewer.model.ViewModel;
 
 /**
  * @author Roberto Attias
- * @since  Jan 2012
+ * @since Jan 2012
  */
-class CompactViewFilter implements MSCDataModelEventFilter { 
+class CompactViewFilter implements MSCDataModelEventFilter {
     private final ViewModel m;
     private Matcher matcher;
 
@@ -30,9 +33,9 @@ class CompactViewFilter implements MSCDataModelEventFilter {
 
     @Override
     public boolean filter(Event ev) {
-        return 
-        m.indexOf(ev.getEntity()) != -1 && 
-        (matcher != null ? matcher.reset(ev.getLabel()).matches() : true);
+        return m.indexOf(ev.getEntity()) != -1
+                && (matcher != null ? matcher.reset(ev.getLabel()).matches()
+                        : true);
     }
 
 }

### 2015-05-27 src/com/cisco/mscviewer/gui/CustomJScrollPane.java

@@ -8,20 +8,21 @@
 package com.cisco.mscviewer.gui;
 
 import java.awt.Component;
-import javax.swing.JScrollPane;
-import com.cisco.mscviewer.util.PNGSnapshotTarget;
 
+import javax.swing.JScrollPane;
+
+import com.cisco.mscviewer.util.PNGSnapshotTarget;
 
 /**
  * @author Roberto Attias
- * @since  Aug 2012
+ * @since Aug 2012
  */
 @SuppressWarnings("serial")
 class CustomJScrollPane extends JScrollPane implements PNGSnapshotTarget {
     public CustomJScrollPane(Component view) {
         super(view);
     }
-    
+
     @Override
     public Component getPNGSnapshotClient() {
         return null;

### 2015-05-27 src/com/cisco/mscviewer/gui/DataPanel.java

@@ -6,12 +6,6 @@
  * http://www.eclipse.org/legal/epl-v10.html
  *------------------------------------------------------------------*/
 package com.cisco.mscviewer.gui;
-import com.cisco.mscviewer.io.JSonException;
-import com.cisco.mscviewer.model.Event;
-import com.cisco.mscviewer.model.Interaction;
-import com.cisco.mscviewer.model.JSonArrayValue;
-import com.cisco.mscviewer.model.JSonObject;
-import com.cisco.mscviewer.model.JSonValue;
 
 import java.awt.BorderLayout;
 import java.util.ArrayList;
@@ -25,10 +19,17 @@ import javax.swing.JTable;
 import org.jdesktop.swingx.JXTreeTable;
 import org.jdesktop.swingx.treetable.AbstractTreeTableModel;
 
+import com.cisco.mscviewer.io.JSonException;
+import com.cisco.mscviewer.model.Event;
+import com.cisco.mscviewer.model.Interaction;
+import com.cisco.mscviewer.model.JSonArrayValue;
+import com.cisco.mscviewer.model.JSonObject;
+import com.cisco.mscviewer.model.JSonValue;
+
 class TreeTableNodeModel {
     String fieldName;
     Object value;
-    
+
     public TreeTableNodeModel(String key, Object value) {
         fieldName = key;
         this.value = value;
@@ -37,78 +38,82 @@ class TreeTableNodeModel {
 
 /**
  * @author Roberto Attias
- * @since  Aug 2012
+ * @since Aug 2012
  */
 class TreeTableModel extends AbstractTreeTableModel {
-    private final static String[] COLUMN_NAMES = {"Key", "Value"};
-    
+    private final static String[] COLUMN_NAMES = { "Key", "Value" };
+
     public TreeTableModel(JSonValue obj) {
         super(new TreeTableNodeModel("ROOT", obj));
     }
-    
+
     @Override
     public int getColumnCount() {
         return COLUMN_NAMES.length;
     }
-    
+
     @Override
     public String getColumnName(int column) {
         return COLUMN_NAMES[column];
     }
-    
+
     @Override
     public boolean isCellEditable(Object node, int column) {
         return false;
     }
-    
+
     @Override
     public boolean isLeaf(Object node) {
-        Object value = ((TreeTableNodeModel)node).value;
-        if (value instanceof JSonObject && ((JSonObject)value).getFieldCount() > 0)
+        final Object value = ((TreeTableNodeModel) node).value;
[…]

### 2015-05-27 src/com/cisco/mscviewer/gui/FindSourcePanel.java

@@ -11,6 +11,12 @@
  */
 package com.cisco.mscviewer.gui;
 
+import java.awt.BorderLayout;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.util.regex.Pattern;
+import java.util.regex.PatternSyntaxException;
+
 import javax.swing.JButton;
 import javax.swing.JLabel;
 import javax.swing.JList;
@@ -18,23 +24,18 @@ import javax.swing.JOptionPane;
 import javax.swing.JPanel;
 import javax.swing.JTextField;
 import javax.swing.ListModel;
-import java.awt.BorderLayout;
-import java.awt.event.ActionEvent;
-import java.awt.event.ActionListener;
-import java.util.regex.Pattern;
-import java.util.regex.PatternSyntaxException;
 
 @SuppressWarnings("serial")
 class FindSourcePanel extends JPanel {
-    private final JList<String> list;   
+    private final JList<String> list;
 
     public FindSourcePanel(final JList<String> list) {
         this.list = list;
         setLayout(new BorderLayout());
-        JLabel jl = new JLabel("Find:");
+        final JLabel jl = new JLabel("Find:");
         add(jl, BorderLayout.WEST);
 
-        JPanel p = new JPanel();
+        final JPanel p = new JPanel();
         p.setLayout(new BorderLayout());
         add(p, BorderLayout.CENTER);
         final JButton prev = new JButton("<");
@@ -45,10 +46,10 @@ class FindSourcePanel extends JPanel {
         p.add(tf, BorderLayout.CENTER);
         p.add(next, BorderLayout.EAST);
 
-        tf.addActionListener(new ActionListener() {			
+        tf.addActionListener(new ActionListener() {
             @Override
             public void actionPerformed(ActionEvent e) {
-                String expr = tf.getText();
+                final String expr = tf.getText();
                 findNext(expr);
             }
         });
@@ -56,36 +57,37 @@ class FindSourcePanel extends JPanel {
         prev.addActionListener(new ActionListener() {
             @Override
             public void actionPerformed(ActionEvent e) {
-                String  txt = tf.getText();
+                final String txt = tf.getText();
                 findPrev(txt);
             }
-        });		
+        });
 
         next.addActionListener(new ActionListener() {
             @Override
             public void actionPerformed(ActionEvent e) {
-                String txt = tf.getText();
+                final String txt = tf.getText();
                 findNext(txt);
             }
-        });		
+        });
     }
 
[…]

### 2015-05-27 src/com/cisco/mscviewer/gui/FunctionParametersDialog.java

@@ -33,14 +33,15 @@ import javax.swing.JPanel;
 import javax.swing.JScrollPane;
 import javax.swing.JTextArea;
 import javax.swing.JTextField;
+import javax.swing.SwingConstants;
 import javax.swing.text.AttributeSet;
 import javax.swing.text.BadLocationException;
 import javax.swing.text.PlainDocument;
 
 import com.cisco.mscviewer.Main;
+import com.cisco.mscviewer.script.PythonFunction;
 import com.cisco.mscviewer.util.PNGSnapshotTarget;
 import com.cisco.mscviewer.util.Utils;
-import com.cisco.mscviewer.script.PythonFunction;
 
 @SuppressWarnings("serial")
 class FunctionParametersDialog extends JDialog implements PNGSnapshotTarget {
@@ -49,40 +50,39 @@ class FunctionParametersDialog extends JDialog implements PNGSnapshotTarget {
     private int value;
 
     class ArgPanel extends JPanel {
-        private boolean validInput = true;
+        private final boolean validInput = true;
 
-        public ArgPanel(
-                String title, final String[] args, String defs[], String[] values, 
-                final int offset, int count, JTextField[] tfarr, ActionListener al) {
+        public ArgPanel(String title, final String[] args, String defs[],
+                String[] values, final int offset, int count,
+                JTextField[] tfarr, ActionListener al) {
             setLayout(new BorderLayout());
             setBorder(BorderFactory.createTitledBorder(title));
-            Box vbox = Box.createVerticalBox();
-            JScrollPane jsp = new JScrollPane(vbox) {
+            final Box vbox = Box.createVerticalBox();
+            final JScrollPane jsp = new JScrollPane(vbox) {
                 @Override
                 public Dimension getPreferredSize() {
-                    Dimension d = super.getPreferredSize();
+                    final Dimension d = super.getPreferredSize();
                     return d;
                 }
             };
             add(jsp, BorderLayout.CENTER);
-            boolean isOptional = offset >= args.length-defs.length;
-            JLabel[] lab = new JLabel[count];
-            Dimension maxLabelSize = new Dimension(0, 0);
-            Dimension maxTFSize = new Dimension(Integer.MAX_VALUE, 0);
+            final boolean isOptional = offset >= args.length - defs.length;
+            final JLabel[] lab = new JLabel[count];
+            final Dimension maxLabelSize = new Dimension(0, 0);
[…]

### 2015-05-27 src/com/cisco/mscviewer/gui/JScriptPanel.java

@@ -11,39 +11,43 @@
  */
 package com.cisco.mscviewer.gui;
 
+import java.awt.BorderLayout;
+import java.awt.Color;
+import java.util.List;
+import java.util.Timer;
+import java.util.TimerTask;
+
+import javax.script.ScriptEngine;
+import javax.script.ScriptEngineFactory;
+import javax.script.ScriptEngineManager;
+import javax.script.ScriptException;
 import javax.swing.JPanel;
 import javax.swing.JScrollPane;
 import javax.swing.JSplitPane;
 import javax.swing.JTextArea;
 import javax.swing.SwingUtilities;
-import javax.script.*;
-
-import java.awt.BorderLayout;
-import java.awt.Color;
-import java.util.*;
 
 @SuppressWarnings("serial")
 class JScriptPanel extends JPanel {
     private ScriptEngine engine;
-    private JTextArea scriptTA;
-    private JTextArea errorTA;
-    private Timer t;
+    private final JTextArea scriptTA;
+    private final JTextArea errorTA;
+    private final Timer t;
     private String scriptContext;
 
     public JScriptPanel() {
-        JSplitPane jsp = new JSplitPane(JSplitPane.VERTICAL_SPLIT);
+        final JSplitPane jsp = new JSplitPane(JSplitPane.VERTICAL_SPLIT);
         setLayout(new BorderLayout());
         add(jsp, BorderLayout.CENTER);
         jsp.setResizeWeight(.7);
-        ScriptEngineManager mgr = new ScriptEngineManager();
-        List<ScriptEngineFactory> factories = mgr.getEngineFactories();
-        for (ScriptEngineFactory factory: factories) {
-            String langName = factory.getLanguageName();
-            String langVersion = factory.getLanguageVersion();
-            if (langName.equals("ECMAScript") && 
-                    langVersion.equals("1.6")) {
+        final ScriptEngineManager mgr = new ScriptEngineManager();
+        final List<ScriptEngineFactory> factories = mgr.getEngineFactories();
+        for (final ScriptEngineFactory factory : factories) {
+            final String langName = factory.getLanguageName();
+            final String langVersion = factory.getLanguageVersion();
+            if (langName.equals("ECMAScript") && langVersion.equals("1.6")) {
                 engine = factory.getScriptEngine();
-                break;	
+                break;
             }
         }
         if (engine == null) {
@@ -56,7 +60,7 @@ class JScriptPanel extends JPanel {
         errorTA.setEditable(false);
[…]

### 2015-05-27 src/com/cisco/mscviewer/gui/MSCRenderer.java

@@ -10,6 +10,7 @@
  * @since  Jun 2011
  */
 package com.cisco.mscviewer.gui;
+
 import java.awt.BasicStroke;
 import java.awt.Color;
 import java.awt.Dimension;
@@ -44,7 +45,7 @@ import com.cisco.mscviewer.util.Resources;
 public class MSCRenderer {
     public final static int EVENT_HEIGHT = 20;
     private int eventHeight = EVENT_HEIGHT;
-    //private EntityHeaderModel headerModel;
+    // private EntityHeaderModel headerModel;
     private Event selectedEvent = null;
     private Interaction selectedInteraction = null;
     private int viewModelSelectedEventIndex = -1;
@@ -52,12 +53,12 @@ public class MSCRenderer {
     private boolean showBlocks = true;
     private boolean showLabels = true;
     private OutputUnit absTimeUnit = OutputUnit.H_M_S_MS;
-    private InputUnit deltaTimeUnit = InputUnit.NS; 
-    //private InputUnit timestampUnit = InputUnit.NS;
+    private InputUnit deltaTimeUnit = InputUnit.NS;
+    // private InputUnit timestampUnit = InputUnit.NS;
     private final boolean drawBands = true;
     private boolean showUnits = true;
     private boolean showDate = false;
-    private boolean  showLeadingZeroes;
+    private boolean showLeadingZeroes;
     private boolean compactView = true;
     private final Vector<SelectionListener> selListeners = new Vector<SelectionListener>();
     private int maxBBwidth = 0;
@@ -69,15 +70,12 @@ public class MSCRenderer {
     private Font mainFont;
     private final boolean timeProportional = false;
 
-    final static BasicStroke basicStroke =  new BasicStroke();
-    final static BasicStroke selStroke =  new BasicStroke(2.0f);
-    final static BasicStroke dashedStroke =  
-        new BasicStroke(1.0f, // line width
-                BasicStroke.CAP_BUTT,
-                BasicStroke.JOIN_BEVEL, 1.0f,
-                new float[] { 3.0f, 3.0f, 3.0f, 3.0f },
-                0.0f); 	
-    final static int STUB_LEN=40;
+    final static BasicStroke basicStroke = new BasicStroke();
+    final static BasicStroke selStroke = new BasicStroke(2.0f);
+    final static BasicStroke dashedStroke = new BasicStroke(1.0f, // line width
[…]

### 2015-05-27 src/com/cisco/mscviewer/gui/MainPanel.java

@@ -10,7 +10,6 @@
  * @since  Jun 2011
  */
 package com.cisco.mscviewer.gui;
-import com.cisco.mscviewer.model.*;
 
 import java.awt.Color;
 import java.awt.Component;
@@ -31,6 +30,13 @@ import javax.swing.Scrollable;
 import javax.swing.SwingConstants;
 import javax.swing.ToolTipManager;
 
+import com.cisco.mscviewer.model.Entity;
+import com.cisco.mscviewer.model.EntityHeaderModelListener;
+import com.cisco.mscviewer.model.Event;
+import com.cisco.mscviewer.model.Interaction;
+import com.cisco.mscviewer.model.MSCDataModel;
+import com.cisco.mscviewer.model.MSCDataModelListener;
+import com.cisco.mscviewer.model.ViewModel;
 
 @SuppressWarnings("serial")
 class TimeHeader extends JPanel {
@@ -42,15 +48,15 @@ class TimeHeader extends JPanel {
 
     @Override
     protected void paintComponent(Graphics g) {
-        MSCRenderer r = mp.getMSCRenderer();
-        Dimension d = getSize();
+        final MSCRenderer r = mp.getMSCRenderer();
+        final Dimension d = getSize();
         if (d.height == 0)
             return;
 
         if (r != null) {
-            JViewport jvp = (JViewport)getParent();
-            Rectangle rec = jvp.getViewRect();
-            r.renderTimeHeader((Graphics2D)g, false, rec.y, rec.height);
+            final JViewport jvp = (JViewport) getParent();
+            final Rectangle rec = jvp.getViewRect();
+            r.renderTimeHeader((Graphics2D) g, false, rec.y, rec.height);
         }
     }
 }
@@ -61,19 +67,20 @@ class TimeHeader extends JPanel {
  */
 @SuppressWarnings("serial")
 public class MainPanel extends JPanel implements Scrollable, KeyListener,
-SelectionListener, MSCDataModelListener, EntityHeaderModelListener {
-    //private float zoomFactor = 1.0f;
+        SelectionListener, MSCDataModelListener, EntityHeaderModelListener {
+    // private float zoomFactor = 1.0f;
     private final MainFrame mf;
     private final MSCRenderer r;
-    //private Rectangle selectionRectangle = null;
+    // private Rectangle selectionRectangle = null;
     private final EntityHeader entityHeader;
     private final ViewModel viewModel;
 
[…]

### 2015-05-27 src/com/cisco/mscviewer/gui/Marker.java

@@ -15,11 +15,8 @@ import java.awt.Color;
 
 public enum Marker {
 
-    ERROR(Color.red),
-    RED(Color.red),
-    YELLOW(new Color(0xFFFF99)),
-    BLUE(new Color(0x99FFFF)),
-    GREEN(new Color(0x29FF29));
+    ERROR(Color.red), RED(Color.red), YELLOW(new Color(0xFFFF99)), BLUE(
+            new Color(0x99FFFF)), GREEN(new Color(0x29FF29));
 
     private Color transparentColor;
     private final Color color;
@@ -34,7 +31,8 @@ public enum Marker {
 
     public Color getTransparentColor() {
         if (transparentColor == null)
-            transparentColor = new Color(color.getRed(), color.getGreen(), color.getBlue(), 128);
+            transparentColor = new Color(color.getRed(), color.getGreen(),
+                    color.getBlue(), 128);
         return transparentColor;
     }
 

### 2015-05-27 src/com/cisco/mscviewer/gui/MarkerBar.java

@@ -22,30 +22,29 @@ import javax.swing.JScrollBar;
 import javax.swing.plaf.ScrollBarUI;
 
 import com.cisco.mscviewer.model.Entity;
-import com.cisco.mscviewer.model.ViewModel;
 import com.cisco.mscviewer.model.EntityHeaderModelListener;
 import com.cisco.mscviewer.model.Event;
 import com.cisco.mscviewer.model.MSCDataModel;
-
+import com.cisco.mscviewer.model.ViewModel;
 
 @SuppressWarnings("serial")
-class MarkerBar extends JPanel implements EntityHeaderModelListener, MouseListener {
+class MarkerBar extends JPanel implements EntityHeaderModelListener,
+        MouseListener {
     final static int markHeight = 4;
     final static int markWidth = 16;
     private final ViewModel viewModel;
     private final EntityHeader entityHeader;
     private final MSCDataModel model;
-    private int topOffset=0, btmOffset=0; 
+    private int topOffset = 0, btmOffset = 0;
     private final MSCRenderer r;
 
     MarkerBar(EntityHeader eh, ViewModel m, MSCRenderer r) {
         this.entityHeader = eh;
-        this.viewModel = m;        
+        this.viewModel = m;
         this.r = r;
         this.model = MSCDataModel.getInstance();
         addMouseListener(this);
     }
-
 
     @Override
     public Dimension getPreferredSize() {
@@ -55,44 +54,45 @@ class MarkerBar extends JPanel implements EntityHeaderModelListener, MouseListen
     @Override
     public void paintComponent(Graphics g) {
         super.paintComponent(g);
-        JScrollBar jsb = new JScrollBar();
-        ScrollBarUI uui = jsb.getUI();
-        Dimension d = uui.getPreferredSize(jsb);
+        final JScrollBar jsb = new JScrollBar();
+        final ScrollBarUI uui = jsb.getUI();
+        final Dimension d = uui.getPreferredSize(jsb);
         if (d != null) {
-            topOffset = (int)d.getWidth()+entityHeader.getHeight();
-            btmOffset = (int)d.getWidth();
+            topOffset = (int) d.getWidth() + entityHeader.getHeight();
+            btmOffset = (int) d.getWidth();
         }
 
         if (model == null)
             return;
         g.setColor(Color.gray);
-        g.drawLine(0, topOffset-1, getWidth(), topOffset-1);
[…]

### 2015-05-27 src/com/cisco/mscviewer/gui/TopLeftPane.java

@@ -18,7 +18,7 @@ import javax.swing.JTabbedPane;
 import com.cisco.mscviewer.util.PNGSnapshotTarget;
 
 @SuppressWarnings("serial")
-class TopLeftPane extends JTabbedPane implements PNGSnapshotTarget{
+class TopLeftPane extends JTabbedPane implements PNGSnapshotTarget {
     public TopLeftPane() {
         setName("TopLeftPane");
     }

### 2015-05-27 src/com/cisco/mscviewer/gui/graph/EntityCheckBox.java

@@ -1,6 +1,5 @@
 package com.cisco.mscviewer.gui.graph;
 
-
 import javax.swing.JCheckBox;
 
 import com.cisco.mscviewer.graph.GraphSeries;
@@ -8,7 +7,7 @@ import com.cisco.mscviewer.graph.GraphSeries;
 @SuppressWarnings("serial")
 public class EntityCheckBox extends JCheckBox {
     public GraphSeries data;
-    
+
     public EntityCheckBox(GraphSeries gd) {
         super(gd.getName());
         data = gd;

### 2015-05-27 src/com/cisco/mscviewer/gui/graph/HeatGraphWindow.java

@@ -1,19 +1,12 @@
 package com.cisco.mscviewer.gui.graph;
 
-import java.awt.BorderLayout;
 import java.awt.Color;
 import java.awt.event.ItemEvent;
 import java.awt.event.ItemListener;
-import java.awt.event.MouseAdapter;
-import java.awt.event.MouseEvent;
 
-import javax.swing.BorderFactory;
 import javax.swing.JComponent;
 import javax.swing.JFrame;
-import javax.swing.JLabel;
-import javax.swing.JPanel;
 import javax.swing.JScrollPane;
-import javax.swing.JSplitPane;
 import javax.swing.JTextField;
 import javax.swing.ListSelectionModel;
 import javax.swing.SwingUtilities;
@@ -25,21 +18,19 @@ import com.cisco.mscviewer.gui.MSCRenderer;
 import com.cisco.mscviewer.gui.MainFrame;
 import com.cisco.mscviewer.model.Event;
 
-
-@SuppressWarnings({ "serial"})
+@SuppressWarnings({ "serial" })
 public class HeatGraphWindow extends JFrame {
-    private Graph graph;
+    private final Graph graph;
     private CheckBoxList list;
     private JTextField xtf;
-    private GraphPanel gp;
-    
-    
+    private final GraphPanel gp;
+/*
     private JComponent mkLegend() {
         list = new CheckBoxList();
         list.setBackground(Color.black);
-        EntityCheckBox[] cbs = new EntityCheckBox[graph.getSeries().size()];
+        final EntityCheckBox[] cbs = new EntityCheckBox[graph.getSeries().size()];
         int idx = 0;
-        for (GraphSeries gd: graph.getSeries()) {
+        for (final GraphSeries gd : graph.getSeries()) {
             cbs[idx] = new EntityCheckBox(gd);
             cbs[idx].setBackground(Color.black);
             cbs[idx].setForeground(gp.getForeground(gd));
@@ -47,62 +38,63 @@ public class HeatGraphWindow extends JFrame {
             cbs[idx].addItemListener(new ItemListener() {
                 @Override
                 public void itemStateChanged(ItemEvent ev) {
-                    EntityCheckBox c = (EntityCheckBox)ev.getItem();
-                    gp.setEnabled(c.data, ev.getStateChange() == ItemEvent.SELECTED);
+                    final EntityCheckBox c = (EntityCheckBox) ev.getItem();
+                    gp.setEnabled(c.data,
+                            ev.getStateChange() == ItemEvent.SELECTED);
                     revalidate();
[…]

### 2015-05-27 src/com/cisco/mscviewer/gui/mvg/Poly.java

@@ -21,33 +21,35 @@ import java.util.ArrayList;
 public class Poly extends Primitive {
     class Point {
         float x, y;
+
         public Point(float x, float y) {
             this.x = x;
             this.y = y;
         }
     }
+
     private final ArrayList<Point> points;
-    
+
     public Poly(float x0, float y0) {
         points = new ArrayList<Point>();
         points.add(new Point(x0, y0));
     }
-    
+
     public void addPoint(float x, float y) {
         points.add(new Point(x, y));
     }
-    
+
     @Override
-    public void setContainerDimension(int w, int h) {        
-        Path2D s = new Path2D.Float();
-        boolean first = true;
-        for(Point p: points) {
+    public void setContainerDimension(int w, int h) {
+        final Path2D s = new Path2D.Float();
+        final boolean first = true;
+        for (final Point p : points) {
             if (first)
-                s.moveTo(p.x*w,p.y*h);
+                s.moveTo(p.x * w, p.y * h);
             else
-                s.lineTo(p.x*w, p.y*h);
+                s.lineTo(p.x * w, p.y * h);
         }
         setShape(s);
     }
-    
+
 }

### 2015-05-27 src/com/cisco/mscviewer/gui/mvg/Rect.java

@@ -18,16 +18,18 @@ import java.awt.geom.Rectangle2D;
  * @author rattias
  */
 public class Rect extends Primitive {
-    private float x, y, w, h;
-    
+    private final float x, y, w, h;
+
     public Rect(float x, float y, float w, float h) {
         this.x = x;
         this.y = y;
         this.w = w;
         this.h = h;
     }
-    
+
+    @Override
     public void setContainerDimension(int width, int height) {
-        setShape(new Rectangle2D.Float(x*width, y*height, w*width, h*height));
+        setShape(new Rectangle2D.Float(x * width, y * height, w * width, h
+                * height));
     }
 }

### 2015-05-27 src/com/cisco/mscviewer/gui/renderer/BlockInteractionRenderer.java

@@ -11,7 +11,6 @@
  */
 package com.cisco.mscviewer.gui.renderer;
 
-
 public class BlockInteractionRenderer extends RectangleInteractionRenderer {
     public BlockInteractionRenderer() {
         setup(null, null);

### 2015-05-27 src/com/cisco/mscviewer/gui/renderer/EventRenderer.java

@@ -11,11 +11,12 @@
  */
 package com.cisco.mscviewer.gui.renderer;
 
-import com.cisco.mscviewer.model.JSonObject;
 import java.awt.Color;
 import java.awt.Dimension;
 import java.awt.Graphics2D;
 import java.awt.Rectangle;
+
+import com.cisco.mscviewer.model.JSonObject;
 
 abstract public class EventRenderer {
     public final static Color SELECTION_COLOR = Color.red;
@@ -27,7 +28,7 @@ abstract public class EventRenderer {
      * @param props
      */
     public void initialize(JSonObject props) {
-//        this.ev = ev;
+        // this.ev = ev;
         setup(props);
     }
 
@@ -36,7 +37,7 @@ abstract public class EventRenderer {
      * @param b
      */
     protected void setScaleSource(boolean b) {
-        scaleSource = b;		
+        scaleSource = b;
     }
 
     /**
@@ -47,33 +48,36 @@ abstract public class EventRenderer {
         return scaleSource;
     }
 
-//    public Event getEvent() {
-//        return ev;
-//    }
+    // public Event getEvent() {
+    // return ev;
+    // }
 
     /**
      *
      * @param props
      */
     public void setup(JSonObject obj) {
-//        String style = props.getProperty("label_style");
-//        if (style != null) {
-//            if (style.equals("bold"))
-//                labelStyle = Font.BOLD;
-//            else if (style.equals("italic"))
-//                labelStyle = Font.ITALIC;
-//            else if (style.equals("plain"))
-//                labelStyle = Font.PLAIN;
-//        }
+        // String style = props.getProperty("label_style");
+        // if (style != null) {
+        // if (style.equals("bold"))
+        // labelStyle = Font.BOLD;
+        // else if (style.equals("italic"))
+        // labelStyle = Font.ITALIC;
+        // else if (style.equals("plain"))
+        // labelStyle = Font.PLAIN;
+        // }
     }
 
-//    public int getLabelStyle() {
-//        return labelStyle;
-//    }
-    /** renders the event. (x,y) is the center
-     * @param g2d	
-     * @param maxDim	
-     * @param isSelected */	
+    // public int getLabelStyle() {
+    // return labelStyle;
+    // }
+    /**
+     * renders the event. (x,y) is the center
+     * 
+     * @param g2d
+     * @param maxDim
+     * @param isSelected
+     */
[…]

### 2015-05-27 src/com/cisco/mscviewer/gui/renderer/InteractionRenderer.java

@@ -11,33 +11,29 @@
  */
 package com.cisco.mscviewer.gui.renderer;
 
-
-import com.cisco.mscviewer.gui.Marker;
-import com.cisco.mscviewer.model.JSonObject;
-import com.cisco.mscviewer.model.Event;
-import com.cisco.mscviewer.model.Interaction;
 import java.awt.BasicStroke;
 import java.awt.Color;
 import java.awt.Graphics2D;
 import java.awt.Rectangle;
 import java.util.HashMap;
 
+import com.cisco.mscviewer.gui.Marker;
+import com.cisco.mscviewer.model.Event;
+import com.cisco.mscviewer.model.Interaction;
+import com.cisco.mscviewer.model.JSonObject;
 
-abstract public class  InteractionRenderer {
+abstract public class InteractionRenderer {
     private final static HashMap<String, BasicStroke> bs = new HashMap<String, BasicStroke>();
     private Interaction inter;
 
-    
     protected final static BasicStroke getBasicStroke(int width, boolean dashed) {
-        String k = width+"-"+dashed;
+        final String k = width + "-" + dashed;
         BasicStroke b = bs.get(k);
         if (b == null) {
             if (dashed)
-                b = new BasicStroke(width,
-                    BasicStroke.CAP_BUTT,
-                    BasicStroke.JOIN_BEVEL, 1.0f,
-                    new float[] { 3.0f, 3.0f, 3.0f, 3.0f },
-                    0.0f);
+                b = new BasicStroke(width, BasicStroke.CAP_BUTT,
+                        BasicStroke.JOIN_BEVEL, 1.0f, new float[] { 3.0f, 3.0f,
+                                3.0f, 3.0f }, 0.0f);
             else
                 b = new BasicStroke(width);
             bs.put(k, b);
@@ -54,21 +50,15 @@ abstract public class  InteractionRenderer {
 
     abstract public void setup(JSonObject props, Event ev);
 
-
     public Interaction getInteraction() {
         return inter;
     }
 
+    public abstract void render(Rectangle fb, Rectangle tb, Graphics2D g2d,
+            boolean isSelected, Marker m);
 
-    public abstract void render(
-            Rectangle fb,
-            Rectangle tb,
-            Graphics2D g2d, boolean isSelected, Marker m);
-
-    public abstract boolean inSelectionArea(
-            Rectangle b1,
-            Rectangle b2,
-            int px, int py, boolean self);
[…]

### 2015-05-27 src/com/cisco/mscviewer/gui/renderer/LaneRenderer.java

@@ -11,10 +11,6 @@
  */
 package com.cisco.mscviewer.gui.renderer;
 
-import com.cisco.mscviewer.gui.Marker;
-import com.cisco.mscviewer.model.JSonObject;
-import com.cisco.mscviewer.model.*;
-
 import java.awt.BasicStroke;
 import java.awt.Color;
 import java.awt.Graphics2D;
@@ -22,17 +18,22 @@ import java.awt.Rectangle;
 import java.awt.Stroke;
 import java.util.HashMap;
 
+import com.cisco.mscviewer.gui.Marker;
+import com.cisco.mscviewer.model.Entity;
+import com.cisco.mscviewer.model.Event;
+import com.cisco.mscviewer.model.JSonNumberValue;
+import com.cisco.mscviewer.model.JSonObject;
+import com.cisco.mscviewer.model.JSonValue;
+
 public class LaneRenderer extends InteractionRenderer {
     final static int MAX_LANES = 1280;
     private static final HashMap<Entity, String[]> hm = new HashMap<Entity, String[]>();
     private int lane;
     private final static int LANE_WIDTH = 10;
     BasicStroke basic, basic2, thickStroke;
-    private final static BasicStroke dashedStroke =  new BasicStroke(1.0f, 
-            BasicStroke.CAP_BUTT,
-            BasicStroke.JOIN_BEVEL, 1.0f,
-            new float[] { 3.0f, 3.0f, 3.0f, 3.0f },
-            0.0f);
+    private final static BasicStroke dashedStroke = new BasicStroke(1.0f,
+            BasicStroke.CAP_BUTT, BasicStroke.JOIN_BEVEL, 1.0f, new float[] {
+                    3.0f, 3.0f, 3.0f, 3.0f }, 0.0f);
     int[] xp = new int[4];
     int[] yp = new int[4];
 
@@ -44,137 +45,137 @@ public class LaneRenderer extends InteractionRenderer {
     public void setup(JSonObject props, Event ev) {
         float strokeWidth = 1.0f;
         if (props != null) {
-            JSonNumberValue stroke = ((JSonNumberValue)props.get("stroke_width"));
+            final JSonNumberValue stroke = ((JSonNumberValue) props
+                    .get("stroke_width"));
             if (stroke != null)
                 strokeWidth = stroke.floatValue();
         }
         basic = new BasicStroke(strokeWidth);
-        basic2 = new BasicStroke(strokeWidth+2);
[…]

### 2015-05-27 src/com/cisco/mscviewer/gui/renderer/TransitionRenderer.java

@@ -11,19 +11,22 @@
  */
 package com.cisco.mscviewer.gui.renderer;
 
-import com.cisco.mscviewer.model.JSonObject;
 import com.cisco.mscviewer.model.Event;
+import com.cisco.mscviewer.model.JSonObject;
 import com.cisco.mscviewer.model.JSonStringValue;
 import com.cisco.mscviewer.model.JSonValue;
 
 public class TransitionRenderer extends DefaultInteractionRenderer {
+    @Override
     public void setup(JSonObject props, Event ev) {
-        JSonObject p = new JSonObject();
+        final JSonObject p = new JSonObject();
         JSonValue v = props.get("color");
-        p.set("color", new JSonStringValue((v != null) ? v.toString() : "00AA00"));
+        p.set("color", new JSonStringValue((v != null) ? v.toString()
+                : "00AA00"));
 
         v = props.get("stroke_width");
-        p.set("stroke_width", new JSonStringValue((v != null) ? v.toString() : "2.0"));
+        p.set("stroke_width", new JSonStringValue((v != null) ? v.toString()
+                : "2.0"));
 
         p.set("draw_tip", new JSonStringValue("false"));
         p.set("straight", new JSonStringValue("true"));

### 2015-05-27 src/com/cisco/mscviewer/io/Config.java

@@ -25,15 +25,16 @@ public class Config {
     static String ATTR_MARKER_LINE = "line";
     static String ATTR_MARKER_COLOR = "color";
     static String ATTR_MARKER_NOTE = "note";
-    static SimpleDateFormat sdf = new SimpleDateFormat("dd-MM-yyyy hh:mm:ss"); 
+    static SimpleDateFormat sdf = new SimpleDateFormat("dd-MM-yyyy hh:mm:ss");
 
     public static String getDateString(long t) {
-        Date d = new Date(t);
-        String dateString = sdf.format(d);
+        final Date d = new Date(t);
+        final String dateString = sdf.format(d);
         return dateString;
     }
 
-    public static long getTimeSinceEpoch(String dateString) throws ParseException {
+    public static long getTimeSinceEpoch(String dateString)
+            throws ParseException {
         return sdf.parse(dateString).getTime();
     }
 }

### 2015-05-27 src/com/cisco/mscviewer/io/ConfigLoader.java

@@ -32,80 +32,98 @@ class UserAbortException extends SAXException {
 
 public class ConfigLoader {
     /**
-     * loads a configuration and applies it to the passed model if non-null, or tries
-     * to load the model referred to by the configuration first.  
+     * loads a configuration and applies it to the passed model if non-null, or
+     * tries to load the model referred to by the configuration first.
+     * 
      * @param fname
      * @param mod
      * @param obs
-     * @return 
-     * @throws java.io.IOException 
+     * @return
+     * @throws java.io.IOException
      */
-    public static MSCDataModel load(String fname, MSCDataModel mod) throws IOException {
-        SAXParserFactory factory = SAXParserFactory.newInstance();
+    public static MSCDataModel load(String fname, MSCDataModel mod)
+            throws IOException {
+        final SAXParserFactory factory = SAXParserFactory.newInstance();
         SAXParser saxParser = null;
         try {
             saxParser = factory.newSAXParser();
-        } catch (ParserConfigurationException e1) {
+        } catch (final ParserConfigurationException e1) {
             throw new IOException(e1);
-        } catch (SAXException e1) {
+        } catch (final SAXException e1) {
             throw new IOException(e1);
         }
         final String cfgPath = fname;
-        final MSCDataModel min = mod; 
+        final MSCDataModel min = mod;
 
-        DefaultHandler handler = new DefaultHandler() {
+        final DefaultHandler handler = new DefaultHandler() {
             @Override
-            public void startElement(String uri, String localName,String qName, 
-                    Attributes attributes) throws SAXException {
+            public void startElement(String uri, String localName,
+                    String qName, Attributes attributes) throws SAXException {
                 if (qName.equalsIgnoreCase(Config.EL_MSCCONFIG)) {
-                    String logPath = attributes.getValue(Config.ATTR_MSCCONFIG_LOG);
-                    String dateString = attributes.getValue(Config.ATTR_MSCCONFIG_DATE);
+                    final String logPath = attributes
+                            .getValue(Config.ATTR_MSCCONFIG_LOG);
+                    final String dateString = attributes
+                            .getValue(Config.ATTR_MSCCONFIG_DATE);
 
                     long t = 0;
                     try {
                         t = Config.getTimeSinceEpoch(dateString);
-                    } catch (ParseException e) {
+                    } catch (final ParseException e) {
                         e.printStackTrace();
                     }
-                    File f = new File(logPath);
-                    long lastModified = f.lastModified();
[…]

### 2015-05-27 src/com/cisco/mscviewer/io/ConvertFormat.java

@@ -10,16 +10,17 @@ import java.util.regex.Pattern;
 
 public class ConvertFormat {
     private static Pattern pv1 = Pattern.compile("entity_id\\s*=\\s*\".+\"");
-    private static Pattern pv1_el = Pattern.compile("(@msc_entity)|(@msc_event)|(@msc_source)|(@msc_sink)|([a-zA-Z_]+)\\s*=\\s*\"([^\"]+)\"");
-    private final static int IN_FMT_V1 = 1; //v1.0
-    
+    private static Pattern pv1_el = Pattern
+            .compile("(@msc_entity)|(@msc_event)|(@msc_source)|(@msc_sink)|([a-zA-Z_]+)\\s*=\\s*\"([^\"]+)\"");
+    private final static int IN_FMT_V1 = 1; // v1.0
+
     private final static int GRP_ENTITY = 1;
-    private final static int GRP_EVENT  = 2;
+    private final static int GRP_EVENT = 2;
     private final static int GRP_SOURCE = 3;
-    private final static int GRP_SINK   = 4;
-    private final static int GRP_KEY    = 5;
-    private final static int GRP_VALUE  = 6;
-    
+    private final static int GRP_SINK = 4;
+    private final static int GRP_KEY = 5;
+    private final static int GRP_VALUE = 6;
+
     public static void main(String args[]) throws IOException {
         int fmt = 0;
 
@@ -27,111 +28,119 @@ public class ConvertFormat {
             System.err.println("Syntax: mscupgrade <input file> <output file>");
             System.exit(1);
         }
-        
-        String fin = args[0];
-        BufferedReader br = new BufferedReader(new FileReader(fin));
+
+        final String fin = args[0];
+        final BufferedReader br = new BufferedReader(new FileReader(fin));
         String line = null;
-        PrintStream ps;        
+        PrintStream ps;
         ps = new PrintStream(args[1]);
-        System.out.println("converting file "+args[0]+"...");
+        System.out.println("converting file " + args[0] + "...");
         try {
-            while((line = br.readLine()) != null) {
+            while ((line = br.readLine()) != null) {
                 if (line.indexOf("@msc") == -1) {
                     ps.println(line);
                     continue;
                 }
                 if (fmt == 0) {
-                    if (line.indexOf("@msc_event") != -1 && pv1.matcher(line).find()) {
-                        //v1.0 format
+                    if (line.indexOf("@msc_event") != -1
+                            && pv1.matcher(line).find()) {
[…]

### 2015-05-27 src/com/cisco/mscviewer/io/JsonLoader.java

@@ -11,21 +11,13 @@
  */
 package com.cisco.mscviewer.io;
 
-import com.cisco.mscviewer.Main;
-import com.cisco.mscviewer.gui.MainFrame;
-import com.cisco.mscviewer.gui.renderer.*;
-import com.cisco.mscviewer.model.*;
-import com.cisco.mscviewer.tree.Interval;
-import com.cisco.mscviewer.util.JSonParser;
-import com.cisco.mscviewer.util.ProgressReport;
-import com.cisco.mscviewer.util.Resources;
-
 import java.beans.PropertyChangeEvent;
 import java.beans.PropertyChangeListener;
 import java.io.BufferedReader;
 import java.io.File;
 import java.io.FileReader;
 import java.io.IOException;
+import java.io.PrintStream;
 import java.text.ParseException;
 import java.text.SimpleDateFormat;
 import java.util.ArrayList;
@@ -39,71 +31,98 @@ import java.util.concurrent.ExecutionException;
 import javax.swing.JOptionPane;
 import javax.swing.SwingWorker;
 
+import com.cisco.mscviewer.Main;
+import com.cisco.mscviewer.gui.MainFrame;
+import com.cisco.mscviewer.gui.renderer.DefaultInteractionRenderer;
+import com.cisco.mscviewer.gui.renderer.EventRenderer;
+import com.cisco.mscviewer.gui.renderer.InteractionRenderer;
+import com.cisco.mscviewer.model.Entity;
+import com.cisco.mscviewer.model.Event;
+import com.cisco.mscviewer.model.Interaction;
+import com.cisco.mscviewer.model.JSonArrayValue;
+import com.cisco.mscviewer.model.JSonObject;
+import com.cisco.mscviewer.model.JSonStringValue;
+import com.cisco.mscviewer.model.JSonValue;
+import com.cisco.mscviewer.model.LogListModel;
+import com.cisco.mscviewer.model.MSCDataModel;
+import com.cisco.mscviewer.model.SimpleInterval;
+import com.cisco.mscviewer.tree.Interval;
+import com.cisco.mscviewer.util.JSonParser;
+import com.cisco.mscviewer.util.Prefs;
+import com.cisco.mscviewer.util.ProgressReport;
+import com.cisco.mscviewer.util.Resources;
+
 public class JsonLoader implements Loader {
     public enum TypeEn {
 
         SOURCE, SINK, LOCAL
     };
+
     private static final String MSC_EVENT = "@msc_event";
[…]

### 2015-05-27 src/com/cisco/mscviewer/io/Loader.java

@@ -17,5 +17,7 @@ import com.cisco.mscviewer.model.MSCDataModel;
 
 public interface Loader {
     void waitIfLoading();
-    void load(final String fname, final MSCDataModel dm, boolean batchMode) throws IOException;
+
+    void load(final String fname, final MSCDataModel dm, boolean batchMode)
+            throws IOException;
 }

### 2015-05-27 src/com/cisco/mscviewer/io/PNGSaver.java

@@ -11,11 +11,6 @@
  */
 package com.cisco.mscviewer.io;
 
-import com.cisco.mscviewer.gui.MSCRenderer;
-import com.cisco.mscviewer.model.Entity;
-import com.cisco.mscviewer.model.MSCDataModel;
-import com.cisco.mscviewer.util.ProgressReport;
-
 import java.awt.Color;
 import java.awt.FontMetrics;
 import java.awt.Graphics2D;
@@ -31,105 +26,131 @@ import javax.imageio.stream.ImageOutputStream;
 import javax.swing.JOptionPane;
 import javax.swing.SwingUtilities;
 
+import com.cisco.mscviewer.gui.MSCRenderer;
+import com.cisco.mscviewer.model.Entity;
+import com.cisco.mscviewer.model.MSCDataModel;
+import com.cisco.mscviewer.util.ProgressReport;
+
 public class PNGSaver {
     public final static int SAVE_MARKED = 1;
     public final static int SAVE_OPENED = 2;
     public final static int SAVE_ALL = 3;
-    
-    public static void saveMSCasPNG(final String path, final MSCRenderer r, int mode) throws IOException {
-        Thread t = new Thread("Image Writer") {
+
+    public static void saveMSCasPNG(final String path, final MSCRenderer r,
+            int mode) throws IOException {
+        final Thread t = new Thread("Image Writer") {
             @Override
             public void run() {
                 ImageOutputStream ios = null;
                 try {
-                    BufferedImage tmp = new BufferedImage(1, 1, BufferedImage.TYPE_INT_RGB);
+                    final BufferedImage tmp = new BufferedImage(1, 1,
+                            BufferedImage.TYPE_INT_RGB);
                     Graphics2D g2d = tmp.createGraphics();
-                    FontMetrics fm = g2d.getFontMetrics();
+                    final FontMetrics fm = g2d.getFontMetrics();
                     int entityWidth = 0;
-                    for(Iterator<Entity> it = MSCDataModel.getInstance().getEntityIterator(false); it.hasNext();) {
-                        Entity en = it.next();
-                        int w = fm.stringWidth(en.getName());
-                        if (w>entityWidth)
+                    for (final Iterator<Entity> it = MSCDataModel.getInstance()
+                            .getEntityIterator(false); it.hasNext();) {
+                        final Entity en = it.next();
+                        final int w = fm.stringWidth(en.getName());
+                        if (w > entityWidth)
                             entityWidth = w;
                     }
                     g2d.dispose();
[…]

### 2015-05-27 src/com/cisco/mscviewer/model/AbstractEntityHeaderModelListener.java

@@ -12,7 +12,7 @@
 package com.cisco.mscviewer.model;
 
 public abstract class AbstractEntityHeaderModelListener implements
-EntityHeaderModelListener {
+        EntityHeaderModelListener {
 
     @Override
     public int getEntityHeaderModelNotificationPriority() {

### 2015-05-27 src/com/cisco/mscviewer/model/EntityHeaderModelListener.java

@@ -11,12 +11,16 @@
  */
 package com.cisco.mscviewer.model;
 
-
 public interface EntityHeaderModelListener {
-    void entityAdded(ViewModel eh, Entity en, int idx);    
-    void entityRemoved(ViewModel eh, Entity parentEn, Entity en, int idx);    
+    void entityAdded(ViewModel eh, Entity en, int idx);
+
+    void entityRemoved(ViewModel eh, Entity parentEn, Entity en, int idx);
+
     void entitySelectionChanged(ViewModel eh, Entity en, int idx);
+
     void entityMoved(ViewModel eh, Entity en, int toIdx);
+
     int getEntityHeaderModelNotificationPriority();
+
     void boundsChanged(ViewModel entityHeaderModel, Entity en, int idx);
 }

### 2015-05-27 src/com/cisco/mscviewer/model/EventRange.java

@@ -22,9 +22,10 @@ public class EventRange {
     }
 
     public int getSize() {
-        return toIdx-fromIdx+1;
+        return toIdx - fromIdx + 1;
     }
+
     public Event getEventAtIndex(int idx) {
-        return dm.getEventAt(fromIdx+idx);
+        return dm.getEventAt(fromIdx + idx);
     }
 }

### 2015-05-27 src/com/cisco/mscviewer/model/InputUnit.java

@@ -12,17 +12,11 @@
 package com.cisco.mscviewer.model;
 
 public enum InputUnit {
-    NS("ns"),
-    US("us"),
-    MS("ms"),
-    S("s"),
-    M("m"),
-    H("h"),
-    T("ticks");
+    NS("ns"), US("us"), MS("ms"), S("s"), M("m"), H("h"), T("ticks");
 
     private final String str;
 
-    private InputUnit(String s){
+    private InputUnit(String s) {
         str = s;
     }
 
@@ -32,7 +26,7 @@ public enum InputUnit {
     }
 
     public long getNsCount() {
-        switch(this) {
+        switch (this) {
         case T:
         case NS:
             return 1L;
@@ -43,9 +37,9 @@ public enum InputUnit {
         case S:
             return 1000000000L;
         case M:
-            return 1000000000L*60;
+            return 1000000000L * 60;
         case H:
-            return 1000000000L*60*60;
+            return 1000000000L * 60 * 60;
         default:
             return -1;
         }

### 2015-05-27 src/com/cisco/mscviewer/model/Interaction.java

@@ -11,8 +11,8 @@
  */
 package com.cisco.mscviewer.model;
 
-import com.cisco.mscviewer.gui.renderer.InteractionRenderer;
 import com.cisco.mscviewer.gui.Marker;
+import com.cisco.mscviewer.gui.renderer.InteractionRenderer;
 import com.cisco.mscviewer.tree.Interval;
 
 /**
@@ -30,8 +30,8 @@ import com.cisco.mscviewer.tree.Interval;
  * An interaction has a type and an associated renderer.
  *
  * Interactions are stored in the data model as Intervals in an interval tree
- * {@see http://en.wikipedia.org/wiki/Interval_tree}. Elements of the tree
- * must implement the {@link Interval} interface, which this class does implement.
+ * {@see http://en.wikipedia.org/wiki/Interval_tree}. Elements of the tree must
+ * implement the {@link Interval} interface, which this class does implement.
  *
  * @author rattias
  */
@@ -46,10 +46,14 @@ public final class Interaction implements Interval {
      * Instantiates an <code>Interaction</code> with the specified model,
      * indices for source and sink even in the data model
      *
-     * @param model     {@link MSCDataModel} the interaction belongs to
-     * @param fromIdx   data model index of the source event
-     * @param toIdx     data model index of the sink event
-     * @param irenderer renderer for the interaction
+     * @param model
+     *            {@link MSCDataModel} the interaction belongs to
+     * @param fromIdx
+     *            data model index of the source event
+     * @param toIdx
+     *            data model index of the sink event
+     * @param irenderer
+     *            renderer for the interaction
      */
     public Interaction(MSCDataModel model, int fromIdx, int toIdx,
             InteractionRenderer irenderer) {
@@ -60,9 +64,11 @@ public final class Interaction implements Interval {
     }
 
     /**
-     * if the source/sink event is passed as argument, returns the sink/source event.
+     * if the source/sink event is passed as argument, returns the sink/source
+     * event.
+     * 
      * @param ev
-     * @return 
+     * @return
      */
     public Event getOtherEvent(Event ev) {
         if (ev == getFromEvent()) {
@@ -74,20 +80,23 @@ public final class Interaction implements Interval {
         }
     }
 
-        /**
-     * returns the type of the Event. The type corresponds to the
-     * name of the Renderer class, stripped of the "Renderer" suffix.
-     * @return 
+    /**
+     * returns the type of the Event. The type corresponds to the name of the
+     * Renderer class, stripped of the "Renderer" suffix.
+     * 
+     * @return
[…]

### 2015-05-27 src/com/cisco/mscviewer/model/JSonArrayValue.java

@@ -3,25 +3,26 @@ package com.cisco.mscviewer.model;
 import java.util.ArrayList;
 
 public class JSonArrayValue implements JSonValue {
-    private ArrayList<JSonValue> value;
-    
+    private final ArrayList<JSonValue> value;
+
     @SuppressWarnings("unchecked")
     public JSonArrayValue(ArrayList<JSonValue> al) {
-        value = (ArrayList<JSonValue>)al.clone();
+        value = (ArrayList<JSonValue>) al.clone();
     }
 
     public JSonArrayValue() {
         value = new ArrayList<JSonValue>();
     }
-    
+
     public ArrayList<JSonValue> value() {
         return value;
     }
-    
+
+    @Override
     public String toString() {
         return value.toString();
     }
-    
+
     public int size() {
         return value.size();
     }

### 2015-05-27 src/com/cisco/mscviewer/model/Unit.java

@@ -12,17 +12,11 @@
 package com.cisco.mscviewer.model;
 
 public enum Unit {
-    NS("ns"),
-    US("us"),
-    MS("ms"),
-    S("s"),
-    M("m"),
-    H("h"),
-    D("d");
+    NS("ns"), US("us"), MS("ms"), S("s"), M("m"), H("h"), D("d");
 
     private final String str;
 
-    private Unit(String s){
+    private Unit(String s) {
         str = s;
     }
 

### 2015-05-27 src/com/cisco/mscviewer/model/package-info.java

@@ -31,3 +31,4 @@
 
  */
 package com.cisco.mscviewer.model;
+

### 2015-05-27 src/com/cisco/mscviewer/package-info.java

@@ -16,3 +16,4 @@
  * @since   2014-05-01
  */
 package com.cisco.mscviewer;
+

### 2015-05-27 src/com/cisco/mscviewer/script/PythonFunction.java

@@ -20,27 +20,27 @@ import org.python.core.PyTuple;
 
 public class PythonFunction {
     private final String name;
-    private String[] argNames;
+    private final String[] argNames;
     private String[] argDefaults;
-    private String[] argValues;
+    private final String[] argValues;
     private String doc;
     private boolean wasSet;
-    private Python python;
-    private String pkg;
-    
+    private final Python python;
+    private final String pkg;
+
     public PythonFunction(Python p, String pkg, String name) {
-    	this.pkg = pkg;
+        this.pkg = pkg;
         this.name = name;
         python = p;
-        PyObject args = p.eval("inspect.getargspec("+pkg+"."+name+")");
-        PyTuple t = (PyTuple) args;
+        final PyObject args = p.eval("inspect.getargspec(" + pkg + "." + name + ")");
+        final PyTuple t = (PyTuple) args;
         PyObject[] objs = ((PyList) t.get(0)).getArray();
         argNames = new String[objs.length];
         for (int i = 0; i < argNames.length; i++) {
             argNames[i] = objs[i].toString();
         }
         argValues = new String[objs.length];
-        Object l = t.get(3);
+        final Object l = t.get(3);
         if (l != null) {
             objs = ((PyTuple) l).getArray();
             argDefaults = new String[objs.length];
@@ -50,10 +50,10 @@ public class PythonFunction {
 
         for (int i = 0; i < argDefaults.length; i++) {
             argDefaults[i] = objs[i].toString();
-            int idx = argNames.length - argDefaults.length + i;
+            final int idx = argNames.length - argDefaults.length + i;
             argValues[idx] = argDefaults[i];
         }
-        PyString d = (PyString) p.get(name + ".__doc__");
+        final PyString d = (PyString) p.get(name + ".__doc__");
         if (d != null)
             doc = d.toString();
     }
@@ -62,10 +62,10 @@ public class PythonFunction {
         return name;
     }
 
-//    public void setDoc(String d) {
-//        doc = d;
-//    }
-//
+    // public void setDoc(String d) {
+    // doc = d;
+    // }
+    //
     public String getDoc() {
         return doc;
     }
@@ -93,14 +93,15 @@ public class PythonFunction {
     }
 
     public String getInvocation() {
-        StringBuilder sb = new StringBuilder();
-        int regArgCount = argValues.length - argDefaults.length;
+        final StringBuilder sb = new StringBuilder();
+        final int regArgCount = argValues.length - argDefaults.length;
         sb.append(name).append("(");
[…]

### 2015-05-27 src/com/cisco/mscviewer/tree/Interval.java

@@ -15,7 +15,8 @@ package com.cisco.mscviewer.tree;
  *
  * @author rattias
  */
-public interface Interval  extends Value {
-    int  getStart();
-    int  getEnd();    
+public interface Interval extends Value {
+    int getStart();
+
+    int getEnd();
 }

### 2015-05-27 src/com/cisco/mscviewer/tree/IntervalTree.java

@@ -19,81 +19,81 @@ import java.util.ArrayList;
  */
 public class IntervalTree extends AVLTree {
     public static boolean dbg = false;
-    
+
     public IntervalTree(String name) {
         super(name);
     }
-    
+
     public ArrayList<Interval> getIntervalsWithEndBound(int c) {
-        ArrayList<Interval> els = new ArrayList<Interval>();
+        final ArrayList<Interval> els = new ArrayList<Interval>();
         getIntervalsWithEndBound(c, els);
         return els;
     }
 
     public ArrayList<Interval> getContainingIntervals(int c) {
-        ArrayList<Interval> els = new ArrayList<Interval>();
+        final ArrayList<Interval> els = new ArrayList<Interval>();
         if (root != null)
-            ((IntervalTreeNode)root).getContainingIntervals(c, els);
+            ((IntervalTreeNode) root).getContainingIntervals(c, els);
         return els;
     }
-    
+
     public void getContainingIntervals(int c, ArrayList<Interval> ret) {
         if (root != null)
-            ((IntervalTreeNode)root).getContainingIntervals(c, ret);        
+            ((IntervalTreeNode) root).getContainingIntervals(c, ret);
     }
 
     public ArrayList<Interval> getIntersectingIntervals(int start, int end) {
-        ArrayList<Interval> els = new ArrayList<Interval>();
+        final ArrayList<Interval> els = new ArrayList<Interval>();
         if (root != null)
-            ((IntervalTreeNode)root).getIntersectingIntervals(start, end, els);
+            ((IntervalTreeNode) root).getIntersectingIntervals(start, end, els);
         return els;
-        
+
     }
 
-    public void getIntersectingIntervals(int start, int end, ArrayList<Interval> ret) {
+    public void getIntersectingIntervals(int start, int end,
+            ArrayList<Interval> ret) {
         if (root != null)
-            ((IntervalTreeNode)root).getIntersectingIntervals(start, end, ret);
-//        System.out.println("PATH TO 116:"+pathToStart(116));
-//        verify("???");
+            ((IntervalTreeNode) root).getIntersectingIntervals(start, end, ret);
+        // System.out.println("PATH TO 116:"+pathToStart(116));
+        // verify("???");
     }
-    
+
     public void getIntervalsWithEndBound(int c, ArrayList<Interval> ret) {
-        Interval o = (Interval)find(c);
+        final Interval o = (Interval) find(c);
[…]

### 2015-05-27 src/com/cisco/mscviewer/tree/TreeIntegrityException.java

@@ -11,22 +11,21 @@
  */
 package com.cisco.mscviewer.tree;
 
-
 /**
  *
  * @author rattias
  */
 @SuppressWarnings("serial")
 public class TreeIntegrityException extends Exception {
-    private String path;
+    private final String path;
     int value;
-    
+
     public TreeIntegrityException(String msg, String path, int v) {
         super(msg);
         this.path = path;
         value = v;
     }
-    
+
     public String getTreePath() {
         return path;
     }

### 2015-06-04 doc/manual/mscviewer.tex
refactored ColorPicker 'letter' subcomponent, added 'about memory'

@@
 
+\section{The Source View}
+The source View is a tab in the bottom-right part of the GUI. This view shows the original log file that was 
+parsed to create the sequence diagram model. Lines that contributed event information are highlighted in blue, 
+while other lines are shown in black. Clicking on an event line selects the correspoding event, provided that the
+owning entity was open in the sequence diagram area. Selecting an event in the sequence diagram causes the 
+corresponding line in the Source View to be selected. Double-clicking on an event line in the Source View
+causes the corresponding entity to be opened in the sequence diagram and the event selected.
+
+\section{The Data View}
+Events may have associated structured data. The data associated to the selected event is shown in the Data View,
+which is located inside a tab in the bottomr-right part of the GUI.
+
+\section{The Notes View}
+In order to facilitate a debugging session the user can associate notes to events. An note associated with an
+event is shown as a small yellow square on the event. Selecting the event and right-mouse-clicking the user can
+checkmark the "Note Sticker" menu item to make the note visible as a sticker in the sequence diagram.
+To create a note, the user selects the event and edit the note in the Notes View, which is situated in a tab
+in the bottom-right part of the GUI.
+
+is a tab in the bottom-right part of the GUI. This view shows the original log file that was 
+parsed to create the sequence diagram model. Lines that contributed event information are highlighted in blue, 
+while other lines are shown in black. Clicking on an event line selects the correspoding event, provided that the
+owning entity was open in the sequence diagram area. Selecting an event in the sequence diagram causes the 
+corresponding line in the Source View to be selected. Double-clicking on an event line in the Source View
+causes the corresponding entity to be opened in the sequence diagram and the event selected.
+
 \section{The Tool Bar}

### 2015-06-04 src/com/cisco/mscviewer/gui/NoteEditor.java

@@ -5,18 +5,10 @@ import java.awt.Color;
 import java.awt.Container;
 import java.awt.Font;
 import java.awt.font.TextAttribute;
-import java.io.ByteArrayInputStream;
-import java.io.ByteArrayOutputStream;
-import java.io.File;
-import java.io.IOException;
-import java.io.InputStream;
-import java.util.Enumeration;
 import java.util.HashMap;
 import java.util.Vector;
 
 import javax.swing.Box;
-import javax.swing.JButton;
-import javax.swing.JColorChooser;
 import javax.swing.JFrame;
 import javax.swing.JLayer;
 import javax.swing.JPanel;
@@ -26,29 +18,18 @@ import javax.swing.JToggleButton;
 import javax.swing.JToolBar;
 import javax.swing.event.DocumentListener;
 import javax.swing.text.AttributeSet;
-import javax.swing.text.BadLocationException;
 import javax.swing.text.DefaultStyledDocument;
-import javax.swing.text.Document;
 import javax.swing.text.Element;
 import javax.swing.text.SimpleAttributeSet;
 import javax.swing.text.StyleConstants;
 import javax.swing.text.StyledDocument;
-import javax.swing.text.html.HTMLEditorKit;
-import javax.swing.text.rtf.RTFEditorKit;
-import javax.xml.parsers.DocumentBuilder;
-import javax.xml.parsers.DocumentBuilderFactory;
-import javax.xml.parsers.ParserConfigurationException;
-
-import org.w3c.dom.Node;
-import org.w3c.dom.NodeList;
-import org.xml.sax.EntityResolver;
-import org.xml.sax.InputSource;
-import org.xml.sax.SAXException;
-
-import com.cisco.mscviewer.io.Session;
 
 
+@SuppressWarnings("serial")
 public class NoteEditor extends JPanel {
+    public static Color DEFAULT_FOREGROUND = Color.black;
+    public static Color DEFAULT_BACKGROUND = Color.white;
+    
     private JTextPane tp;
     private JToggleButton bold;
     private JToggleButton italic;
@@ -73,11 +54,17 @@ public class NoteEditor extends JPanel {
         italic.setEnabled(v);
         underline.setEnabled(v);
         fgPicker.setEnabled(v);
+        bgPicker.setEnabled(v);
     }
     public NoteEditor() {
         setLayout(new BorderLayout());
         StyledDocument doc = new DefaultStyledDocument();
+        
[…]

### 2015-08-06 doc/manual/mscviewer.tex
Various fixes

@@
 \usepackage{lipsum}
+\usepackage{dirtree}
 \include{generated/titlepage}
@@
 \section{Timestamps}
-It is possible to associate timestamps to each event throught the \texttt{time}
-key. The value can assume different formats, as shown in \texttt{lst4.msc},
-visible in fig.~\ref{fig:gui-lst4}. \prog{} internally converts the units
-indicated in the input files into nanoseconds. By default timestamps are shown
-to the left of events in a \texttt{hh:mm:ss} format. The format can be changed
-through the \texttt{view/Preferences...} menu item.
-
-%\lstinputlisting[language=Java]{../../examples/lst4.msc}
+Timestamps can be associated to events throught the \texttt{time}
+key. The value can assume different formats, as shown in \texttt{lst4.msc}:
+
+\lstinputlisting[language=Java]{../../examples/lst4.msc}
+.
+Regardless of the unit specified in input, \prog{} converts internally the
+timestamp into nanoseconds, and visualizes them in a format that can be chosen
+by the user. The default format is \texttt{hh:mm:ss,ms}, but it can be 
+changed through the the \texttt{Edit/Preferences...} menu item. Fig~\ref{fig:gui-lst4}
+shows timestamps visualized near events.
+
 \begin{figure}[ht!]
@@
 \section{Orphaned Interactions}
-When collecting traces from a system it is possible that either the even
+When collecting traces from a system it is possible that either the event
 representing a cause or the one representing an effect for an interaction goes
@@
 
-\section{The Sequence Diagram area}
-The sequence diagram area is situated on the top-right part of the GUI. Entities can be opened in this area by
-double-clicking on them in the Entity Tree. Open entities can be rearranged by dragging them from their 
-header.
-
-\section{The Source View}
-The source View is a tab in the bottom-right part of the GUI. This view shows the original log file that was 
+\section{The Sequence Diagram}
+The Sequence Diagram ais situated on the top-right part of the GUI. Entities can be opened in this area by
+various user actions:
+\begin{itemize}
+\item double-clicking a node in the \textit{Entity Tree}, or pressing enter open the selected entity
+\item double-clicking on a line in the \textit{Log File View}
+\item programmatically, by Python scripts.
+\end{itemize}
+
+Open entities can be rearranged by dragging their \texttt{Header}, the rectangle containing the entity
+name.
+
+Width for an entity column can be increased or reduced by selecting the header and pressing repreatedly the
+\keystroke{+} or \keystroke{-} keys.
+
+\section{The Log File View}
+The Log File View is a tab in the bottom-right part of the GUI. This view shows the original log file that was 
 parsed to create the sequence diagram model. Lines that contributed event information are highlighted in blue, 
@@
 
-\section{The Data View}
+Clicking and dragging in the Log View causes text to be selected. When the mouse button is released the 
+currently selected test is copied in the system clipboard.
+
+\section{The Event Data View}
 Events may have associated structured data. The data associated to the selected event is shown in the Data View,
@@
 \section{The Notes View}
-In order to facilitate a debugging session the user can associate notes to events. An note associated with an
+In order to facilitate a debugging session the user can associate notes to events. A note associated with an
 event is shown as a small yellow square on the event. Selecting the event and right-mouse-clicking the user can
@@
 
-is a tab in the bottom-right part of the GUI. This view shows the original log file that was 
-parsed to create the sequence diagram model. Lines that contributed event information are highlighted in blue, 
-while other lines are shown in black. Clicking on an event line selects the correspoding event, provided that the
-owning entity was open in the sequence diagram area. Selecting an event in the sequence diagram causes the 
-corresponding line in the Source View to be selected. Double-clicking on an event line in the Source View
-causes the corresponding entity to be opened in the sequence diagram and the event selected.
-
 \section{The Tool Bar}
@@
 		\end{minipage}\\ \\
+    \tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/note.png}
+    & \begin{minipage}[t]{0.8\columnwidth}
+        Shows/hides notes associated to events
+        \end{minipage}\\ \\
 	\end{longtable}  
@@
 
-\chapter{Pyhton API}
+\chapter{Customizing \prog}
+\section{Preferences}
+a number of parameters affecting the GUI can be modified in the \texttt{Preferences}
+dialog accessible via the \texttt{Edit/Preferences...} menu item. These include:
+\begin{itemize}
+\item how to interpret event timestamps where units were not specified
+\item the visualized format for timestamps in the sequence diagram
+\item the format for entities headers in the sequence diagram
+\item colors of various GUI elements   
+\end{itemize}
+When any of the parameters is modified the change is immediately visible in the GUI. If
+the dialog is closed by pressing the \texttt{Ok} button, then those changes become permanent.
+Pressing the \texttt{Cancel} button or closing the dialog via the OS-specific window-close button
+results in the original parameters being restored.
+
+The original parameters can also be restored without closing the dialog by pressing the \texttt{Reset}
+button.
+
+\section{Sessions}
+While \texttt{Preferences} control program parameters irrespective of the loaded log files, some set 
+of parameters can be associated to specific Log files loaded in the tool. These set of parameters, 
+referrred to as \textit{Sessions}, are saved in XML files which can be reloaded later or even
+transfer across different machines. Session information includes:
+\begin{itemize}
+\item Entities open in the sequence diagram
+\item currently selected event or interaction
+\item Notes associated to events
+\item markers associated to events
+\end{itemize}
+
+\section{Passing Resource Sets to \prog{}}
+At the time of execution \prog{} can be passed one or more directories, each one specifying a set of resources.
+Resource directories are passed using the \texttt{-r} option. Directory paths should be separated using 
+the OS-specific path separator character (\texttt{:} on Linux/OS-X and \texttt{;} on Windows). 
+Each directory can contain one or both the following sub-directories:
+\begin{itemize}
+\item \texttt{renderer}: this directory can contain images in \texttt{.png} format. These images
+are loaded by \prog and become available as renderer for events whose type matches the file names (without the extension).
+\item \texttt{script}: this directory can contains Python scripts. These scripts are parsed by \prog and 
+specially decorated functions become available for execution in the GUI. For more information 
+on Python scripts see chapter~\ref{sec:python-api}. 
+\end{itemize}
+
+Consider the following example on Linux:
+\begin{lstlisting}
+mscviewer -r food;animals test.msc
+\end{lstlisting}
+
+\noindent where \texttt{test.msc} contains
+
+\begin{lstlisting}
+@event { "entity":"food",    "type":"bananas", "label":"bananas"}
+@event { "entity":"food",    "type":"cake",    "label":"cake"}
+@event { "entity":"animals", "type":"bee",     "label":"bee"}
+@event { "entity":"animals", "type":"snail",   "label":"snail"}
+\end{lstlisting}
+
+\noindent and the current directory has the following directory structure:
+
+\dirtree{% comment here is required as first char to be found must be a dot
+.1 \texttt{.} . %
+.2 animals/. % space after dot is required!
+.3 renderer/. %
+.4 bee.png. %
+.4 snail.png. %
+.2 food/. %
+.3 renderer/. %
+.4 bananas.png. %
+.4 cake.png. %
+}
+
+This loads a sequence diagram where icons for various events are picked up from the \texttt{renderer}
+subdirectories.
+
+This example is present in the \texttt{examples/custom-icons} directory of the distribution, together with 
+a \texttt{run.sh} script that runs it regardless of the OS in use.
+
+\chapter{Python Integration}
 One of the most powerful aspects of \prog{} is the integration with a Python interpreter
@@
 system multiple times, this scales the effort of an activity that otherwise would have to be
-performed by one or more human beings.
+performed by one or more human beings. A tutorial on how to create flow validation scripts
+using the APIs described in this chapter is provided in chapter~\ref{chp:flowdef}
 
@@
 open some entities in the sequence diagram, captures screenshots and saves them.
+
+The interaction between the user Python script and the tool is done through APIs 
+collected in a few Python files the script can import, and described in details 
+in \ref{sec:python-api}.
+
+\section{\textit{Hello World} of Python Integration}
+
+Let's start with the smallest possible \textit{Hello World} program in Python (\texttt{examples/hello.py}):
+
+\lstinputlisting{../../examples/hello.py}
+
+This can be executed by \prog{} as follows:
+
+\begin{verbatim}
+$ mscviewer -b examples/hello.py examples/lst1.msc 
+ Hello World
+\end{verbatim}
+
+Here we're invoking \prog{} in batch mode, passing the \texttt{hello.py} script and
+a log file. The log file is not even used in this case, and the script is simply
+passed to the embedded Python interpreter which runs it, producing the output on
+the console. Not particularly exciting.
+
+Let's examine next how we can interact with the model created from the log file, as
+demonstrated by \texttt{examples/info.py}:
+
+\lstinputlisting{../../examples/info.py}
+
+\begin{verbatim}
+$ bin/mscviewer -b examples/info.py examples/lst1.msc
+ entity= producer label= start
+ entity= producer label= produce
+ entity= consumer label= consume
+\end{verbatim}
+
+This example uses the Python API to interact with the model created from the log file, 
+printing out for each event the entity path and the label. The extensive set of APIs 
+provided to interact with the model as well as the GUI is documented in section
+\ref{sec:python-api}.
+
+In addition to executing a single Python program in batch mode, it is possible
+to define any number of Python functions that can be explicitly invoked by the
+user within the GUI. To demonstrate this, let's consider the \texttt{examples/hello1/hello.py}
+file:
+
+\lstinputlisting{../../examples/hello1/hello.py}
+
+In order for functions to be visible by the gui we need to place the Python file declaring them
+into a package, which we can achieve by creating an empty \texttt{\_\_init\_\_.py} file in the 
+directory containing the file. For this reason, the \texttt{examples/hello1} directory has
+the following structure:
+
+\hfill \break
+\dirtree{% comment here is required as first char to be found must be a dot
+.1 \texttt{hello1}. %
+.2 \texttt{\_\_init\_\_.py}. % space after dot is required!
+.2 \texttt{hello.py}. % space after dot is required!
+}
+\hfill \break
+
+We can now run \prog{} as follows:
+
+\begin{verbatim}
+mscviewer -p examples/hello1 examples/lst1.msc
+\end{verbatim}
+
+Once the GUI comes up, click on the \texttt{scripts} tab. The tool will parse the Python
+modules available in the path, and the visualized tree should contain a \texttt{hello1}
+node representing the package. Expanding such node should reveal a leaf node representing
+the \texttt{hello\_world()} function. Notice that in order for a function to show up in the
+GUI tree the function has to be decorated by the \texttt{@msc\_fun} decorator. This 
+allow to have various utility functions in the file that do not show up as first class
+citizens in the GUI.
+
+In order to execute the function, just double-click on its node in the tree. In this 
+particular case the function takes no arguments, so it will be immediately executed producing
+the expected \texttt{Hello World} output on the console.
+
+Let's now consider \texttt{examples/hello2/hello.py}:
+
+\lstinputlisting{../../examples/hello2/hello.py}
+
+This example provides three functions that will be listed in the GUI:
+\begin{itemize}
+\item \texttt{hello\_something()} expects an argument of type string and prints the concatenation of \texttt{'Hello '}
+followed by such string. The first time we double-click on this node a dialog will open allowing us to 
+provide a value for the argument. We can type \texttt{'World'} (including the apices) and press \texttt{OK}. 
+This time the output will not be produced on the console, but rather in the \texttt{Script Console} tab in the 
+bottom-right are of the GUI. Double-clicking on the same node again will not open the dialog again, as \prog{}
+remembers the previosly passed value and uses it again.  In order to open the dialog again and change the 
+value keep the \keystroke{SHIFT} key pressed while double-clicking on the node. 
+\item \texttt{hello\_world()} calls the previous function passing the value of \texttt{'World'} for the argument.
+\item \texttt{hello\_world\_or\_not()} has a keyword parameter. Keyword parameters have a default
+value, hence double-clicking on the node executes the function with such default value for the
+parameter. Again, to change such value keep the \keystroke{SHIFT} key pressed while double-clicking.
+\end{itemize}
+
+It should be noted that this particular example follows a common pattern which allows a script
+to be executed in batch mode, or to provide functions to be called in interactive mode. The pattern
+consists in the presence of an \texttt{if \_\_name\_\_ == '\_\_main\_\_'} statement which 
+is executed when in batch mode, calling a function with default values. Also, the pattern
+makes use of the \texttt{msc\_print} function to produce output: this function will direct
+its output to the GUI \texttt{Script Console} view when in interactive mode, while 
+falling back to printing on the console when in batch mode. We can run the 
+script in batch mode with
+
+\begin{verbatim}
+mscviewer -b examples/hello2/hello.py examples/lst1.msc
+\end{verbatim}
+
+\
+
+\section{Pyhton API}
+\label{sec:python-api}
 
@@
 \end{itemize}
-\section{Model API}
+
+\subsection{Model API}
 
@@
 
-\section{GUI API}
+\subsection{GUI API}
 \input{generated/python-api-gui.tex}
 
-\section{Flows API}
+\subsection{Flows API}
+\label{sec:flow-api}
 \input{generated/python-api-flowdef.tex}
 
-\section{Graph API}
+\subsection{Graph API}
 \input{generated/python-api-graph.tex}
 
-\chapter{Customizing \prog}
-\section{Icons}
-\section{Python Scripts}
-
-\chapter{Flow Definition}
-\section{Introduction}
+\section{Flow Definition}
+\label{chp:flowdef}
+
 \prog{} provides a powerful infrastructure supporting automated flow validation.
@@
 
-\section{Your First Flow Definition}
-The following is a simple flow-definition script:
+\subsection{Your First Flow Definition}
+File \texttt{examples/flw1.py} contains a simple flow definition script. Let's look at it in detail:
 \lstinputlisting{../../examples/flw1.py}
 
+\noindent Lines 1, 2 import some packages required for flow definition. These are defined in Python files
+contained in the \texttt{resources/default} directory of the \prog{} install directory.
+
+Lines 5-7 define a function returning a flow definition. The flow definition is specified as a sequence (\texttt{fseq})
+of two events (\texttt{fev}). The two parameters for each \texttt{fev()} element are respectively the entity id and
+the label of the events. A model containing an ordered sequence of two events on an entity named \textit{foo}, the 
+first one with label \texttt{event\_a} and the second with label \texttt{event\_b} does contain the flow specified
+by function \texttt{get\_flow()}. Function \texttt{get\_flow()} returns the defined flow as an object.
+
+Function
+\texttt{find\_flow()} at line 12 calls such function to retrieve the flow definition and repeatedly calls function
+\texttt{match()} on it. the \texttt{match()} function attempts to match the flow definition to the model
+currently loaded in \prog{}, starting with the model event with the index specified as the \texttt{start\_event\_idx}
+parameter. In case of match, the function returns the index of the last event in the model matching one of the elements
+in the flow definition, plus one. If the entire flow definition is not found in the model, then the function throws a
+FlowError. If passed a starting event index corresponding to the total number of events the function returns -1.
+
+The \texttt{examples/flw1-match.msc} is an example of a log file containing the specified flow:
+\lstinputlisting{../../examples/flw1-match.msc}
+
+However, note that the \texttt{examples/flw1-match.msc} file also contains the specified flow:
+
+\lstinputlisting{../../examples/flw1-match2.msc}
+
+This is the case because \texttt{fseq} requires events to be in the specified order, but
+not to be contiguous in the file, or even within the entity.
+
+We can test the scripts by running \prog{} in batch mode:
+
+\begin{verbatim}
+$ mscviewer -b examples/flw1.py examples/flw1-match.msc 
+ Found match!
+$ mscviewer -b examples/flw1.py examples/flw2-match.msc 
+ Found match!
+$ bin/mscviewer -b examples/flw1.py examples/flw1-nomatch.msc
+ No match found ( element (foo, event_a) not found in model. )
+$\end{verbatim}
+
+\subsection{Model Elements for a Flow}
+
+In addition to knowing that a certain flow is present in a model, you may want to discover which 
+\texttt{fev} elements match which mdodel events. This can be achieved using the \texttt{get\_model\_map()}
+function, as illustrated by the \texttt{examples/flw2.py} example:
+
+\lstinputlisting{../../examples/flw2.py}
+
+The \texttt{get\_model\_map()} function returns a map where each \texttt{fev} in the flow definition is a key,
+and the event matching it is the value associated to the key. Various pieces of information 
+can be stracted from the event using the \texttt{event\_} API defined in the \texttt{msc.model} module.
+In this example, we print the line number where the event is defined in the input file:
+
+\begin{verbatim}
+$ bin/mscviewer -b examples/flw2.py examples/flw1-match.msc
+ found match!
+ fev(foo, event_b) : 2
+ fev(foo, event_a) : 1
+$ bin/mscviewer -b examples/flw2.py examples/flw1-match2.msc
+ found match!
+ fev(foo, event_b) : 4
+ fev(foo, event_a) : 1
+\end{verbatim}
+
 \appendix
-\section{Useful Links}
-\begin{tabular}{l l p{9.0cm}}
-
-\end{tabular}
 

### 2015-08-06 src/com/cisco/mscviewer/Main.java

@@ -19,6 +19,8 @@ import java.nio.charset.StandardCharsets;
 import java.nio.file.Files;
 import java.nio.file.Paths;
 import java.util.Iterator;
+import java.util.logging.Level;
+import java.util.logging.Logger;
 
 import javax.script.ScriptException;
 import javax.swing.SwingUtilities;
@@ -41,6 +43,7 @@ import com.cisco.mscviewer.model.MSCDataModel;
 import com.cisco.mscviewer.model.ViewModel;
 import com.cisco.mscviewer.script.Python;
 import com.cisco.mscviewer.script.ScriptResult;
+import com.cisco.mscviewer.util.MSCViewerError;
 import com.cisco.mscviewer.util.Report;
 import com.cisco.mscviewer.util.Resources;
 import com.cisco.mscviewer.util.Utils;
@@ -68,28 +71,19 @@ abstract class Opt {
  * @since Jun 2012
  */
 public class Main {
+    public static final String PYPATH = "pypath";
     public static final String VERSION = "2.1.0";
     public static final boolean WITH_BLOCKS = true;
     private static boolean topologicalSorting = true;
     
     private static Loader loader;
-    private static MainFrame mf;
-    @SuppressWarnings("unused")
-    private static boolean extra;
+   @SuppressWarnings("unused")
     private static String script;
     private static String loaderClass = "JsonLoader";
-    // public static String loaderClass = "LegacyLoader";
     static boolean batchMode = false;
     private static String batchFun = null;
-
-    private static final void appendToPyPath(String s) {
-        String v = System.getProperty("pypath");
-        if (v != null && v.length() > 0)
-            v += File.pathSeparator + s;
-        else
-            v = s;
-        System.setProperty("pypath", v);
-    }
+    private static String plugins;
+    private static HeatGraphWindow graph;
 
     private static final Opt[] opts = new Opt[] {
             new Opt('h', "help", true, "shows this help") {
@@ -113,16 +107,10 @@ public class Main {
                     }
                 }
             },
-            new Opt('p', "pypath", true, "specify a Python module search path") {
+            new Opt('p', PYPATH, true, "specify a Python module search path") {
                 @Override
                 void found(String arg) {
                     appendToPyPath(arg);
-                }
-            },
-            new Opt('x', "extra", false, "enable some extra features") {
-                @Override
-                void found(String arg) {
-                    Main.extra = true;
                 }
             },
             new Opt('s', "script", true,
@@ -157,7 +145,18 @@ public class Main {
                 }
             }            
     };
[…]

### 2015-08-06 src/com/cisco/mscviewer/expression/ExpressionParser.java

@@ -9,7 +9,6 @@
 
 package com.cisco.mscviewer.expression;
 
-import java.util.ArrayList;
 import java.util.List;
 
 import javax.script.ScriptEngine;
@@ -19,6 +18,8 @@ import javax.script.ScriptException;
 
 import com.cisco.mscviewer.model.Event;
 import com.cisco.mscviewer.model.Interaction;
+import com.cisco.mscviewer.util.MSCViewerError;
+import com.cisco.mscviewer.util.Report;
 
 /**
  * Parser for the expression grammar accepted by search fields. THe grammar is 
@@ -50,19 +51,19 @@ public class ExpressionParser {
         final List<ScriptEngineFactory> factories = mgr.getEngineFactories();
         for (final ScriptEngineFactory factory : factories) {
             final String langName = factory.getLanguageName();
-            // String langVersion = factory.getLanguageVersion();
-            if (langName.equals("ECMAScript")) {
+
+            if ("ECMAScript".equals(langName)) {
                 engine = factory.getScriptEngine();
                 break;
             }
         }
         if (engine == null) {
-            throw new Error("Unable to retrieve JavaScript engine.");
+            throw new MSCViewerError("Unable to retrieve JavaScript engine.");
         }
     }
 
-    final static int LEFT = 0;
-    final static int RIGHT = 1;
+    static final int LEFT = 0;
+    static final int RIGHT = 1;
 
     /*
      * start ::= 'event' [type=event] 'where' orexp | 'interaction' [type=int]
@@ -74,7 +75,7 @@ public class ExpressionParser {
      * '<' | '>' | '<=' | '>=') LONG ('ns' | 'us' | 'ms' | 's')
      */
 
-    public static void main(String args[]) {
+    public static void main(String[] args) {
         final ParserState ps = new ParserState(args[0]);
         final ParsedExpression expr = new ExpressionParser().parse(ps);
         if (expr != null) {
@@ -83,7 +84,7 @@ public class ExpressionParser {
             System.out.println(toJS(expr.getFirstToken()));
         }
         if (args[0].endsWith("" + Token.COMPL_CHAR)) {
-            final ArrayList<String> compl = ps.getCompletions();
+            final List<String> compl = ps.getCompletions();
             System.out.println("completions:");
             for (final String tt : compl) {
                 System.out.println("    " + tt);
@@ -162,7 +163,7 @@ public class ExpressionParser {
             final boolean b = (Boolean) engine.eval(js);
             return b;
         } catch (final ScriptException e) {
[…]

### 2015-08-06 src/com/cisco/mscviewer/graph/Graph.java

@@ -8,10 +8,12 @@ import com.cisco.mscviewer.model.MSCDataModel;
 
 public class Graph {
     private final ArrayList<GraphSeries> series;
-
+    private String name;
+    
     public Graph(String name) {
         this.series = new ArrayList<GraphSeries>();
         MSCDataModel.getInstance().addGraph(this);
+        this.name = name;
     }
 
     public void add(GraphSeries g) {

### 2015-08-06 src/com/cisco/mscviewer/gui/StyledButton.java

@@ -38,6 +38,7 @@ public class StyledButton extends JButton {
 
     }
     
+    @Override
     public void paintComponent(Graphics g) {
         Graphics2D g2 = (Graphics2D)g;
         if (getModel().isRollover()) {

### 2015-08-06 src/com/cisco/mscviewer/gui/graph/EntityCheckBox.java

@@ -6,7 +6,7 @@ import com.cisco.mscviewer.graph.GraphSeries;
 
 @SuppressWarnings("serial")
 public class EntityCheckBox extends JCheckBox {
-    public GraphSeries data;
+    transient public GraphSeries data;
 
     public EntityCheckBox(GraphSeries gd) {
         super(gd.getName());

### 2015-08-06 src/com/cisco/mscviewer/io/ConfigLoader.java

@@ -14,6 +14,8 @@ package com.cisco.mscviewer.io;
 import java.io.File;
 import java.io.IOException;
 import java.text.ParseException;
+import java.util.logging.Level;
+import java.util.logging.Logger;
 
 import javax.swing.JOptionPane;
 import javax.xml.parsers.ParserConfigurationException;
@@ -24,6 +26,7 @@ import org.xml.sax.Attributes;
 import org.xml.sax.SAXException;
 import org.xml.sax.helpers.DefaultHandler;
 
+import com.cisco.mscviewer.Main;
 import com.cisco.mscviewer.model.MSCDataModel;
 
 @SuppressWarnings("serial")
@@ -69,7 +72,8 @@ public class ConfigLoader {
                     try {
                         t = Config.getTimeSinceEpoch(dateString);
                     } catch (final ParseException e) {
-                        e.printStackTrace();
+                        Logger logger = Logger.getLogger(Main.class.getName());
+                        logger.log(Level.INFO,"startElement() failed:", e);                        
                     }
                     final File f = new File(logPath);
                     final long lastModified = f.lastModified();
@@ -192,6 +196,8 @@ public class ConfigLoader {
         try {
             saxParser.parse(fname, handler);
         } catch (final UserAbortException e) {
+            Logger logger = Logger.getLogger(Main.class.getName());
+            logger.log(Level.INFO,"Load operation aborted by user", e);                        
         } catch (final SAXException e) {
             throw new IOException(e);
         }

### 2015-08-06 src/com/cisco/mscviewer/io/JsonLoader.java

@@ -23,10 +23,13 @@ import java.text.SimpleDateFormat;
 import java.util.ArrayList;
 import java.util.Date;
 import java.util.HashMap;
+import java.util.List;
 import java.util.Properties;
 import java.util.TimeZone;
 import java.util.concurrent.CountDownLatch;
 import java.util.concurrent.ExecutionException;
+import java.util.logging.Level;
+import java.util.logging.Logger;
 
 import javax.swing.JOptionPane;
 import javax.swing.SwingUtilities;
@@ -167,7 +170,7 @@ public class JsonLoader implements Loader {
             }
         } catch (final IndexOutOfBoundsException ex) {
             throw new IllegalArgumentException(fname + ":" + lineNum + ":"
-                    + pos + ":Expecting " + expected + ", found end-of-line.");
+                    + pos + ":Expecting " + expected + ", found end-of-line.", ex);
         }
     }
 
@@ -356,7 +359,7 @@ public class JsonLoader implements Loader {
                                 } catch (final ClassNotFoundException e1) {
                                     throw new IOException(fname + ":" + lineNum
                                             + ":Unable to instantiate class "
-                                            + rendererName + ".", e);
+                                            + rendererName + ".", e1);
                                 }
                             }
                             try {
@@ -421,7 +424,7 @@ public class JsonLoader implements Loader {
                                     MSC_KEY_INTER_ID).toString());
                         } else if (sourceValue instanceof JSonArrayValue) {
                             // this event is source for multiple interactions
-                            final ArrayList<JSonValue> al = ((JSonArrayValue) sourceValue)
+                            final List<JSonValue> al = ((JSonArrayValue) sourceValue)
                                     .value();
                             for (final JSonValue j : al) {
                                 interAttrs.add((JSonObject) j);
@@ -628,6 +631,8 @@ public class JsonLoader implements Loader {
             latch.await();
         } catch (final InterruptedException e) {
             // TODO Auto-generated catch block
+            Logger logger = Logger.getLogger(Main.class.getName());
+            logger.log(Level.INFO, "exception while waiting for load completion", e);                        
             e.printStackTrace();
         }
     }
@@ -644,8 +649,6 @@ public class JsonLoader implements Loader {
                 MainFrame.getInstance().setFilename(fname);
             });
         } catch (InvocationTargetException | InterruptedException e) {
-            // TODO Auto-generated catch block
-            e.printStackTrace();
         }
     }
     

### 2015-08-06 src/com/cisco/mscviewer/script/Python.java

@@ -54,7 +54,7 @@ public class Python {
 
     private void traverse(String pathEl, String fpath, int level,
             ArrayList<String> dirs) {
-        final String fullpath = pathEl + "/" + fpath;
+        final String fullpath = fpath.equals("") ? pathEl : pathEl + "/" + fpath;
         final File f = new File(fullpath);
         if (f.isDirectory()) {
             dirs.add(f.getAbsolutePath());
@@ -111,9 +111,10 @@ public class Python {
 
             interpreter.exec("import sys");
             interpreter.exec("import inspect");
-            // interpreter.exec("import mscviewer");
             interpreter.exec("def list_msc_functions(pkg):\n"
+                   // + "    print 'PKG=', pkg\n"
                     + "    ret = []\n" + "    for fn_name in dir(pkg):\n"
+                  //  + "        print 'FUNC = ', fn_name\n"
                     + "        fn = getattr(pkg, fn_name)\n"
                     + "        if hasattr(fn, \"is_msc_fun\"):\n"
                     + "            ret.append(fn_name)\n" + "    return ret;");

### 2015-08-06 src/com/cisco/mscviewer/tree/AVLTreeNode.java

@@ -14,6 +14,9 @@ package com.cisco.mscviewer.tree;
 import java.util.ArrayList;
 import java.util.HashSet;
 import java.util.List;
+import java.util.Set;
+
+import com.cisco.mscviewer.util.MSCViewerError;
 
 /**
  * This class implements an Interval Tree (actually, an Augmented Tree). The
@@ -93,20 +96,20 @@ public class AVLTreeNode {
         return l;
     }
 
-    protected void verify(AVLTreeNode root, HashSet<Object> set, String msg,
+    protected void verify(AVLTreeNode root, Set<Object> set, String msg,
             int min, int max) {
         if (data.getValue() < min || data.getValue() > max) {
             final List<String> al = new ArrayList<String>();
             root.pathsToValue(data.getValue(), "", al);
             System.err.println("Exception: current tree: ");
-            throw new Error(msg + ":" + al.get(0) + ": " + data.getValue()
+            throw new MSCViewerError(msg + ":" + al.get(0) + ": " + data.getValue()
                     + " should be in range (" + min + "," + max + ")");
         }
         if (set.contains(this))
-            throw new Error("Circular Link: " + msg);
+            throw new MSCViewerError("Circular Link: " + msg);
         set.add(this);
         if (set.contains(data))
-            throw new Error("Duplicated value: " + msg);
+            throw new MSCViewerError("Duplicated value: " + msg);
         set.add(data);
         if (left != null) {
             left.verify(root, set, msg, min, data.getValue());

### 2015-08-06 src/com/cisco/mscviewer/util/MSCViewerError.java

@@ -1,0 +1,8 @@
+package com.cisco.mscviewer.util;
+
+@SuppressWarnings("serial")
+public class MSCViewerError extends Error {
+    public MSCViewerError(String s) {
+        super(s);
+    }
+}
